### 2015-03-23 paper.tex
Initial import

\documentclass{llncs}

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[all]{xy}
\usepackage{float}
\usepackage{listings}
\usepackage{lipsum}

\usepackage[ruled,vlined]{algorithm2e}
\usepackage{alltt}
\urldef{\mailsa}\path|pat@dcs.gla.ac.uk|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}
\newlength{\halftextwidth}
\setlength{\halftextwidth}{0.47\textwidth}
\usepackage{multicol}
\usepackage{listings}
\usepackage{url}
\usepackage{coffee2}
%\usepackage{amsthm}
%\newtheorem*{definition}{Definition}#
\usepackage{amsopn}

\pagestyle{plain}
\begin{document}

\title{Constructing Sailing Match Race Schedules: round robin pairing lists}
\titlerunning{Match Race Scheduling}
%\toctitle{}
\author{Ciaran McCreesh, Craig MacDonald, Alice Miller and Patrick Prosser}
\authorrunning{McCreesh, MacDonald, Miller and Prosser}
\tocauthor{Patrick Prosser}
\institute{School of Computing Science, University of Glasgow, fname.sname@glasgow.ac.uk}
\maketitle

\begin{abstract} 
The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog.
\end{abstract}

\section{Introduction}
\coffee{1}

\section{Problem Definition: round robin pairing lists}
In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section M.2 Recommended Criteria for Round Robin Pairing Lists,  the following criteria are given:

\begin{enumerate}
\item Each skipper sails against each other skipper once.
\item When there is an even number of flights, each skipper has the same number of port and starboard assignments. 
\item When there is an odd number of flights, the first half of the skippers will have one more starboard assignment.
\item No skipper in the last match of a flight should be in the first match of the next flight. 
\item No skipper should have more than two consecutive port or starboard assignments.
\item Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
\item In flights with five or more matches no skipper should be in the next-to-last match in a flight and then in the first match of the next flight.
\item If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper (i.e. \#1 will be starboard against \#2, \#3 will be starboard against \#4).
\item Close ranked skippers meet in the last flight.
\item Minimize the number of boat changes.
\item Skippers in the last match of a flight do not change boats.
\item Skippers in new boats do not sail in the first match of the next flight.
\item Skippers have a reasonable sequence of matches and blanks.
\end{enumerate}

\noindent
Note: criteria 10, 11 and 12 only apply when there are less boats than skippers

\section{The Constraint Models}
The schedules are produced in 4 stages. The first stage produces a schedule that respects criteria 1, 4, 11 and 12 and minimises criteria 10 (boat changes). The second stage constructs a schedule that respects criteria 1,4,11,12 again and has criteria 10 as a hard constraint generated from first stage and minimises criteria 6 (balance). This results in a schedule that attempts to minimise boat changes \emph{and} balance. The third stage satisfies criteria 9, and is a simple translation of the schedule produced in stage 2.  The final stage, stage 4, orients skippers within matches to address criteria 2, 3 and 8.

We now describe the constraint models and processes used in each stage. In the text below we assume there are $n$ skipper and $b$ boats, with $m = b/2$ matches in a flight. In total there are $t = n(n-1)/2$ matches and $f = \lceil n(n-1)/m  \rceil$ flights. We may use the schedule in Table \ref{tab1}, for 7 skippers and 6 boats, to help illustrate the constraint models. Our descriptions of the models omit some minor details, however the models are available to download here (give us a link or something).

\begin{table}[h]
%\vspace{-0.2cm}
\begin{center}
\begin{tabular}{cc} \\ 
flight & matches \\ \hline
0 & (0,1) (2,3) (4,5)  \\
1 & (0,2) (4,6) (1,5)  \\
2 & (2,6) (0,5) (1,3)  \\
3 & (5,6) (0,3) (1,4)  \\
4 & (3,5) (1,6) (2,4)  \\
5 & (3,6) (0,4) (2,5)  \\
6 & (3,4) (1,2) (0,6)  \\ \hline
\end{tabular}
\end{center}
\caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights. Skippers are numbered 0 to 6. Note that the order of skippers within a flight are significant as is position within a match (port or starboard). This schedule is the result of stages 1 and 2, and has yet to be renumbered and oriented (stages 3 and 4)}
\label{tab1}
\end{table}

\subsection{Stage 1: minimising boat changes}
The first thing we model is a skipper. A skipper $\sigma$ has a temporal view of his schedulle in the array of constrained integer variables $timeSlot_{0}$ to $timeSlot_{t-1}$ (equation \ref{eq3} below) and a state view in the array of constraint integer variables $state_{0}$ to $state_{f-1}$ (equation \ref{eq4} below), i.e. $state_{i}$ is the state of this skipper in flight $i$ and corresponds to timeslots $timeSlot_{i*m}$ to $timeSlot_{m.(i+1)-1}$.

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ timeSlot_{\tau} \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ state_{i} \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ state_{i} = FIRST \iff timeSlot_{i.m} \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ state_{i} = MID \iff  \exists_{j \in [i.m+1 .. i.m+m-2]} ~ timeSlot_{j} \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ state_{i} = LAST \iff timeSlot_{(i+1).m - 1} \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ state_{i} = BYE \iff  \forall_{j \in [i.m .. m.(i+1)-1]} ~ timeSlot_{j} = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ state_{i} = END \iff  \forall_{j \in [i.m .. m.(i+1)-1]} ~ timeSlot_{j} = -2  \label{eq9} \\
& globalCardinality(timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
\end{flalign}

In (\ref{eq3}) the array $timeSlot$ is defined and in (\ref{eq4}) $state$ is defined. If variable $timeSlot_{i} = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$. Variable $state_{i}$ gives the state of this skipper in flight $i$. The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{... actually, not first and not last.} (\ref{eq6}) or in the last time slot of the flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the skipper is in a bye (\ref{eq8}) and if all time slots in a flight are equal to -2 then the skipper has finished all his matches (\ref{eq9}).

A global cardinality constraint \cite{globCard} is then imposed on the array $timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e. $\{0 .. n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 .. 1\}$) and once only (i.e. $\{1 .. 1\}$). The $state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In addition, we have the rule that if a skipper has finished his matches in flight $i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on). These criteria are imposed on the $state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.

The constraints above are shown pictorially in Figure \ref{skipper5}, and corresponds to skipper 5 in the Table \ref{tab1} schedule. The $state$ array is presented as coloured boxes, and below that the $timeSlot$ array. The arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The $state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE. The schedule of Table \ref{tab1} is reproduced with the matches for skipper 5 emboldened. To the right of the schedule is schema for the dfa. Coloured arc represent a transition from one state to another. The dfa is encoded as a set of transition objects $\langle q_{i},\iota,q_{j} \rangle$ where a transition is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we specify the accepting states, being all states except the start state (white) and bye state (pink).

A boat change occurs when a skipper has been in a BYE state in flight $i$ and then is in a match in the next flight $i+1$. This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $totalChange$ (\ref{eq12}).

\begin{flalign}
& \forall_{i \in [0..f-2]} ~ change_{i} \in \{0,1\} \label{eq10} \\
& \forall_{i \in [0..f-2]} ~ change_{i} = 1 \iff state_{i} = BYE \wedge state_{i+1} \neq BYE \label{eq11} \\
& totalChange = \sum_{i=0}^{f-2} ~ change_{i} \label{eq12}
\end{flalign}

%\vspace{-6mm}
\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
\vspace{-25mm}
\caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey timeslots. The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state START in white, FIRST in blue, MID in yellow, LAST in green, BYE in pink and END in red.}
\label{skipper5}
\end{figure}

\noindent
We are now in a position to model criteria 1 (each skipper sails against every other skipper) and optimisation criteria 10 (minimise boat changes).  In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
match-perspective of the schedule, using a two dimensional array of variables $match$, where $match_{i,j}$ is the time slot that skippers $s_{i}$ and $s_{j}$ meet in a match. Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e. $match_{i,j}$ is \emph{exactly} the same constrained variable as $match_{j,i}$.  Constraint (\ref{eq15}) states that  a match between skippers $s_{i}$ and $s_{j}$ takes place at time $k$ (i.e. $match_{i,j} = k$) if and only if  skipper $s_{i}$'s $k^{th}$ time slot is skipper $s_{j}$ and conversely that skipper $s_{j}$'s $k^{th}$ time slot is skipper $s_{i}$.  Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e. $modMatch_{i,j}$ is the flight in which skippers $s_{i}$ and $s_{j}$ meet for a match. Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights. Also, since $modMatch_{i,j} \equiv modMatch_{j,i}$, setting rows to be all different also ensures that columns are all different.

%
% the match array
%
\begin{flalign}
& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match_{i,j} \in \{0..t-1\} \label{eq13} \\
& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match_{j,i} \equiv match_{i,j} \label{eq14} \\
& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ match_{i,j} = k \iff s_{i}.timeSlot_{k} = j  ~ \wedge ~ s_{j}.timeSlot_{k} = i  \label{eq15} \\
& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch_{i,j} \in \{0..f-1\} \label{eq16} \\
& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch_{j,i} \equiv modMatch_{i,j} \label{eq17} \\
& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch_{i,j} = \frac{match_{i,j}}{m} \label{eq18} \\
& \forall_{i \in [0..n-1]} ~ allDifferent(modMatch_{i}) \label{eq19}
\end{flalign}

\noindent
We now take a temporal view (\ref{eq20}), such that $time_{\tau}$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s_{i}$ and $s_{j}$ are in a match, i.e. we channel between the match-perspective and the temporal-perspective.
%
% one dimensional time and decision variables
%
\begin{flalign}
& \forall_{\tau \in [0..t-1]} ~ time_{\tau} \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
& \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time_{\tau} = (i,j) \iff match_{i,j} = \tau \label{eq21}
\end{flalign}

\noindent
Finally we have the optimisation criteria (criteria 10) to minimise the number of boat changes. This is presented in (\ref{eq22}) and (\ref{eq23}) below.

%
% optimisation criteria 10
%
\begin{flalign}
& totalBoatChanges = \sum_{i=0}^{n-1} s_{i}.totalChange  \label{eq22} \\
& minimise(totalBoatChanges) \label{eq23}
\end{flalign}

Figure \ref{schedChanges} gives a pictorial view of the model, using the 7 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots. Again, top right, we give the schedule actually produced.  Middle left we have the $match$ array and at the bottom the $time$ array. Above the $match$ array we have the $modMatch$ array. The yellow arrows show the channeling between parts of the model.

\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats. The schedule is reproduced top right. On the right we have the 7 skippers, on top left the $modMatch$ array, at the bottom $time$ and middle left the $match$ array. The yellow arrows signify channeling between parts of the model.}
\label{schedChanges} 
\end{figure}

The decision variables are $time_{0}$ to $time_{t-1}$, i.e. for each time slot we decide what match takes place. A symmetry break is made at the top of search by forcing the first round to contain the matches (0,1), (2,3), ... i.e. $\forall_{i \in [0..m-1]} ~ match_{2.i,2i+1} = i$. The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.

\subsection{Stage 2 and 3: minimising imbalance and renaming skippers}
Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance. Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e. $totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a zero/one variable $position_{i,j}$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e. in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via (\ref{imbA}) for each position, as the absolute amount of over or under expected presence in a given postion. Finally, (\ref{imbB}) we compute the maximum imbalance over all positions for this skipper.

\begin{flalign}
& \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} \in \{0,1\} \label{posA} \\
& \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} = 1 \iff \sigma.timeSlot_{m.j+i} \geq 0 \label{posB} \\
& \forall_{i \in [0..m-1]} ~ imbalance_{i} = |\frac{n-1}{m} - \sum_{j=0}{f-1} position_{i,j}| \label{imbA} \\
& \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

\noindent
We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision variables are $time_{0}$ to $time_{t-1}$ and the same symmetry breaking is imposed at top of search.

\begin{flalign}
& \forall_{i \in [0..n-1]} ~ imbalance_{i} = \sigma_{i}.maxImbalance \label{balAllA} \\
& maxImbalance = maximum(imbalance) \label{balAllB} \\
& minimise(maxImbalance) \label{balAllC}
\end{flalign}

\noindent
Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round of the last flight to be (0,1), satisfying criteria 9. This is a simple linear process. The schedule produced for 7 skippers and 6 boats is shown in Table \ref{tab2}.

\begin{table}[h]
%\vspace{-0.2cm}
\begin{center}
\begin{tabular}{cc} \\ 
flight & matches \\ \hline
0 & (0,6) (2,3) (4,5) \\
1 & (0,2) (4,1) (6,5) \\
2 & (2,1) (0,5) (6,3) \\
3 & (5,1) (0,3) (6,4) \\
4 & (3,5) (6,1) (2,4) \\
5 & (3,1) (0,4) (2,5) \\
6 & (3,4) (6,2) (0,1) \\ \hline
\end{tabular}
\end{center}
\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights. Result of stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of imbalance is skipper $\sigma_{0}$ with 2 matches in position 0 (first), 3 in position 1 and 1 (mid) in position 2 (last). Perfect balance would be 2 matches in each position, only achieved by skipper 2.}
\label{tab2}
\end{table}

\subsection{Stage 4: orienting matches}
The final stage, stage 4, orients skippers within matches, such that they are either port (red) or starboard (green). This is done to satisfy criteria 2 and 3, 5 and 8. A sketch of the constraint model is given with a supporting diagram, Figure \ref{oriented}.  A sequence of zero/one constrained integer variables, of length $n-1$, is produced for each skipper. These correspond to the sequence of skippers they meet in matches. For example, taking the schedule in Table \ref{tab2}, skipper $\sigma_{2}$ meets skippers in the following order: 3,0,1,4,5,6 and skipper $\sigma_{5}$ in the order: 4,6,0,1,3,2. Therefore, skipper $\sigma_{2}$'s 4$^{th}$ variable must take a different value from $\sigma_{5}$ 5$^{th}$ variable. There are summation constraints on each skipper to enforce criteria 2 and 3 (equal number of port and starboard matches). Criteria 8 is enforced by posting constraints such that in a match ($\sigma_{i},\sigma_{j}$) where $|i - j| = 1$ the higher indexed skipper (lower ranked) is on the port side. A deterministic finite automata constraint is posted for criteria 5 (restricting sequences of port and starboard assignments).

In Figure \ref{oriented} port is red and starboard green. The sequence of zero/one variables for each skipper is shown on the left. Bottom right is the dfa, and top right is the final schedule produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. Three days cpu time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The schedule presented here is new, not appearing in the ISAF World Sailing Umpire's Manual.
\begin{figure}[h]
\centering
\includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
%\vspace{-35mm}
\caption{A pictorial representation of the orientation process, stage 4. Top right is the actual oriented schedule. Below that is the dfa to satisfy criteria 5. On the left is the zero/one variables, a row representing a skippers sequence of competitors. An edge between variables corresponds to a matched pair, that must take different values. Bottom right is a sketch by one of the authors.}
\label{oriented} 
\end{figure}

\section{Sample Schedules}

\subsection{Discussion}

\section{Conclusion}

\section*{Acknowledgments}
We would like to thank our parents, God and all his angels.
\coffee{2}

\bibliographystyle{plain}
\bibliography{bib}

\end{document}

### 2015-03-23 paper.tex
added in criteria 5 to list
fixed equation 27

@@
 The third stage satisfies criteria 9, and is a simple translation of the schedule produced in stage 2.
-The final stage, stage 4, orients skippers within matches to address criteria 2, 3 and 8.
+The final stage, stage 4, orients skippers within matches to address criteria 2, 3, 5 and 8.
 
@@
 & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} = 1 \iff \sigma.timeSlot_{m.j+i} \geq 0 \label{posB} \\
-& \forall_{i \in [0..m-1]} ~ imbalance_{i} = |\frac{n-1}{m} - \sum_{j=0}{f-1} position_{i,j}| \label{imbA} \\
+& \forall_{i \in [0..m-1]} ~ imbalance_{i} = |\frac{n-1}{m} - \sum_{j=0}^{f-1} position_{i,j}| \label{imbA} \\
 & \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}

### 2015-03-23 paper.tex
Change fox to duck
dog is a pig

@@
 
-\title{Constructing Sailing Match Race Schedules: round robin pairing lists}
+\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
 \titlerunning{Match Race Scheduling}
@@
 \begin{abstract} 
-The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog. The quick brown fox jumped over the lazy dog.
+The quick brown duck jumped over the lazy pig. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog.
 \end{abstract}

### 2015-03-24 paper.tex
Title case
Authors and emails

@@
 %\toctitle{}
-\author{Ciaran McCreesh, Craig MacDonald, Alice Miller and Patrick Prosser}
-\authorrunning{McCreesh, MacDonald, Miller and Prosser}
+\author{Patrick Prosser \and Ciaran McCreesh\thanks{This work was supported by
+the Engineering and Physical Sciences Research Council [grant number
+EP/K503058/1]}\and Craig MacDonald \and Alice Miller}
+\institute{University of Glasgow, Glasgow, Scotland \\ \email{patrick.prosser@glasgow.ac.uk}}
+\authorrunning{Prosser, McCreesh, MacDonald, Miller}
 \tocauthor{Patrick Prosser}
-\institute{School of Computing Science, University of Glasgow, fname.sname@glasgow.ac.uk}
 \maketitle

### 2015-03-24 paper.tex
Spaces and line widths
Grammar

@@
 %\toctitle{}
-\author{Patrick Prosser \and Ciaran McCreesh\thanks{This work was supported by
-the Engineering and Physical Sciences Research Council [grant number
-EP/K503058/1]}\and Craig MacDonald \and Alice Miller}
+\author{Craig MacDonald \and Ciaran McCreesh \and Alice Miller \and Patrick Prosser}
 \institute{University of Glasgow, Glasgow, Scotland \\ \email{patrick.prosser@glasgow.ac.uk}}
-\authorrunning{Prosser, McCreesh, MacDonald, Miller}
-\tocauthor{Patrick Prosser}
+\authorrunning{MacDonald, McCreesh, Miller, Prosser}
 \maketitle
@@
 \section{Problem Definition: round robin pairing lists}
-In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section M.2 Recommended Criteria for Round Robin Pairing Lists,  the following criteria are given:
+In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section
+M.2 Recommended Criteria for Round Robin Pairing Lists, the following criteria
+are given:
 
@@
 \item Each skipper sails against each other skipper once.
-\item When there is an even number of flights, each skipper has the same number of port and starboard assignments. 
-\item When there is an odd number of flights, the first half of the skippers will have one more starboard assignment.
-\item No skipper in the last match of a flight should be in the first match of the next flight. 
-\item No skipper should have more than two consecutive port or starboard assignments.
-\item Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
-\item In flights with five or more matches no skipper should be in the next-to-last match in a flight and then in the first match of the next flight.
-\item If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper (i.e. \#1 will be starboard against \#2, \#3 will be starboard against \#4).
+\item When there is an even number of flights, each skipper has the same number
+    of port and starboard assignments.
+\item When there is an odd number of flights, the first half of the skippers
+    will have one more starboard assignment.
+\item No skipper in the last match of a flight should be in the first match of
+    the next flight.
+\item No skipper should have more than two consecutive port or starboard
+    assignments.
+\item Each skipper should be assigned to match 1, match 2, etc. in a flight as
+    equally as possible.
+\item In flights with five or more matches no skipper should be in the
+    next-to-last match in a flight and then in the first match of the next
+    flight.
+\item If possible, a skipper should be starboard when meeting the nearest
+    lowest ranked skipper (i.e. \#1 will be starboard against \#2, \#3 will be
+    starboard against \#4).
 \item Close ranked skippers meet in the last flight.
@@
 
-\noindent
-Note: criteria 10, 11 and 12 only apply when there are less boats than skippers
+Note that criteria 10, 11 and 12 only apply when there are fewer boats than
+skippers.
 

### 2015-03-24 paper.tex
Spacing and line widths
Commas and the like

@@
 \section{The Constraint Models}
-The schedules are produced in 4 stages.
-The first stage produces a schedule that respects criteria 1, 4, 11 and 12 and minimises criteria 10 (boat changes).
-The second stage constructs a schedule that respects criteria 1,4,11,12 again and has criteria 10 as a hard constraint generated from first stage and minimises criteria 6 (balance).
-This results in a schedule that attempts to minimise boat changes \emph{and} balance.
-The third stage satisfies criteria 9, and is a simple translation of the schedule produced in stage 2.
-The final stage, stage 4, orients skippers within matches to address criteria 2, 3, 5 and 8.
 
-We now describe the constraint models and processes used in each stage.
-In the text below we assume there are $n$ skipper and $b$ boats, with $m = b/2$ matches in a flight.
-In total there are $t = n(n-1)/2$ matches and $f = \lceil n(n-1)/m  \rceil$ flights.
-We may use the schedule in Table \ref{tab1}, for 7 skippers and 6 boats, to help illustrate the constraint models.
-Our descriptions of the models omit some minor details, however the models are available to download here (give us a link or something).
+The schedules are produced in four stages. The first stage produces a schedule
+that respects criteria 1, 4, 11 and 12, and minimises criteria 10 (boat
+changes). The second stage constructs a schedule that respects criteria 1, 4,
+11, 12 (again), has criteria 10 as a hard constraint generated from first
+stage, and minimises criteria 6 (balance). This results in a schedule that
+attempts to minimise boat changes \emph{and} balance. The third stage satisfies
+criteria 9, and is a simple translation of the schedule produced in stage 2.
+The final stage, orients skippers within matches to address criteria 2, 3, 5
+and 8.
+
+We now describe the constraint models and processes used in each stage. In the
+text below we assume there are $n$ skipper and $b$ boats, with $m = b/2$
+matches in a flight. In total there are $t = n(n-1)/2$ matches and $f = \lceil
+n(n-1)/m  \rceil$ flights. We may use the schedule in Table \ref{tab1}, for 7
+skippers and 6 boats, to help illustrate the constraint models. Our
+descriptions of the models omit some minor details, however the models are
+available to download here (give us a link or something).
 

### 2015-03-24 paper.tex
Wording

@@
 We now describe the constraint models and processes used in each stage. In the
-text below we assume there are $n$ skipper and $b$ boats, with $m = b/2$
+text below we assume there are $n$ skippers and $b$ boats, with $m = b/2$
 matches in a flight. In total there are $t = n(n-1)/2$ matches and $f = \lceil
-n(n-1)/m  \rceil$ flights. We may use the schedule in Table \ref{tab1}, for 7
+n(n-1)/m  \rceil$ flights. We use the schedule in Table~\ref{tab1}, for 7
 skippers and 6 boats, to help illustrate the constraint models. Our
 descriptions of the models omit some minor details, however the models are
-available to download here (give us a link or something).
+available to download\footnote{?? give us a link to the models}.
 

### 2015-03-24 paper.tex
Grammar

@@
 \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
-Skippers are numbered 0 to 6.
-Note that the order of skippers within a flight are significant as is position within a match (port or starboard).
-This schedule is the result of stages 1 and 2, and has yet to be renumbered and oriented (stages 3 and 4)}
+Skippers are numbered 0 to 6. Note that the order of skippers within a flight
+is significant, as is position within a match (port or starboard). This
+schedule is the result of stages 1 and 2, and has yet to be renumbered and
+oriented (stages 3 and 4).}
 \label{tab1}

### 2015-03-24 paper.tex
Move table
Speeeling

@@
 
-\begin{table}[h]
-%\vspace{-0.2cm}
+\begin{table}[tb]
 \begin{center}
@@
 
-\subsection{Stage 1: minimising boat changes}
-The first thing we model is a skipper.
-A skipper $\sigma$ has a temporal view of his schedulle in the array of constrained integer variables $timeSlot_{0}$ to $timeSlot_{t-1}$ (equation \ref{eq3} below) and a state view in the array of constraint integer variables $state_{0}$ to $state_{f-1}$ (equation \ref{eq4} below), i.e.
-$state_{i}$ is the state of this skipper in flight $i$ and corresponds to timeslots $timeSlot_{i*m}$ to $timeSlot_{m.(i+1)-1}$.
+\subsection{Stage 1: Minimising Boat Changes}
+
+The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
+of his schedule in the array of constrained integer variables $timeSlot_{0}$
+to $timeSlot_{t-1}$ (equation \ref{eq3} below), and a state view in the array of
+constraint integer variables $state_{0}$ to $state_{f-1}$ (equation \ref{eq4}
+below), i.e. $state_{i}$ is the state of this skipper in flight $i$ and
+corresponds to timeslots $timeSlot_{i*m}$ to $timeSlot_{m.(i+1)-1}$.
 

### 2015-03-24 paper.tex
Use [] rather than subscripts

@@
 The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
-of his schedule in the array of constrained integer variables $timeSlot_{0}$
-to $timeSlot_{t-1}$ (equation \ref{eq3} below), and a state view in the array of
-constraint integer variables $state_{0}$ to $state_{f-1}$ (equation \ref{eq4}
-below), i.e. $state_{i}$ is the state of this skipper in flight $i$ and
-corresponds to timeslots $timeSlot_{i*m}$ to $timeSlot_{m.(i+1)-1}$.
+of his schedule in the array of constrained integer variables $timeSlot[0]$
+to $timeSlot[{t-1}]$ (equation \ref{eq3} below), and a state view in the array of
+constraint integer variables $state[0]$ to $state[{f-1}]$ (equation \ref{eq4}
+below), i.e. $state[i]$ is the state of this skipper in flight $i$ and
+corresponds to timeslots $timeSlot[{i*m}]$ to $timeSlot[{m(i+1)-1}]$.
 
@@
 & t = n(n-1)/2 \label{eq2} \\
-& \forall_{\tau \in [0..t-1]} ~ timeSlot_{\tau} \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
-& \forall_{i \in [0..f-1]} ~ state_{i} \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
-& \forall_{i \in [0..f]} ~ state_{i} = FIRST \iff timeSlot_{i.m} \geq 0  \label{eq5} \\
-& \forall_{i \in [0..f]} ~ state_{i} = MID \iff  \exists_{j \in [i.m+1 .. i.m+m-2]} ~ timeSlot_{j} \geq 0  \label{eq6} \\
-& \forall_{i \in [0..f]} ~ state_{i} = LAST \iff timeSlot_{(i+1).m - 1} \geq 0  \label{eq7} \\
-& \forall_{i \in [0..f]} ~ state_{i} = BYE \iff  \forall_{j \in [i.m .. m.(i+1)-1]} ~ timeSlot_{j} = -1  \label{eq8} \\
-& \forall_{i \in [0..f]} ~ state_{i} = END \iff  \forall_{j \in [i.m .. m.(i+1)-1]} ~ timeSlot_{j} = -2  \label{eq9} \\
+& \forall_{\tau \in [0..t-1]} ~ timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
+& \forall_{i \in [0..f-1]} ~ state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
+& \forall_{i \in [0..f]} ~ state[{i}] = FIRST \iff timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
+& \forall_{i \in [0..f]} ~ state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ timeSlot[{j}] \geq 0  \label{eq6} \\
+& \forall_{i \in [0..f]} ~ state[{i}] = LAST \iff timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
+& \forall_{i \in [0..f]} ~ state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ timeSlot[j] = -1  \label{eq8} \\
+& \forall_{i \in [0..f]} ~ state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ timeSlot[j] = -2  \label{eq9} \\
 & globalCardinality(timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
@@
 In (\ref{eq3}) the array $timeSlot$ is defined and in (\ref{eq4}) $state$ is defined.
-If variable $timeSlot_{i} = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$.
-Variable $state_{i}$ gives the state of this skipper in flight $i$.
+If variable $timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$.
+Variable $state[{i}]$ gives the state of this skipper in flight $i$.
 The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{...
@@
 \begin{flalign}
-& \forall_{i \in [0..f-2]} ~ change_{i} \in \{0,1\} \label{eq10} \\
-& \forall_{i \in [0..f-2]} ~ change_{i} = 1 \iff state_{i} = BYE \wedge state_{i+1} \neq BYE \label{eq11} \\
-& totalChange = \sum_{i=0}^{f-2} ~ change_{i} \label{eq12}
+    & \forall_{i \in [0..f-2]} ~ change[{i}] \in \{0,1\} \label{eq10} \\
+    & \forall_{i \in [0..f-2]} ~ change[{i}] = 1 \iff state[{i}] = BYE \wedge state[{i+1}] \neq BYE \label{eq11} \\
+    & totalChange = \sum_{i=0}^{f-2} ~ change[{i}] \label{eq12}
 \end{flalign}
@@
 In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
-match-perspective of the schedule, using a two dimensional array of variables $match$, where $match_{i,j}$ is the time slot that skippers $s_{i}$ and $s_{j}$ meet in a match.
+match-perspective of the schedule, using a two dimensional array of variables $match$, where $match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match.
 Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e.
-$match_{i,j}$ is \emph{exactly} the same constrained variable as $match_{j,i}$.
-Constraint (\ref{eq15}) states that  a match between skippers $s_{i}$ and $s_{j}$ takes place at time $k$ (i.e.
-$match_{i,j} = k$) if and only if  skipper $s_{i}$'s $k^{th}$ time slot is skipper $s_{j}$ and conversely that skipper $s_{j}$'s $k^{th}$ time slot is skipper $s_{i}$.
+$match[{i,j}]$ is \emph{exactly} the same constrained variable as $match[{j,i}]$.
+Constraint (\ref{eq15}) states that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$ (i.e.
+$match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.
 Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e.
-$modMatch_{i,j}$ is the flight in which skippers $s_{i}$ and $s_{j}$ meet for a match.
+$modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match.
 Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights.
-Also, since $modMatch_{i,j} \equiv modMatch_{j,i}$, setting rows to be all different also ensures that columns are all different.
+Also, since $modMatch[{i,j}] \equiv modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.
 
@@
 \begin{flalign}
-& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match_{i,j} \in \{0..t-1\} \label{eq13} \\
-& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match_{j,i} \equiv match_{i,j} \label{eq14} \\
-& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ match_{i,j} = k \iff s_{i}.timeSlot_{k} = j  ~ \wedge ~ s_{j}.timeSlot_{k} = i  \label{eq15} \\
-& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch_{i,j} \in \{0..f-1\} \label{eq16} \\
-& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch_{j,i} \equiv modMatch_{i,j} \label{eq17} \\
-& \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch_{i,j} = \frac{match_{i,j}}{m} \label{eq18} \\
-& \forall_{i \in [0..n-1]} ~ allDifferent(modMatch_{i}) \label{eq19}
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match[{i,j}] \in \{0..t-1\} \label{eq13} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match[{j,i}] \equiv match[{i,j}] \label{eq14} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ match[{i,j}] = k \iff s[{i}].timeSlot[{k}] = j  ~ \wedge ~ s[{j}].timeSlot_{k} = i  \label{eq15} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{i,j}] \in \{0..f-1\} \label{eq16} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{j,i}] \equiv modMatch[{i,j}] \label{eq17} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{i,j}] = \frac{match[{i,j}]}{m} \label{eq18} \\
+    & \forall_{i \in [0..n-1]} ~ allDifferent(modMatch[{i}]) \label{eq19}
 \end{flalign}
@@
 \noindent
-We now take a temporal view (\ref{eq20}), such that $time_{\tau}$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s_{i}$ and $s_{j}$ are in a match, i.e.
+We now take a temporal view (\ref{eq20}), such that $time[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a match, i.e.
 we channel between the match-perspective and the temporal-perspective.
@@
 \begin{flalign}
-& \forall_{\tau \in [0..t-1]} ~ time_{\tau} \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
-& \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time_{\tau} = (i,j) \iff match_{i,j} = \tau \label{eq21}
+    & \forall_{\tau \in [0..t-1]} ~ time[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
+    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff match[{i,j}] = \tau \label{eq21}
 \end{flalign}
@@
 \begin{flalign}
-& totalBoatChanges = \sum_{i=0}^{n-1} s_{i}.totalChange  \label{eq22} \\
+    & totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].totalChange  \label{eq22} \\
 & minimise(totalBoatChanges) \label{eq23}
@@
 
-The decision variables are $time_{0}$ to $time_{t-1}$, i.e.
+The decision variables are $time[{0}]$ to $time[{t-1}]$, i.e.
 for each time slot we decide what match takes place.
@@
 i.e.
-$\forall_{i \in [0..m-1]} ~ match_{2.i,2i+1} = i$.
+$\forall_{i \in [0..m-1]} ~ match[{2.i,2i+1}] = i$.
 The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.
@@
 $totalBoatChanges \leq \beta$.
-For each skipper $\sigma$ we introduce a zero/one variable $position_{i,j}$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.
+For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.
 in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}).
@@
 \begin{flalign}
-& \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} \in \{0,1\} \label{posA} \\
-& \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position_{i,j} = 1 \iff \sigma.timeSlot_{m.j+i} \geq 0 \label{posB} \\
-& \forall_{i \in [0..m-1]} ~ imbalance_{i} = |\frac{n-1}{m} - \sum_{j=0}^{f-1} position_{i,j}| \label{imbA} \\
+    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position[{i,j}] \in \{0,1\} \label{posA} \\
+    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position[{i,j}] = 1 \iff \sigma.timeSlot[{m.j+i}] \geq 0 \label{posB} \\
+    & \forall_{i \in [0..m-1]} ~ imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} position[{i,j}]| \label{imbA} \\
 & \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
@@
 We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}).
-As before, the decision variables are $time_{0}$ to $time_{t-1}$ and the same symmetry breaking is imposed at top of search.
+As before, the decision variables are $time[{0}]$ to $time[{t-1}]$ and the same symmetry breaking is imposed at top of search.
 
 \begin{flalign}
-& \forall_{i \in [0..n-1]} ~ imbalance_{i} = \sigma_{i}.maxImbalance \label{balAllA} \\
+    & \forall_{i \in [0..n-1]} ~ imbalance[{i}] = \sigma[{i}].maxImbalance \label{balAllA} \\
 & maxImbalance = maximum(imbalance) \label{balAllB} \\
@@
 It has 6 boat changes and imbalance 1.
-An example of imbalance is skipper $\sigma_{0}$ with 2 matches in position 0 (first), 3 in position 1 and 1 (mid) in position 2 (last).
+An example of imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in position 1 and 1 (mid) in position 2 (last).
 Perfect balance would be 2 matches in each position, only achieved by skipper 2.}
@@
 These correspond to the sequence of skippers they meet in matches.
-For example, taking the schedule in Table \ref{tab2}, skipper $\sigma_{2}$ meets skippers in the following order: 3,0,1,4,5,6 and skipper $\sigma_{5}$ in the order: 4,6,0,1,3,2.
-Therefore, skipper $\sigma_{2}$'s 4$^{th}$ variable must take a different value from $\sigma_{5}$ 5$^{th}$ variable.
+For example, taking the schedule in Table \ref{tab2}, skipper $\sigma[{2}]$ meets skippers in the following order: 3,0,1,4,5,6 and skipper $\sigma[{5}]$ in the order: 4,6,0,1,3,2.
+Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from $\sigma[{5}]$ 5$^{th}$ variable.
 There are summation constraints on each skipper to enforce criteria 2 and 3 (equal number of port and starboard matches).
-Criteria 8 is enforced by posting constraints such that in a match ($\sigma_{i},\sigma_{j}$) where $|i - j| = 1$ the higher indexed skipper (lower ranked) is on the port side.
+Criteria 8 is enforced by posting constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$ the higher indexed skipper (lower ranked) is on the port side.
 A deterministic finite automata constraint is posted for criteria 5 (restricting sequences of port and starboard assignments).

### 2015-03-24 paper.tex
Liberal use of mathit

@@
 \usepackage{amsopn}
+
+\newcommand{\match}{\mathit{match}}
+\newcommand{\timeSlot}{\mathit{timeSlot}}
+\newcommand{\state}{\mathit{state}}
+\newcommand{\change}{\mathit{change}}
+\newcommand{\totalChange}{\mathit{totalChange}}
+\newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
+\newcommand{\modMatch}{\mathit{modMatch}}
+\newcommand{\position}{\mathit{position}}
+\newcommand{\imbalance}{\mathit{imbalance}}
+\newcommand{\maxImbalance}{\mathit{maxImbalance}}
+
+\newcommand{\globalCardinality}{\mathrm{globalCardinality}}
+\newcommand{\allDifferent}{\mathrm{allDifferent}}
 
@@
 The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
-of his schedule in the array of constrained integer variables $timeSlot[0]$
-to $timeSlot[{t-1}]$ (equation \ref{eq3} below), and a state view in the array of
-constraint integer variables $state[0]$ to $state[{f-1}]$ (equation \ref{eq4}
-below), i.e. $state[i]$ is the state of this skipper in flight $i$ and
-corresponds to timeslots $timeSlot[{i*m}]$ to $timeSlot[{m(i+1)-1}]$.
+of his schedule in the array of constrained integer variables $\timeSlot[0]$
+to $\timeSlot[{t-1}]$ (equation \ref{eq3} below), and a state view in the array of
+constraint integer variables $\state[0]$ to $\state[{f-1}]$ (equation \ref{eq4}
+below), i.e. $\state[i]$ is the state of this skipper in flight $i$ and
+corresponds to timeslots $\timeSlot[{i*m}]$ to $\timeSlot[{m(i+1)-1}]$.
 
@@
 & t = n(n-1)/2 \label{eq2} \\
-& \forall_{\tau \in [0..t-1]} ~ timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
-& \forall_{i \in [0..f-1]} ~ state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
-& \forall_{i \in [0..f]} ~ state[{i}] = FIRST \iff timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
-& \forall_{i \in [0..f]} ~ state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ timeSlot[{j}] \geq 0  \label{eq6} \\
-& \forall_{i \in [0..f]} ~ state[{i}] = LAST \iff timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
-& \forall_{i \in [0..f]} ~ state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ timeSlot[j] = -1  \label{eq8} \\
-& \forall_{i \in [0..f]} ~ state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ timeSlot[j] = -2  \label{eq9} \\
-& globalCardinality(timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
+& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
+& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
+& \globalCardinality(\timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
 \end{flalign}
 
-In (\ref{eq3}) the array $timeSlot$ is defined and in (\ref{eq4}) $state$ is defined.
-If variable $timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$.
-Variable $state[{i}]$ gives the state of this skipper in flight $i$.
+In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is defined.
+If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$.
+Variable $\state[{i}]$ gives the state of this skipper in flight $i$.
 The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{...
@@
 
-A global cardinality constraint \cite{globCard} is then imposed on the array $timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e.
+A global cardinality constraint \cite{globCard} is then imposed on the array $\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e.
 $\{0 ..
@@
 1\}$).
-The $state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first).
+The $\state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first).
 In addition, we have the rule that if a skipper has finished his matches in flight $i$ (i.e.
 END) then he has finished his matches in flight $i+1$ (and so on).
-These criteria are imposed on the $state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.
+These criteria are imposed on the $\state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.
 
 The constraints above are shown pictorially in Figure \ref{skipper5}, and corresponds to skipper 5 in the Table \ref{tab1} schedule.
-The $state$ array is presented as coloured boxes, and below that the $timeSlot$ array.
+The $\state$ array is presented as coloured boxes, and below that the $\timeSlot$ array.
 The arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}).
-The $state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE.
+The $\state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE.
 The schedule of Table \ref{tab1} is reproduced with the matches for skipper 5 emboldened.
@@
 A boat change occurs when a skipper has been in a BYE state in flight $i$ and then is in a match in the next flight $i+1$.
-This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $totalChange$ (\ref{eq12}).
+This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).
 
 \begin{flalign}
-    & \forall_{i \in [0..f-2]} ~ change[{i}] \in \{0,1\} \label{eq10} \\
-    & \forall_{i \in [0..f-2]} ~ change[{i}] = 1 \iff state[{i}] = BYE \wedge state[{i+1}] \neq BYE \label{eq11} \\
-    & totalChange = \sum_{i=0}^{f-2} ~ change[{i}] \label{eq12}
+    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
+    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = BYE \wedge \state[{i+1}] \neq BYE \label{eq11} \\
+    & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
 \end{flalign}
@@
 In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
-match-perspective of the schedule, using a two dimensional array of variables $match$, where $match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match.
+match-perspective of the schedule, using a two dimensional array of variables $\match$, where $\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match.
 Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e.
-$match[{i,j}]$ is \emph{exactly} the same constrained variable as $match[{j,i}]$.
+$\match[{i,j}]$ is \emph{exactly} the same constrained variable as $\match[{j,i}]$.
 Constraint (\ref{eq15}) states that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$ (i.e.
-$match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.
+$\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.
 Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e.
-$modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match.
+$\modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match.
 Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights.
-Also, since $modMatch[{i,j}] \equiv modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.
+Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.
 
@@
 \begin{flalign}
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match[{i,j}] \in \{0..t-1\} \label{eq13} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~match[{j,i}] \equiv match[{i,j}] \label{eq14} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ match[{i,j}] = k \iff s[{i}].timeSlot[{k}] = j  ~ \wedge ~ s[{j}].timeSlot_{k} = i  \label{eq15} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{i,j}] \in \{0..f-1\} \label{eq16} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{j,i}] \equiv modMatch[{i,j}] \label{eq17} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ modMatch[{i,j}] = \frac{match[{i,j}]}{m} \label{eq18} \\
-    & \forall_{i \in [0..n-1]} ~ allDifferent(modMatch[{i}]) \label{eq19}
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~\match[{i,j}] \in \{0..t-1\} \label{eq13} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~\match[{j,i}] \equiv \match[{i,j}] \label{eq14} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ \match[{i,j}] = k \iff s[{i}].\timeSlot[{k}] = j  ~ \wedge ~ s[{j}].\timeSlot[{k}] = i  \label{eq15} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{i,j}] \in \{0..f-1\} \label{eq16} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{j,i}] \equiv \modMatch[{i,j}] \label{eq17} \\
+    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{i,j}] = \frac{\match[{i,j}]}{m} \label{eq18} \\
+    & \forall_{i \in [0..n-1]} ~ \allDifferent(\modMatch[{i}]) \label{eq19}
 \end{flalign}
@@
     & \forall_{\tau \in [0..t-1]} ~ time[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
-    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff match[{i,j}] = \tau \label{eq21}
+    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
 \end{flalign}
@@
 \begin{flalign}
-    & totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].totalChange  \label{eq22} \\
-& minimise(totalBoatChanges) \label{eq23}
+    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChange  \label{eq22} \\
+& minimise(\totalBoatChanges) \label{eq23}
 \end{flalign}
@@
 Again, top right, we give the schedule actually produced.
-Middle left we have the $match$ array and at the bottom the $time$ array.
-Above the $match$ array we have the $modMatch$ array.
+Middle left we have the $\match$ array and at the bottom the $time$ array.
+Above the $match$ array we have the $\modMatch$ array.
 The yellow arrows show the channeling between parts of the model.
@@
 The schedule is reproduced top right.
-On the right we have the 7 skippers, on top left the $modMatch$ array, at the bottom $time$ and middle left the $match$ array.
+On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $time$ and middle left the $\match$ array.
 The yellow arrows signify channeling between parts of the model.}
@@
 i.e.
-$\forall_{i \in [0..m-1]} ~ match[{2.i,2i+1}] = i$.
+$\forall_{i \in [0..m-1]} ~ \match[{2.i,2i+1}] = i$.
 The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.
@@
 Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e.
-$totalBoatChanges \leq \beta$.
+$\totalBoatChanges \leq \beta$.
 For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.
@@
 \begin{flalign}
-    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position[{i,j}] \in \{0,1\} \label{posA} \\
-    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.position[{i,j}] = 1 \iff \sigma.timeSlot[{m.j+i}] \geq 0 \label{posB} \\
-    & \forall_{i \in [0..m-1]} ~ imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} position[{i,j}]| \label{imbA} \\
-& \sigma.maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
+    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
+    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
+    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]| \label{imbA} \\
+& \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
 \end{flalign}
@@
 \begin{flalign}
-    & \forall_{i \in [0..n-1]} ~ imbalance[{i}] = \sigma[{i}].maxImbalance \label{balAllA} \\
-& maxImbalance = maximum(imbalance) \label{balAllB} \\
-& minimise(maxImbalance) \label{balAllC}
+    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
+& \maxImbalance = maximum(\imbalance) \label{balAllB} \\
+& minimise(\maxImbalance) \label{balAllC}
 \end{flalign}

### 2015-03-24 paper.tex
Formatting tweaks

@@
 
-In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is defined.
-If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with skipper $k$ at time $i$.
-Variable $\state[{i}]$ gives the state of this skipper in flight $i$.
-The skipper can be in a match in the first time slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{...
-actually, not first and not last.} (\ref{eq6}) or in the last time slot of the flight (\ref{eq7}).
-If all time slots in a flight are equal to -1 then the skipper is in a bye (\ref{eq8}) and if all time slots in a flight are equal to -2 then the skipper has finished all his matches (\ref{eq9}).
+In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is
+defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is
+in a match with skipper $k$ at time $i$. Variable $\state[{i}]$ gives the state
+of this skipper in flight $i$. The skipper can be in a match in the first time
+slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{\ldots
+actually, not first and not last.} (\ref{eq6}), or in the last time slot of the
+flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the
+skipper is in a bye (\ref{eq8}), and if all time slots in a flight are equal to
+-2 then the skipper has finished all his matches (\ref{eq9}).
 

### 2015-03-24 paper.tex
Formatting
Wording

@@
 
-A global cardinality constraint \cite{globCard} is then imposed on the array $\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all other skippers (i.e.
-$\{0 ..
-n-1 \} \setminus \{\sigma\}$) once (i.e.
-$\{1 ..
-1\}$) and once only (i.e.
-$\{1 ..
-1\}$).
-The $\state$ variables are then used to impose match race criteria 4 (if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first).
-In addition, we have the rule that if a skipper has finished his matches in flight $i$ (i.e.
-END) then he has finished his matches in flight $i+1$ (and so on).
-These criteria are imposed on the $\state$ variables via a deterministic finite automata (dfa) constraint \cite{Pesant04}.
+A global cardinality constraint \cite{globCard} is then imposed on the array
+$\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all
+other skippers (i.e. $\{0 \ldots n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 \ldots
+1\}$) and once only (i.e. $\{1 \ldots 1\}$). The $\state$ variables are then used
+to impose match race criteria 4 (if last in flight $i$ then not first in flight
+$i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$)
+and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In
+addition, we have the rule that if a skipper has finished his matches in flight
+$i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on).
+These criteria are imposed on the $\state$ variables via a deterministic finite
+automata (DFA) constraint \cite{Pesant04}.
 
-The constraints above are shown pictorially in Figure \ref{skipper5}, and corresponds to skipper 5 in the Table \ref{tab1} schedule.
-The $\state$ array is presented as coloured boxes, and below that the $\timeSlot$ array.
-The arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}).
-The $\state$ array is coloured with green representing LAST, yellow for MID, blue for FIRST, red for LAST and (not shown) pink for BYE.
-The schedule of Table \ref{tab1} is reproduced with the matches for skipper 5 emboldened.
-To the right of the schedule is schema for the dfa.
-Coloured arc represent a transition from one state to another.
-The dfa is encoded as a set of transition objects $\langle q_{i},\iota,q_{j} \rangle$ where a transition is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$.
-In addition we specify the accepting states, being all states except the start state (white) and bye state (pink).
+The constraints above are shown pictorially in Figure~\ref{skipper5}, and
+corresponds to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
+is presented as coloured boxes, and below that is the $\timeSlot$ array. The
+arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The
+$\state$ array is coloured with green representing LAST, yellow for MID, blue
+for FIRST, red for LAST and (not shown) pink for BYE. The schedule of
+Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
+the right of the schedule is schema for the DFA. Coloured arcs represent a
+transition from one state to another. The DFA is encoded as a set of transition
+objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
+state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we
+specify the accepting states, which are all states except the start state
+(white) and the bye state (pink).
 

### 2015-03-24 paper.tex
Change GCC phrasing

@@
 
-\newcommand{\globalCardinality}{\mathrm{globalCardinality}}
+\newcommand{\eachOccursExactlyOnce}{\mathrm{eachOccursExactlyOnce}}
 \newcommand{\allDifferent}{\mathrm{allDifferent}}
@@
 & \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
-& \globalCardinality(\timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
+& \eachOccursExactlyOnce(\timeSlot, \{0, \ldots, n-1\} \setminus \{\sigma\}\})
 \end{flalign}
@@
 
-A global cardinality constraint \cite{globCard} is then imposed on the array
-$\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all
-other skippers (i.e. $\{0 \ldots n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 \ldots
-1\}$) and once only (i.e. $\{1 \ldots 1\}$). The $\state$ variables are then used
-to impose match race criteria 4 (if last in flight $i$ then not first in flight
-$i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$)
-and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In
-addition, we have the rule that if a skipper has finished his matches in flight
-$i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on).
-These criteria are imposed on the $\state$ variables via a deterministic finite
-automata (DFA) constraint \cite{Pesant04}.
+We must then ensure that each skipper $\sigma$ is in a match with all other
+skippers $\{0, \ldots, n-1\} \setminus \{sigma\}$. This may be done by imposing
+a global cardinality constraint \cite{globCard} on the array $\timeSlot$. The
+$\state$ variables are then used to impose match race criteria 4 (if last in
+flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$
+then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then
+flight $i$ is not first). In addition, we have the rule that if a skipper has
+finished his matches in flight $i$ (i.e. END) then he has finished his matches
+in flight $i+1$ (and so on).  These criteria are imposed on the $\state$
+variables via a deterministic finite automata (DFA) constraint \cite{Pesant04}.
 

### 2015-03-24 paper.tex
Formatting for START etc

@@
 \newcommand{\maxImbalance}{\mathit{maxImbalance}}
+
+\newcommand{\START}{\textnormal{\textsc{Start}}}
+\newcommand{\FIRST}{\textnormal{\textsc{First}}}
+\newcommand{\MID}{\textnormal{\textsc{Mid}}}
+\newcommand{\LAST}{\textnormal{\textsc{Last}}}
+\newcommand{\END}{\textnormal{\textsc{End}}}
+\newcommand{\BYE}{\textnormal{\textsc{Bye}}}
 
@@
 & \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
-& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
+& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{eq4} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = \FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = \MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = \LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = \BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
+& \forall_{i \in [0..f]} ~ \state[{i}] = \END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
 & \eachOccursExactlyOnce(\timeSlot, \{0, \ldots, n-1\} \setminus \{\sigma\}\})
@@
 arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The
-$\state$ array is coloured with green representing LAST, yellow for MID, blue
-for FIRST, red for LAST and (not shown) pink for BYE. The schedule of
+$\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue
+for $\FIRST$, red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of
 Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
@@
 
-A boat change occurs when a skipper has been in a BYE state in flight $i$ and then is in a match in the next flight $i+1$.
+A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$ and then is in a match in the next flight $i+1$.
 This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).
@@
     & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
-    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = BYE \wedge \state[{i+1}] \neq BYE \label{eq11} \\
+    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
     & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
@@
 \caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey timeslots.
-The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state START in white, FIRST in blue, MID in yellow, LAST in green, BYE in pink and END in red.}
+The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}
 \label{skipper5}

### 2015-03-24 paper.tex
Total changes, plural
Figure layout
Formatting

@@
 \newcommand{\change}{\mathit{change}}
-\newcommand{\totalChange}{\mathit{totalChange}}
+\newcommand{\totalChanges}{\mathit{totalChanges}}
 \newcommand{\totalBoatChanges}{\mathit{totalBoatChanges}}
@@
 
-A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$ and then is in a match in the next flight $i+1$.
-This is encoded using the array of zero/one variables (\ref{eq10}) and constraint (\ref{eq11}), and accumulated into $\totalChange$ (\ref{eq12}).
+A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$
+and then is in a match in the next flight $i+1$. This is encoded using the
+array of zero/one variables \ref{eq10}, and the constraint (\ref{eq11}), and
+accumulated into $\totalChanges$ (\ref{eq12}).
 
@@
     & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
-    & \totalChange = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
+    & \totalChanges = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
 \end{flalign}
 
-%\vspace{-6mm}
-\begin{figure}[h]
+\begin{figure}[tb]
 \centering
 \includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
-\vspace{-25mm}
-\caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey timeslots.
-The schedule for skipper 5 is in bold and the deterministic finite automata for criteria 4, 11 and 12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}
+\caption{A pictorial representation of a skipper (skipper 5) with multicoloured
+state and grey timeslots. The schedule for skipper 5 is in bold and the
+deterministic finite automata for criteria 4, 11 and 12 is drawn with state
+$\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
+in pink and $\END$ in red.}
 \label{skipper5}
@@
 
-\noindent
-We are now in a position to model criteria 1 (each skipper sails against every other skipper) and optimisation criteria 10 (minimise boat changes).
-In (\ref{eq13}), (\ref{eq14})  and (\ref{eq15}) we present a
-match-perspective of the schedule, using a two dimensional array of variables $\match$, where $\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a match.
-Only the half above the diagonal is represented and the lower half is made up of exactly the same variables, i.e.
-$\match[{i,j}]$ is \emph{exactly} the same constrained variable as $\match[{j,i}]$.
-Constraint (\ref{eq15}) states that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$ (i.e.
-$\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time slot is skipper $s[{i}]$.
-Constraints (\ref{eq16}), (\ref{eq17})  and (\ref{eq18}) then convert this from time slots to flights, i.e.
-$\modMatch[{i,j}]$ is the flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match.
-Finally, constraint (\ref{eq19}) ensures that each skipper's match occurs in different flights.
-Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows to be all different also ensures that columns are all different.
+We are now in a position to model criteria 1 (each skipper sails against every
+other skipper) and optimisation criteria 10 (minimise boat changes).  In
+\ref{eq13}, \ref{eq14} and \ref{eq15} we present a match perspective of the
+schedule, using a two dimensional array of variables $\match$, where
+$\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a
+match. Only the half above the diagonal is represented, and the lower half is
+made up of exactly the same variables, i.e. $\match[{i,j}]$ is \emph{exactly}
+the same constrained variable as $\match[{j,i}]$. Constraint \ref{eq15} states
+that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$
+(i.e. $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time
+slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time
+slot is skipper $s[{i}]$).  Constraints \ref{eq16}, \ref{eq17} and \ref{eq18}
+then convert this from time slots to flights, i.e.  $\modMatch[{i,j}]$ is the
+flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally,
+constraint \ref{eq19} ensures that each skipper's match occurs in different
+flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows
+to be all different also ensures that columns are all different.
 
@@
 \begin{flalign}
-    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChange  \label{eq22} \\
+    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChanges  \label{eq22} \\
 & minimise(\totalBoatChanges) \label{eq23}

### 2015-03-24 paper.tex
mathit for time

@@
 \newcommand{\maxImbalance}{\mathit{maxImbalance}}
+\newcommand{\timeVar}{\mathit{time}}
 
@@
 
-\noindent
-We now take a temporal view (\ref{eq20}), such that $time[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a match, i.e.
-we channel between the match-perspective and the temporal-perspective.
+We now take a temporal view (\ref{eq20}), such that $\timeVar[{\tau}]$ is a pair
+$(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a
+match, i.e. we channel between the match-perspective and the
+temporal-perspective.
 %
@@
 \begin{flalign}
-    & \forall_{\tau \in [0..t-1]} ~ time[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
-    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ time[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
+    & \forall_{\tau \in [0..t-1]} ~ \timeVar[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
+    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \timeVar[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
 \end{flalign}
@@
 Again, top right, we give the schedule actually produced.
-Middle left we have the $\match$ array and at the bottom the $time$ array.
+Middle left we have the $\match$ array and at the bottom the $\timeVar$ array.
 Above the $match$ array we have the $\modMatch$ array.
@@
 The schedule is reproduced top right.
-On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $time$ and middle left the $\match$ array.
+On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $\timeVar$ and middle left the $\match$ array.
 The yellow arrows signify channeling between parts of the model.}
@@
 
-The decision variables are $time[{0}]$ to $time[{t-1}]$, i.e.
+The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$, i.e.
 for each time slot we decide what match takes place.
@@
 We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}).
-As before, the decision variables are $time[{0}]$ to $time[{t-1}]$ and the same symmetry breaking is imposed at top of search.
+As before, the decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
 

### 2015-03-24 paper.tex
Formatting

@@
 
-\noindent
-Finally we have the optimisation criteria (criteria 10) to minimise the number of boat changes. This is presented in (\ref{eq22}) and (\ref{eq23}) below.
+Finally we have the optimisation criteria (criteria 10) to minimise the number
+of boat changes. This is presented in \ref{eq22} and \ref{eq23} below.
 

### 2015-03-24 paper.tex
Layout
Backslash after i.e.

@@
 \item If possible, a skipper should be starboard when meeting the nearest
-    lowest ranked skipper (i.e. \#1 will be starboard against \#2, \#3 will be
+    lowest ranked skipper (i.e.\ \#1 will be starboard against \#2, \#3 will be
     starboard against \#4).
@@
 constraint integer variables $\state[0]$ to $\state[{f-1}]$ (equation \ref{eq4}
-below), i.e. $\state[i]$ is the state of this skipper in flight $i$ and
+below), i.e.\ $\state[i]$ is the state of this skipper in flight $i$ and
 corresponds to timeslots $\timeSlot[{i*m}]$ to $\timeSlot[{m(i+1)-1}]$.
@@
 flight $i$ is not first). In addition, we have the rule that if a skipper has
-finished his matches in flight $i$ (i.e. END) then he has finished his matches
+finished his matches in flight $i$ (i.e.\ $\END$) then he has finished his matches
 in flight $i+1$ (and so on).  These criteria are imposed on the $\state$
@@
 match. Only the half above the diagonal is represented, and the lower half is
-made up of exactly the same variables, i.e. $\match[{i,j}]$ is \emph{exactly}
+made up of exactly the same variables, i.e.\ $\match[{i,j}]$ is \emph{exactly}
 the same constrained variable as $\match[{j,i}]$. Constraint \ref{eq15} states
 that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$
-(i.e. $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time
+(i.e.\ $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time
 slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time
 slot is skipper $s[{i}]$).  Constraints \ref{eq16}, \ref{eq17} and \ref{eq18}
-then convert this from time slots to flights, i.e.  $\modMatch[{i,j}]$ is the
+then convert this from time slots to flights, i.e.\ $\modMatch[{i,j}]$ is the
 flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally,
@@
 $(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a
-match, i.e. we channel between the match-perspective and the
+match, i.e.\ we channel between the match-perspective and the
 temporal-perspective.
@@
 
-Figure \ref{schedChanges} gives a pictorial view of the model, using the 7 skipper and 6 boat problem.
-On the right we have the 7 skippers with their states and time slots.
-Again, top right, we give the schedule actually produced.
-Middle left we have the $\match$ array and at the bottom the $\timeVar$ array.
-Above the $match$ array we have the $\modMatch$ array.
-The yellow arrows show the channeling between parts of the model.
+Figure \ref{schedChanges} gives a pictorial view of the model, using the 7
+skipper and 6 boat problem. On the right we have the 7 skippers with their
+states and time slots. Again, top right, we give the schedule actually
+produced.  Middle left we have the $\match$ array and at the bottom the
+$\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The
+yellow arrows show the channeling between parts of the model.
 
-\begin{figure}[h]
+\begin{figure}[tb]
 \centering
 \includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
-%\vspace{-35mm}
-\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats.
-The schedule is reproduced top right.
-On the right we have the 7 skippers, on top left the $\modMatch$ array, at the bottom $\timeVar$ and middle left the $\match$ array.
-The yellow arrows signify channeling between parts of the model.}
+\caption{A pictorial representation of the entire model of the schedule for 7
+skippers and 6 boats. The schedule is reproduced top right. On the right we
+have the 7 skippers, on top left the $\modMatch$ array, at the bottom
+$\timeVar$ and middle left the $\match$ array. The yellow arrows signify
+channeling between parts of the model.}
 \label{schedChanges}
@@
 
-The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$, i.e.
-for each time slot we decide what match takes place.
-A symmetry break is made at the top of search by forcing the first round to contain the matches (0,1), (2,3), ...
-i.e.
-$\forall_{i \in [0..m-1]} ~ \match[{2.i,2i+1}] = i$.
-The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and last flight skipper 1.
+The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$, i.e.\ for each
+time slot we decide what match takes place. A symmetry break is made at the top
+of search by forcing the first round to contain the matches $(0,1), (2,3), \ldots$,
+i.e.\ $\forall_{i \in [0 \ldots m-1]} ~ \match[{2i,2i+1}] = i$. The schedule
+presented has 6 boat changes: there are no boat changes in flight 0 (first
+flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat
+change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and
+last flight skipper 1.
 
@@
 Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance.
-Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e.
-$\totalBoatChanges \leq \beta$.
-For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.
-in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}).
+Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e.\ $\totalBoatChanges \leq \beta$.
+For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.\ in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}).
 Imbalance is then computed via (\ref{imbA}) for each position, as the absolute amount of over or under expected presence in a given postion.

### 2015-03-24 paper.tex
Title case

@@
 
-\subsection{Stage 2 and 3: minimising imbalance and renaming skippers}
+\subsection{Stages 2 and 3: Minimising Imbalances and Renaming Skippers}
+
 Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance.

### 2015-03-24 paper.tex
speeling

@@
 
-Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance.
-Assuming the first stage produced a schedule with $\beta$ boat changes we post this as a hard constraint in stage 2, i.e.\ $\totalBoatChanges \leq \beta$.
-For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if skipper $\sigma$ is in a match in time $m.j + i$, i.e.\ in the $i^{th}$ match of the  $j^{th}$ flight (\ref{posB}).
-Imbalance is then computed via (\ref{imbA}) for each position, as the absolute amount of over or under expected presence in a given postion.
-Finally, (\ref{imbB}) we compute the maximum imbalance over all positions for this skipper.
+Having produced a schedule that minimises boat changes, we then minimise
+criteria 6, imbalance. Assuming the first stage produced a schedule with
+$\beta$ boat changes we post this as a hard constraint in stage 2, i.e.\
+$\totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a
+zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if
+skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
+of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via
+(\ref{imbA}) for each position, as the absolute amount of over or under
+expected presence in a given position. Finally, (\ref{imbB}) we compute the
+maximum imbalance over all positions for this skipper.
 

### 2015-03-24 paper.tex
Speeling
Roman minimise

@@
 \newcommand{\allDifferent}{\mathrm{allDifferent}}
+\newcommand{\minimise}{\mathrm{minimise}}
 
@@
     & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChanges  \label{eq22} \\
-& minimise(\totalBoatChanges) \label{eq23}
+& \minimise(\totalBoatChanges) \label{eq23}
 \end{flalign}
@@
 
-\noindent
-We then capture the maxmum imbalance over all skippers (\ref{balAllA} and \ref{balAllB}) and minimise this (\ref{balAllC}).
-As before, the decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
+We then capture the maximum imbalance over all skippers (\ref{balAllA} and
+\ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision
+variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry
+breaking is imposed at top of search.
 
@@
 & \maxImbalance = maximum(\imbalance) \label{balAllB} \\
-& minimise(\maxImbalance) \label{balAllC}
+& \minimise(\maxImbalance) \label{balAllC}
 \end{flalign}

### 2015-03-24 paper.tex
Layout

@@
 
-\noindent
-Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round of the last flight to be (0,1), satisfying criteria 9.
-This is a simple linear process.
-The schedule produced for 7 skippers and 6 boats is shown in Table \ref{tab2}.
+Stage 3 then takes as input the schedule produced in stage 2 and renames
+skippers in the last round of the last flight to be (0,1), satisfying criteria
+9. This is a simple linear process. The schedule produced for 7 skippers and 6
+boats is shown in Table~\ref{tab2}.
 
-\begin{table}[h]
-%\vspace{-0.2cm}
+\begin{table}[tb]
 \begin{center}
@@
 \end{center}
-\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights.
-Result of stages 1, 2, and 3.
-It has 6 boat changes and imbalance 1.
-An example of imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in position 1 and 1 (mid) in position 2 (last).
-Perfect balance would be 2 matches in each position, only achieved by skipper 2.}
+\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights. Result of
+stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of
+imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in
+position 1 and 1 (mid) in position 2 (last). Perfect balance would be 2 matches
+in each position, only achieved by skipper 2.}
 \label{tab2}

### 2015-03-24 paper.tex
Title case
Formatting

@@
 
-\subsection{Stage 4: orienting matches}
-The final stage, stage 4, orients skippers within matches, such that they are either port (red) or starboard (green).
-This is done to satisfy criteria 2 and 3, 5 and 8.
-A sketch of the constraint model is given with a supporting diagram, Figure \ref{oriented}.
-A sequence of zero/one constrained integer variables, of length $n-1$, is produced for each skipper.
-These correspond to the sequence of skippers they meet in matches.
-For example, taking the schedule in Table \ref{tab2}, skipper $\sigma[{2}]$ meets skippers in the following order: 3,0,1,4,5,6 and skipper $\sigma[{5}]$ in the order: 4,6,0,1,3,2.
-Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from $\sigma[{5}]$ 5$^{th}$ variable.
-There are summation constraints on each skipper to enforce criteria 2 and 3 (equal number of port and starboard matches).
-Criteria 8 is enforced by posting constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$ the higher indexed skipper (lower ranked) is on the port side.
-A deterministic finite automata constraint is posted for criteria 5 (restricting sequences of port and starboard assignments).
+\subsection{Stage 4: Orienting Matches}
+
+The final stage, stage 4, orients skippers within matches, such that they are
+either port (red) or starboard (green). This is done to satisfy criteria 2 and
+3, 5 and 8. A sketch of the constraint model is given with a supporting
+diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained integer
+variables, of length $n-1$, is produced for each skipper. These correspond to
+the sequence of skippers they meet in matches. For example, taking the schedule
+in Table~\ref{tab2}, skipper $\sigma[{2}]$ meets skippers in order:
+3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order 4,6,0,1,3,2.  Therefore,
+skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
+$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each
+skipper to enforce criteria 2 and 3 (equal number of port and starboard
+matches). Criteria 8 is enforced by posting constraints such that in a match
+($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$, the higher indexed skipper
+(lower ranked) is on the port side. A DFA constraint is posted for criteria 5
+(restricting sequences of port and starboard assignments).
 

### 2015-03-24 paper.tex
Remove some unused packages
Better absolute value formatting

@@
 \usepackage{url}
-\usepackage{graphics}
 \usepackage{graphicx}
-\usepackage[all]{xy}
 \usepackage{float}
 \usepackage{listings}
-\usepackage{lipsum}
-
 \usepackage[ruled,vlined]{algorithm2e}
-\usepackage{alltt}
-\urldef{\mailsa}\path|pat@dcs.gla.ac.uk|
-\newcommand{\keywords}[1]{\par\addvspace\baselineskip
-\noindent\keywordname\enspace\ignorespaces#1}
-\newlength{\halftextwidth}
-\setlength{\halftextwidth}{0.47\textwidth}
-\usepackage{multicol}
-\usepackage{listings}
-\usepackage{url}
+\usepackage{mathtools}
 \usepackage{coffee2}
-%\usepackage{amsthm}
-%\newtheorem*{definition}{Definition}#
-\usepackage{amsopn}
 
@@
 \newcommand{\minimise}{\mathrm{minimise}}
+
+\DeclarePairedDelimiter\abs{\lvert}{\rvert}
 
@@
     & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
-    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = |\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]| \label{imbA} \\
+    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{imbA} \\
 & \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
@@
 matches). Criteria 8 is enforced by posting constraints such that in a match
-($\sigma[{i}],\sigma[{j}]$) where $|i - j| = 1$, the higher indexed skipper
+($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher indexed skipper
 (lower ranked) is on the port side. A DFA constraint is posted for criteria 5

### 2015-03-24 paper.tex
Formatting

@@
 
-In Figure \ref{oriented} port is red and starboard green.
-The sequence of zero/one variables for each skipper is shown on the left.
-Bottom right is the dfa, and top right is the final schedule produced from stages 1 to 4.
-The schedule has 6 boat changes and a maximum imbalance of 1.
-Three days cpu time was devoted to stages 1 and 2.
-Stages 3 and 4 completed in 15 milliseconds.
-The schedule presented here is new, not appearing in the ISAF World Sailing Umpire's Manual.
-\begin{figure}[h]
+In Figure~\ref{oriented}, port is red and starboard green. The sequence of
+zero/one variables for each skipper is shown on the left. Bottom right is the
+DFA, and top right is the final schedule produced from stages 1 to 4. The
+schedule has 6 boat changes and a maximum imbalance of 1. Three days CPU time
+was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
+schedule presented here is new, not appearing in the ISAF World Sailing
+Umpire's Manual.
+
+\begin{figure}[tb]
 \centering
 \includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
-%\vspace{-35mm}
-\caption{A pictorial representation of the orientation process, stage 4.
-Top right is the actual oriented schedule.
-Below that is the dfa to satisfy criteria 5.
-On the left is the zero/one variables, a row representing a skippers sequence of competitors.
-An edge between variables corresponds to a matched pair, that must take different values.
-Bottom right is a sketch by one of the authors.}
+\caption{A pictorial representation of the orientation process, stage 4. Top
+right is the actual oriented schedule. Below that is the dfa to satisfy
+criteria 5. On the left is the zero/one variables, a row representing a
+skippers sequence of competitors. An edge between variables corresponds to a
+matched pair, that must take different values. Bottom right is a sketch by one
+of the authors.}
 \label{oriented}

### 2015-03-24 paper.tex
Oxford comma
Roman maximum

@@
 \newcommand{\minimise}{\mathrm{minimise}}
+\newcommand{\maximum}{\mathrm{maximum}}
 
@@
     & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{imbA} \\
-& \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
+    & \sigma.\maxImbalance = \maximum(\sigma.imbalance)  \label{imbB}
 \end{flalign}
@@
     & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
-& \maxImbalance = maximum(\imbalance) \label{balAllB} \\
+& \maxImbalance = \maximum(\imbalance) \label{balAllB} \\
 & \minimise(\maxImbalance) \label{balAllC}
@@
 \section*{Acknowledgments}
-We would like to thank our parents, God and all his angels.
+We would like to thank our parents, God, and all his angels.
 \coffee{2}

### 2015-03-24 paper.tex
Title case

@@
 
-\section{Problem Definition: round robin pairing lists}
+\section{Problem Definition: Round Robin Pairing Lists}
+
 In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section

### 2015-03-24 paper.tex
Quote title

@@
 
-In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section
+In the ISAF ``International Umpire's and Match Racing Manual'' \cite{isaf}, section
 M.2 Recommended Criteria for Round Robin Pairing Lists, the following criteria

### 2015-03-24 paper.tex
Move apostrophe

--- 2015-03-24 paper.tex
@@
 
-In the ISAF International Umpire's and Match Racing Manual \cite{isaf}, section
+In the ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
 M.2 Recommended Criteria for Round Robin Pairing Lists, the following criteria

### 2015-03-24 paper.tex
Comma
Hyphen

@@
     equally as possible.
-\item In flights with five or more matches no skipper should be in the
+\item In flights with five or more matches, no skipper should be in the
     next-to-last match in a flight and then in the first match of the next
@@
     starboard against \#4).
-\item Close ranked skippers meet in the last flight.
+\item Close-ranked skippers meet in the last flight.
 \item Minimize the number of boat changes.

### 2015-03-24 paper.tex
UK spelling
Better looking table

@@
 \usepackage{mathtools}
+\usepackage[rightcaption]{sidecap}
+\usepackage{multicol}
+\usepackage{booktabs}
 \usepackage{coffee2}
@@
 \DeclarePairedDelimiter\abs{\lvert}{\rvert}
+
+\sidecaptionvpos{table}{c}
 
@@
 \item Close-ranked skippers meet in the last flight.
-\item Minimize the number of boat changes.
+\item Minimise the number of boat changes.
 \item Skippers in the last match of a flight do not change boats.
@@
 
-\begin{table}[tb]
-\begin{center}
-\begin{tabular}{cc} \\
-flight & matches \\ \hline
-0 & (0,1) (2,3) (4,5)  \\
-1 & (0,2) (4,6) (1,5)  \\
-2 & (2,6) (0,5) (1,3)  \\
-3 & (5,6) (0,3) (1,4)  \\
-4 & (3,5) (1,6) (2,4)  \\
-5 & (3,6) (0,4) (2,5)  \\
-6 & (3,4) (1,2) (0,6)  \\ \hline
+\begin{SCtable}[2.0][tb]
+    \begin{tabular}{c@{\hspace{1.5em}}ccc}
+        \toprule
+        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+        0 & (0,1) & (2,3) & (4,5) \\
+        1 & (0,2) & (4,6) & (1,5) \\
+        2 & (2,6) & (0,5) & (1,3) \\
+        3 & (5,6) & (0,3) & (1,4) \\
+        4 & (3,5) & (1,6) & (2,4) \\
+        5 & (3,6) & (0,4) & (2,5) \\
+        6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
     \end{tabular}
-\end{center}
     \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
@@
         schedule is the result of stages 1 and 2, and has yet to be renumbered and
-oriented (stages 3 and 4).}
-\label{tab1}
-\end{table}
+        oriented (stages 3 and 4).} \label{tab1}
+\end{SCtable}
 

### 2015-03-24 paper.tex
Use showframe for now
Don't muck around with page numbers
Extra comma
Major layout tweaking

@@
 
+% \usepackage{showframe}
+
 \usepackage{amssymb}
-\usepackage{amsmath}
+\usepackage[fleqn]{amsmath}
 \usepackage{url}
@@
 \usepackage{booktabs}
+\usepackage{framed}
 \usepackage{coffee2}
@@
 \newcommand{\allDifferent}{\mathrm{allDifferent}}
+\newcommand{\validStateSequence}{\mathrm{validStateSequence}}
 \newcommand{\minimise}{\mathrm{minimise}}
@@
 
+\newcommand\nldots{\,\hbox to 0.8em{.\hss.\hss.}\,}
+
 \sidecaptionvpos{table}{c}
 
-\pagestyle{plain}
 \begin{document}
@@
 criteria 9, and is a simple translation of the schedule produced in stage 2.
-The final stage, orients skippers within matches to address criteria 2, 3, 5
+The final stage orients skippers within matches to address criteria 2, 3, 5
 and 8.
@@
 The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
-of his schedule in the array of constrained integer variables $\timeSlot[0]$
-to $\timeSlot[{t-1}]$ (equation \ref{eq3} below), and a state view in the array of
-constraint integer variables $\state[0]$ to $\state[{f-1}]$ (equation \ref{eq4}
-below), i.e.\ $\state[i]$ is the state of this skipper in flight $i$ and
-corresponds to timeslots $\timeSlot[{i*m}]$ to $\timeSlot[{m(i+1)-1}]$.
+of his schedule in the array of constrained integer variables $\timeSlot[0]$ to
+$\timeSlot[{t-1}]$ (\eqref{var:timeSlot} below), and a state view in the array
+of constraint integer variables $\state[0]$ to $\state[{f-1}]$
+(\eqref{var:state} below), i.e.\ $\state[i]$ is the state of this skipper in
+flight $i$ and corresponds to timeslots $\timeSlot[{i*m}]$ to
+$\timeSlot[{m(i+1)-1}]$.
 
-\begin{flalign}
-& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
-& t = n(n-1)/2 \label{eq2} \\
-& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
-& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{eq4} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = \FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = \MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = \LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = \BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
-& \forall_{i \in [0..f]} ~ \state[{i}] = \END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
-& \eachOccursExactlyOnce(\timeSlot, \{0, \ldots, n-1\} \setminus \{\sigma\}\})
-\end{flalign}
+\begin{figure}
+\setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
+\begin{framed}
+\begin{align}
+    &f = \lceil n(n-1)/m  \rceil \label{var:f} \tag{V1} \\
+    &t = n(n-1)/2 \label{var:t} \tag{V2} \\
+    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V3} \\
+    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V4} \\
+    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
+    &\begin{alignedat}{3}
+    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m+1 \nldots i \cdot m+m-2\} : \timeSlot[{j}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i+1)m - 1}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -1 \\
+    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -2
+    \end{alignedat} \nonumber \\
+&\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
+&\validStateSequence(\state) \label{C3} \tag{C3}
+\end{align}
+\end{framed}
+\caption{A skipper-oriented model. A copy of these variables and constraints is
+created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
+the number of matches.}
+\end{figure}
 
-In (\ref{eq3}) the array $\timeSlot$ is defined and in (\ref{eq4}) $\state$ is
-defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is
-in a match with skipper $k$ at time $i$. Variable $\state[{i}]$ gives the state
-of this skipper in flight $i$. The skipper can be in a match in the first time
-slot in the flight (\ref{eq5}), or in the middle of the flight\footnote{\ldots
-actually, not first and not last.} (\ref{eq6}), or in the last time slot of the
-flight (\ref{eq7}). If all time slots in a flight are equal to -1 then the
-skipper is in a bye (\ref{eq8}), and if all time slots in a flight are equal to
--2 then the skipper has finished all his matches (\ref{eq9}).
+In \eqref{var:timeSlot} the array $\timeSlot$ is defined and in
+\eqref{var:state}, $\state$ is defined. If variable $\timeSlot[{i}] = k$ and $k
+\geq 0$ then this skipper is in a match with skipper~$k$ at time~$i$. Variable
+$\state[{i}]$ gives the state of this skipper in flight~$i$. The cases in
+\eqref{C1} say that a skipper can be in a match in the first time slot in the
+flight, or in the middle of the flight\footnote{\ldots actually, not first and
+not last.}, or in the last time slot of the flight. Alternatively, if all time
+slots in a flight are equal to $-1$ then the skipper is in a bye, and if all time
+slots in a flight are equal to $-2$ then the skipper has finished all his
+matches.
 
 We must then ensure that each skipper $\sigma$ is in a match with all other
-skippers $\{0, \ldots, n-1\} \setminus \{sigma\}$. This may be done by imposing
-a global cardinality constraint \cite{globCard} on the array $\timeSlot$. The
-$\state$ variables are then used to impose match race criteria 4 (if last in
-flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$
-then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then
-flight $i$ is not first). In addition, we have the rule that if a skipper has
-finished his matches in flight $i$ (i.e.\ $\END$) then he has finished his matches
-in flight $i+1$ (and so on).  These criteria are imposed on the $\state$
-variables via a deterministic finite automata (DFA) constraint \cite{Pesant04}.
+skippers $\{0, \nldots, n-1\} \setminus \{\sigma\}$. This is \eqref{C2}, which
+may be implemented by imposing a global cardinality constraint \cite{globCard}
+on the array $\timeSlot$.
+
+The $\state$ variables are then used to impose match race criteria 4 (if last
+in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight
+$i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye
+then flight $i$ is not first).  These criteria are imposed by \eqref{C3}, which
+is a deterministic finite automata (DFA) constraint \cite{Pesant04}.  This
+constraint also ensures that if a skipper has finished his matches in flight
+$i$ (i.e.\ $\END$) then he has finished his matches in flight $i+1$ (and so
+on).
 
@@
 is presented as coloured boxes, and below that is the $\timeSlot$ array. The
-arrows represent the channeling constraints (\ref{eq5}) to (\ref{eq9}). The
+arrows represent the channeling constraints \eqref{C1}. The
 $\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue
@@
 time slot we decide what match takes place. A symmetry break is made at the top
-of search by forcing the first round to contain the matches $(0,1), (2,3), \ldots$,
-i.e.\ $\forall_{i \in [0 \ldots m-1]} ~ \match[{2i,2i+1}] = i$. The schedule
+of search by forcing the first round to contain the matches $(0,1), (2,3), \nldots$,
+i.e.\ $\forall_{i \in [0 \nldots m-1]} ~ \match[{2i,2i+1}] = i$. The schedule
 presented has 6 boat changes: there are no boat changes in flight 0 (first

### 2015-03-24 paper.tex
cdot for multiply

@@
 (\eqref{var:state} below), i.e.\ $\state[i]$ is the state of this skipper in
-flight $i$ and corresponds to timeslots $\timeSlot[{i*m}]$ to
+flight $i$ and corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
 $\timeSlot[{m(i+1)-1}]$.

### 2015-03-24 paper.tex
f and t aren't really variables

@@
 \begin{align}
-    &f = \lceil n(n-1)/m  \rceil \label{var:f} \tag{V1} \\
-    &t = n(n-1)/2 \label{var:t} \tag{V2} \\
-    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V3} \\
-    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V4} \\
+    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
+    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
     &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
@@
 created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
-the number of matches.}
+the number of matches in a flight. The number of flights is $f = \lceil
+n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}
 \end{figure}

### 2015-03-25 paper.tex
Introduce model slightly differently

@@
 
-The first thing we model is a skipper. A skipper $\sigma$ has a temporal view
-of his schedule in the array of constrained integer variables $\timeSlot[0]$ to
-$\timeSlot[{t-1}]$ (\eqref{var:timeSlot} below), and a state view in the array
-of constraint integer variables $\state[0]$ to $\state[{f-1}]$
-(\eqref{var:state} below), i.e.\ $\state[i]$ is the state of this skipper in
-flight $i$ and corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
+The first thing we model, in Figure~\ref{model:skipper}, is a skipper. Each
+skipper $\sigma$ has a temporal view of his schedule in the array of
+constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state
+view in the array of constraint integer variables $\state[0]$ to
+$\state[{f-1}]$. The state of this skipper in flight $i$ is found in
+$\state[i]$, and this corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
 $\timeSlot[{m(i+1)-1}]$.
@@
 the number of matches in a flight. The number of flights is $f = \lceil
-n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}
+n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:skipper}
 \end{figure}

### 2015-03-25 paper.tex
Bring skipper constraints together

@@
 
-\begin{figure}
+\begin{figure}[p]
 \setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
@@
     &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
+    \noalign{\smallskip \nonumber}
     &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
@@
     &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
-&\validStateSequence(\state) \label{C3} \tag{C3}
+    &\validStateSequence(\state) \label{C3} \tag{C3} \\
+    \noalign{\bigskip \nonumber}
+    & \forall i \in \{0 \nldots f-2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
+    & \totalChanges \in \mathbb{N} \label{V4} \tag{V4} \\
+    \noalign{\smallskip \nonumber}
+    & \forall i \in \{0 \nldots f-2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label {C4} \tag{C4} \\
+    & \totalChanges = \textstyle\sum_{i=0}^{f-2} \change[{i}] \label{C5} \tag{C5}
 \end{align}
@@
 and then is in a match in the next flight $i+1$. This is encoded using the
-array of zero/one variables \ref{eq10}, and the constraint (\ref{eq11}), and
-accumulated into $\totalChanges$ (\ref{eq12}).
-
-\begin{flalign}
-    & \forall_{i \in [0..f-2]} ~ \change[{i}] \in \{0,1\} \label{eq10} \\
-    & \forall_{i \in [0..f-2]} ~ \change[{i}] = 1 \iff \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label{eq11} \\
-    & \totalChanges = \sum_{i=0}^{f-2} ~ \change[{i}] \label{eq12}
-\end{flalign}
+array of zero/one variables \eqref{V3}, and the constraint \eqref{C4}, and
+accumulated into $\totalChanges$ (\ref{V4},~\ref{C5}).
 

### 2015-03-25 paper.tex
Model all on one page

@@
 
-The first thing we model, in Figure~\ref{model:skipper}, is a skipper. Each
-skipper $\sigma$ has a temporal view of his schedule in the array of
-constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state
-view in the array of constraint integer variables $\state[0]$ to
+The first thing we model, in the first half of Figure~\ref{model:stage1}, is a
+skipper. Each skipper $\sigma$ has a temporal view of his schedule in the array
+of constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a
+state view in the array of constraint integer variables $\state[0]$ to
 $\state[{f-1}]$. The state of this skipper in flight $i$ is found in
@@
 \begin{figure}[p]
-\setlength{\mathindent}{0pt}\setlength{\abovedisplayskip}{0pt}\setlength{\belowdisplayskip}{0pt}
+\setlength{\mathindent}{1em}
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+\setlength{\abovecaptionskip}{0pt}
 \begin{framed}
 \begin{align}
-    &\forall \tau \in \{0 \nldots t-1\}: \timeSlot[{\tau}] \in \{-2 \nldots t-1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
-    &\forall i \in \{0 \nldots f-1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
-    \noalign{\smallskip \nonumber}
+    \intertext{A copy of these variables and constraints is created for each skipper $\sigma$:\smallskip}
+    &\forall \tau \in \{0 \nldots t{-}1\}: \timeSlot[{\tau}] \in \{{-}2 \nldots t{-}1\} \setminus \{\sigma\} \label{var:timeSlot} \tag{V1} \\
+    &\forall i \in \{0 \nldots f{-}1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
     &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
@@
     &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
-    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m+1 \nldots i \cdot m+m-2\} : \timeSlot[{j}] \geq 0 \\
-    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i+1)m - 1}] \geq 0 \\
-    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -1 \\
-    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i+1)-1\} : \timeSlot[j] = -2
+    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m{+}1 \nldots i \cdot m{+}m{-}2\} : \timeSlot[{j}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i{+}1)m {-} 1}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}1 \\
+    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}2
     \end{alignedat} \nonumber \\
-    &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n-1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
-    &\validStateSequence(\state) \label{C3} \tag{C3} \\
-    \noalign{\bigskip \nonumber}
-    & \forall i \in \{0 \nldots f-2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
+    &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n{-}1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
+    &\validStateSequence(\state) \label{C3} \tag{C3} \\[0.1cm]
+    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
     & \totalChanges \in \mathbb{N} \label{V4} \tag{V4} \\
-    \noalign{\smallskip \nonumber}
-    & \forall i \in \{0 \nldots f-2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i+1}] \neq \BYE \label {C4} \tag{C4} \\
-    & \totalChanges = \textstyle\sum_{i=0}^{f-2} \change[{i}] \label{C5} \tag{C5}
+    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i{+}1}] \neq \BYE \label {C4} \tag{C4} \\
+    & \totalChanges = \textstyle\sum_{i=0}^{f{-}2} \change[{i}] \label{C5} \tag{C5}
+\end{align}
+\end{framed}\begin{framed}
+\begin{align}
+    \intertext{Match and temporal perspectives:\smallskip}
+    & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} : \nonumber \\
+    & \hspace*{1em} \match[{i,j}] \in \{0..t{-}1\} \tag{V5} \label{V5} \\
+    & \hspace*{1em} \match[{j,i}] \equiv \match[{i,j}] \nonumber \\
+    & \hspace*{1em} \forall k \in \{0 \nldots t{-}1 \} : \nonumber \\
+    & \hspace*{2em} \match[{i,j}] = k \Leftrightarrow \sigma[{i}].\timeSlot[{k}] = j \wedge \sigma[{j}].\timeSlot[{k}] = i \tag{C6} \label{C6} \\[0.1cm]
+    & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} \nonumber : \\
+    & \hspace*{1em} \modMatch[{i,j}] \in \{0..f{-}1\} \label{V6} \tag{V6} \\
+    & \hspace*{1em} \modMatch[{j,i}] \equiv \modMatch[{i,j}] \nonumber  \\
+    & \hspace*{1em} \modMatch[{i,j}] = \match[{i,j}] / m \tag{C7} \label{C7} \\
+    & \forall i \in \{0 \nldots n{-}1 \} : \allDifferent(\modMatch[{i}]) \tag{C8} \label{C8} \\[0.1cm]
+    & \forall \tau \in \{0 \nldots t{-}1 \} : \nonumber \\
+    & \hspace*{1em} \timeVar[{\tau}] \in \{(0,1) \nldots (n{-}2,n{-}1)\} \tag{V7} \label{V7} \\
+    & \hspace*{1em} \forall i \in \{0 \nldots n{-}2\} : \forall  j \in \{ i{+}1 \nldots n{-}1 \} : \timeVar[{\tau}] = (i,j) \Leftrightarrow \match[{i,j}] = \tau \tag{C9} \label{C9} \\[0.1cm]
+    & \totalBoatChanges = \textstyle\sum_{i=0}^{n{-}1} \sigma[{i}].\totalChanges  \label{V8} \tag{V8} \\
+    & \minimise(\totalBoatChanges) \label{C10} \tag{C10}
 \end{align}
 \end{framed}
-\caption{A skipper-oriented model. A copy of these variables and constraints is
-created for each skipper $\sigma$. The number of skippers is $n$, and $m$ is
-the number of matches in a flight. The number of flights is $f = \lceil
-n(n-1)/m  \rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:skipper}
+\caption{Our constraint model, from a skipper perspective (top) and a match and
+temporal perspective (below). The number of skippers is $n$, and $m$ is the
+number of matches in a flight. The number of flights is $f = \lceil n(n-1)/m
+\rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:stage1}
 \end{figure}
@@
 We are now in a position to model criteria 1 (each skipper sails against every
-other skipper) and optimisation criteria 10 (minimise boat changes).  In
-\ref{eq13}, \ref{eq14} and \ref{eq15} we present a match perspective of the
-schedule, using a two dimensional array of variables $\match$, where
-$\match[{i,j}]$ is the time slot that skippers $s[{i}]$ and $s[{j}]$ meet in a
-match. Only the half above the diagonal is represented, and the lower half is
-made up of exactly the same variables, i.e.\ $\match[{i,j}]$ is \emph{exactly}
-the same constrained variable as $\match[{j,i}]$. Constraint \ref{eq15} states
-that  a match between skippers $s[{i}]$ and $s[{j}]$ takes place at time $k$
-(i.e.\ $\match[{i,j}] = k$) if and only if  skipper $s[{i}]$'s $k^{th}$ time
-slot is skipper $s[{j}]$ and conversely that skipper $s[{j}]$'s $k^{th}$ time
-slot is skipper $s[{i}]$).  Constraints \ref{eq16}, \ref{eq17} and \ref{eq18}
-then convert this from time slots to flights, i.e.\ $\modMatch[{i,j}]$ is the
-flight in which skippers $s[{i}]$ and $s[{j}]$ meet for a match. Finally,
-constraint \ref{eq19} ensures that each skipper's match occurs in different
+other skipper) and optimisation criteria 10 (minimise boat changes).  In the
+second half of Figure~\ref{model:stage1} we present a match perspective of the
+schedule, using a two dimensional array of variables $\match$ \eqref{V5}, where
+$\match[{i,j}]$ is the time slot that skippers $\sigma[{i}]$ and $\sigma[{j}]$
+meet in a match. Only the half above the diagonal is represented, and the lower
+half is made up of exactly the same variables, i.e.\ $\match[{i,j}]$ is
+\emph{exactly} the same constrained variable as $\match[{j,i}]$. Constraint
+\eqref{C6} states that  a match between skippers $\sigma[{i}]$ and
+$\sigma[{j}]$ takes place at time $k$ (i.e.\ $\match[{i,j}] = k$) if and only
+if  skipper $\sigma[{i}]$'s $k^{th}$ time slot is skipper $\sigma[{j}]$ and
+conversely that skipper $\sigma[{j}]$'s $k^{th}$ time slot is skipper
+$\sigma[{i}]$). Variables \eqref{V6} and constraints \eqref{C7} then convert
+this from time slots to flights, i.e.\ $\modMatch[{i,j}]$ is the flight in
+which skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet for a match. Finally,
+constraint \eqref{C8} ensures that each skipper's match occurs in different
 flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows
@@
 
-%
-% the match array
-%
-\begin{flalign}
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~\match[{i,j}] \in \{0..t-1\} \label{eq13} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~\match[{j,i}] \equiv \match[{i,j}] \label{eq14} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \forall_{k \in [0..t-1]} ~ \match[{i,j}] = k \iff s[{i}].\timeSlot[{k}] = j  ~ \wedge ~ s[{j}].\timeSlot[{k}] = i  \label{eq15} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{i,j}] \in \{0..f-1\} \label{eq16} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{j,i}] \equiv \modMatch[{i,j}] \label{eq17} \\
-    & \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \modMatch[{i,j}] = \frac{\match[{i,j}]}{m} \label{eq18} \\
-    & \forall_{i \in [0..n-1]} ~ \allDifferent(\modMatch[{i}]) \label{eq19}
-\end{flalign}
-
-We now take a temporal view (\ref{eq20}), such that $\timeVar[{\tau}]$ is a pair
-$(i,j)$, stating that at time $\tau$ skippers $s[{i}]$ and $s[{j}]$ are in a
-match, i.e.\ we channel between the match-perspective and the
-temporal-perspective.
-%
-% one dimensional time and decision variables
-%
-\begin{flalign}
-    & \forall_{\tau \in [0..t-1]} ~ \timeVar[{\tau}] \in \{(0,1) .. (n-2,n-1)\} \label{eq20} \\
-    & \forall_{\tau \in [0 .. t-1]} ~ \forall_{i \in [0..n-2]} ~ \forall_{j \in [i+1..n-1]}  ~ \timeVar[{\tau}] = (i,j) \iff \match[{i,j}] = \tau \label{eq21}
-\end{flalign}
+We now take a temporal view \eqref{V7}, such that $\timeVar[{\tau}]$ is a pair
+$(i,j)$, stating that at time $\tau$ skippers $\sigma[{i}]$ and $\sigma[{j}]$
+are in a match. We channel between the match perspective and the
+temporal perspective using \eqref{C9}.
 
 Finally we have the optimisation criteria (criteria 10) to minimise the number
-of boat changes. This is presented in \ref{eq22} and \ref{eq23} below.
-
-%
-% optimisation criteria 10
-%
-\begin{flalign}
-    & \totalBoatChanges = \sum_{i=0}^{n-1} s[{i}].\totalChanges  \label{eq22} \\
-& \minimise(\totalBoatChanges) \label{eq23}
-\end{flalign}
+of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
 

### 2015-03-25 paper.tex
Compact sums

@@
     & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i{+}1}] \neq \BYE \label {C4} \tag{C4} \\
-    & \totalChanges = \textstyle\sum_{i=0}^{f{-}2} \change[{i}] \label{C5} \tag{C5}
+    & \totalChanges = \textstyle\sum \change \label{C5} \tag{C5}
 \end{align}
@@
     & \hspace*{1em} \forall i \in \{0 \nldots n{-}2\} : \forall  j \in \{ i{+}1 \nldots n{-}1 \} : \timeVar[{\tau}] = (i,j) \Leftrightarrow \match[{i,j}] = \tau \tag{C9} \label{C9} \\[0.1cm]
-    & \totalBoatChanges = \textstyle\sum_{i=0}^{n{-}1} \sigma[{i}].\totalChanges  \label{V8} \tag{V8} \\
+    & \totalBoatChanges = \textstyle\sum \sigma.\totalChanges \label{V8} \tag{V8} \\
     & \minimise(\totalBoatChanges) \label{C10} \tag{C10}

### 2015-03-25 paper.tex
Reorder arithmetic

@@
     &\begin{alignedat}{3}
-    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{i \cdot m}] \geq 0 \\
-    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{i\cdot m{+}1 \nldots i \cdot m{+}m{-}2\} : \timeSlot[{j}] \geq 0 \\
-    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[{(i{+}1)m {-} 1}] \geq 0 \\
-    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}1 \\
-    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{i \cdot m \nldots m \cdot (i{+}1){-}1\} : \timeSlot[j] = {-}2
+    &\hspace*{1em} \state[{i}] = \FIRST &\ &\Leftrightarrow&&\ \timeSlot[{m \cdot i}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \MID   &\ &\Leftrightarrow&&\ \exists j \in \{m \cdot i + 1 \nldots m \cdot (i + 1) - 2\} : \timeSlot[{j}] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \LAST  &\ &\Leftrightarrow&&\ \timeSlot[m \cdot (i + 1) - 1] \geq 0 \\
+    &\hspace*{1em} \state[{i}] = \BYE   &\ &\Leftrightarrow&&\ \forall j \in \{m \cdot i \nldots m \cdot (i + 1) - 1\} : \timeSlot[j] = -1 \\
+    &\hspace*{1em} \state[{i}] = \END   &\ &\Leftrightarrow&&\ \forall j \in \{m \cdot i \nldots m \cdot (i + 1) - 1\} : \timeSlot[j] = -2
     \end{alignedat} \nonumber \\
@@
     & \totalChanges \in \mathbb{N} \label{V4} \tag{V4} \\
-    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i{+}1}] \neq \BYE \label {C4} \tag{C4} \\
+    & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] = 1 \Leftrightarrow \state[{i}] = \BYE \wedge \state[{i + 1}] \neq \BYE \label {C4} \tag{C4} \\
     & \totalChanges = \textstyle\sum \change \label{C5} \tag{C5}

### 2015-03-25 paper.tex
Redraw skipper 5 picture

@@
 \usepackage{framed}
+\usepackage{tikz}
 \usepackage{coffee2}
+
+\usetikzlibrary{shapes, shapes.multipart, arrows, positioning}
 
@@
 \sidecaptionvpos{table}{c}
+
+\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
+\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
+\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
+\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
+\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}
+
+\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
+\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
+\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
+\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
+\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
+\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
+\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
+\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}
 
@@
     \centering
-\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
+    \begin{tikzpicture}
+    \begin{scope}[every node/.style={minimum size=2em,inner sep=1}, xshift=-1cm]
+        \node (DFAS) [draw, circle, fill=white]                     at (0,  0)   { \textsc{S} };
+        \node (DFAF) [draw, circle, fill=uofgcobalt]                at (2,  1.7) { \textsc{F} };
+        \node (DFAM) [draw, circle, fill=uofgsunshine]              at (2,  0)   { \textsc{M} };
+        \node (DFAL) [draw, circle, fill=uofglawn]                  at (2, -1.7) { \textsc{L} };
+        \node (DFAB) [draw, circle, fill=uofgthistle, text=white]   at (4,  0)   { \textsc{B} };
+        \node (DFAE) [draw, circle, fill=uofgpillarbox, text=white] at (6,  0)   { \textsc{E} };
+
+        \draw [->, >=latex, thick] (DFAS) to (DFAF);
+        \draw [->, >=latex, thick] (DFAS) to (DFAM);
+        \draw [->, >=latex, thick] (DFAS) to (DFAL);
+        \draw [->, >=latex, thick] (DFAS) to [out=-25, in=-155] (DFAB);
+
+        \draw [->, >=latex, thick] (DFAF) to [out=60, in=120, looseness=6] (DFAF);
+        \draw [->, >=latex, thick] (DFAF) to [out=-125, in=125] (DFAL);
+        \draw [->, >=latex, thick] (DFAF) to (DFAB);
+        \draw [->, >=latex, thick] (DFAF) to [out=0, in=135] (DFAE);
+
+        \draw [<->, >=latex, thick] (DFAF) to (DFAM);
+
+        \draw [->, >=latex, thick] (DFAM) to [out=60, in=120, looseness=6] (DFAM);
+        \draw [->, >=latex, thick] (DFAM) to [out=-25, in=-155] (DFAE);
+
+        \draw [<->, >=latex, thick] (DFAM) to (DFAB);
+        \draw [<->, >=latex, thick] (DFAM) to (DFAL);
+
+        \draw [->, >=latex, thick] (DFAL) to [out=300, in=240, looseness=6] (DFAL);
+        \draw [->, >=latex, thick] (DFAL) to [out=0, in=225] (DFAE);
+
+        \draw [<->, >=latex, thick] (DFAL) to (DFAB);
+
+        \draw [->, >=latex, thick] (DFAB) to [out=30, in=-30, looseness=6] (DFAB);
+
+        \draw [->, >=latex, thick] (DFAE) to [out=30, in=-30, looseness=6] (DFAE);
+    \end{scope}
+
+    \begin{scope}[yshift=5.5cm, scale=0.85]
+        \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofglawn,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofglawn,uofgpillarbox}] at (0, 0) {
+            \nodepart[text width=2em, align=center] {one}   \textsc{L}
+            \nodepart[text width=2em, align=center] {two}   \textsc{L}
+            \nodepart[text width=2em, align=center] {three} \textsc{M}
+            \nodepart[text width=2em, align=center] {four}  \textsc{F}
+            \nodepart[text width=2em, align=center] {five}  \textsc{F}
+            \nodepart[text width=2em, align=center] {six}   \textsc{L}
+            \nodepart[text width=2em, align=center, text=white] {seven} \textsc{E}
+        };
+
+        \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+            \nodepart[text width=0.75em, align=center] {one}
+            \nodepart[text width=0.75em, align=center] {two}
+            \nodepart[text width=0.75em, align=center] {three} 4
+        };
+
+        \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+            \nodepart[text width=0.75em, align=center] {one}
+            \nodepart[text width=0.75em, align=center] {two}
+            \nodepart[text width=0.75em, align=center] {three} 1
+        };
+
+        \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+            \nodepart[text width=0.75em, align=center] {one}
+            \nodepart[text width=0.75em, align=center] {two} 0
+            \nodepart[text width=0.75em, align=center] {three}
+        };
+
+        \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+            \nodepart[text width=0.75em, align=center] {one} 6
+            \nodepart[text width=0.75em, align=center] {two}
+            \nodepart[text width=0.75em, align=center] {three}
+        };
+
+        \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+            \nodepart[text width=0.75em, align=center] {one} 3
+            \nodepart[text width=0.75em, align=center] {two}
+            \nodepart[text width=0.75em, align=center] {three}
+        };
+
+        \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+            \nodepart[text width=0.75em, align=center] {one}
+            \nodepart[text width=0.75em, align=center] {two}
+            \nodepart[text width=0.75em, align=center] {three} 2
+        };
+
+        \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+            \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+            \nodepart[text width=0.75em, align=center] {two}
+            \nodepart[text width=0.75em, align=center] {three}
+        };
+
+        \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+        \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+        \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+        \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+        \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+        \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+        \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+    \end{scope}
+
+    \begin{scope}
+        \node at (-3.8, 0) {
+            \begin{minipage}{4cm}
+            \begin{framed}
+                \centering
+                \begin{tabular}{c@{\hspace{3mm}}c@{\hspace{3mm}}c}
+                    (0, 1) & (2, 3) & \textbf{(4, 5)} \\
+                    (0, 2) & (4, 6) & \textbf{(1, 5)} \\
+                    (2, 6) & \textbf{(0, 5)} & (1, 3) \\
+                    \textbf{(5, 6)} & (0, 3) & (1, 4) \\
+                    \textbf{(3, 5)} & (1, 6) & (2, 4) \\
+                    (3, 6) & (0, 4) & \textbf{(2, 5)} \\
+                    (3, 4) & (1, 2) & (0, 6) \\
+                \end{tabular}
+            \end{framed}
+            \end{minipage}
+        };
+    \end{scope}
+
+    \end{tikzpicture}
     \caption{A pictorial representation of a skipper (skipper 5) with multicoloured
@@
         $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
-in pink and $\END$ in red.}
-\label{skipper5}
+    in pink and $\END$ in red.}\label{skipper5}
 \end{figure}

### 2015-03-25 paper.tex
Muck around with DFA description

@@
 then flight $i$ is not first).  These criteria are imposed by \eqref{C3}, which
-is a deterministic finite automata (DFA) constraint \cite{Pesant04}.  This
-constraint also ensures that if a skipper has finished his matches in flight
-$i$ (i.e.\ $\END$) then he has finished his matches in flight $i+1$ (and so
-on).
+is a deterministic finite automata (DFA) constraint \cite{Pesant04}. The
+transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
+represent a transition from one state to another. The DFA is encoded as a set
+of transition objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition
+is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In
+addition we specify the accepting states, which are all states except the start
+state (white) and the bye state (pink).  This constraint also ensures that if a
+skipper has finished his matches in flight $i$ (i.e.\ $\END$) then he has
+finished his matches in flight $i+1$ (and so on).
 
-The constraints above are shown pictorially in Figure~\ref{skipper5}, and
-corresponds to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
+Figure~\ref{skipper5} also shows the skipper-oriented variables and constraints
+corresponding to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
 is presented as coloured boxes, and below that is the $\timeSlot$ array. The
@@
 for $\FIRST$, red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of
-Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened. To
-the right of the schedule is schema for the DFA. Coloured arcs represent a
-transition from one state to another. The DFA is encoded as a set of transition
-objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
-state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In addition we
-specify the accepting states, which are all states except the start state
-(white) and the bye state (pink).
+Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened.
 
@@
     \begin{scope}[yshift=5.5cm, scale=0.85]
+        \node at (-5, 0) { \textbf{ Skipper 5: } };
+
         \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,

### 2015-03-25 paper.tex
Paragraph headings for the model

@@
 
-The first thing we model, in the first half of Figure~\ref{model:stage1}, is a
-skipper. Each skipper $\sigma$ has a temporal view of his schedule in the array
-of constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a
-state view in the array of constraint integer variables $\state[0]$ to
-$\state[{f-1}]$. The state of this skipper in flight $i$ is found in
-$\state[i]$, and this corresponds to timeslots $\timeSlot[{i \cdot m}]$ to
-$\timeSlot[{m(i+1)-1}]$.
+\paragraph{Modelling skippers:} The first thing we model, in the first half of
+Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal
+view of his schedule in the array of constrained integer variables
+$\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state view in the array of
+constraint integer variables $\state[0]$ to $\state[{f-1}]$. The state of this
+skipper in flight $i$ is found in $\state[i]$, and this corresponds to
+timeslots $\timeSlot[{i \cdot m}]$ to $\timeSlot[{m(i+1)-1}]$.
 
@@
 
-The $\state$ variables are then used to impose match race criteria 4 (if last
-in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight
-$i$ then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye
-then flight $i$ is not first).  These criteria are imposed by \eqref{C3}, which
-is a deterministic finite automata (DFA) constraint \cite{Pesant04}. The
-transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
-represent a transition from one state to another. The DFA is encoded as a set
-of transition objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition
-is made from state $q_{i}$ to state $q_{j}$ when encountering input $\iota$. In
-addition we specify the accepting states, which are all states except the start
-state (white) and the bye state (pink).  This constraint also ensures that if a
-skipper has finished his matches in flight $i$ (i.e.\ $\END$) then he has
-finished his matches in flight $i+1$ (and so on).
+\paragraph{State transitions:} The $\state$ variables are then used to impose
+match race criteria 4 (if last in flight $i$ then not first in flight $i+1$),
+criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and
+criteria 12 (if flight $i$ is a bye then flight $i$ is not first).  These
+criteria are imposed by \eqref{C3}, which is a deterministic finite automata
+(DFA) constraint \cite{Pesant04}. The transitions for the DFA are shown
+pictorially in Figure~\ref{skipper5}: arcs represent a transition from one
+state to another. The DFA is encoded as a set of transition objects $\langle
+q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to
+state $q_{j}$ when encountering input $\iota$. In addition we specify the
+accepting states, which are all states except the start state (white) and the
+bye state (pink).  This constraint also ensures that if a skipper has finished
+his matches in flight $i$ (i.e.\ $\END$) then he has finished his matches in
+flight $i+1$ (and so on).
 
@@
 
-A boat change occurs when a skipper has been in a $\BYE$ state in flight $i$
-and then is in a match in the next flight $i+1$. This is encoded using the
-array of zero/one variables \eqref{V3}, and the constraint \eqref{C4}, and
-accumulated into $\totalChanges$ (\ref{V4},~\ref{C5}).
+\paragraph{Boat changes:} A boat change occurs when a skipper has been in a
+$\BYE$ state in flight $i$ and then is in a match in the next flight $i+1$.
+This is encoded using the array of zero/one variables \eqref{V3}, and the
+constraint \eqref{C4}, and accumulated into $\totalChanges$
+(\ref{V4},~\ref{C5}).
 
@@
 
-We are now in a position to model criteria 1 (each skipper sails against every
-other skipper) and optimisation criteria 10 (minimise boat changes).  In the
-second half of Figure~\ref{model:stage1} we present a match perspective of the
-schedule, using a two dimensional array of variables $\match$ \eqref{V5}, where
-$\match[{i,j}]$ is the time slot that skippers $\sigma[{i}]$ and $\sigma[{j}]$
-meet in a match. Only the half above the diagonal is represented, and the lower
-half is made up of exactly the same variables, i.e.\ $\match[{i,j}]$ is
-\emph{exactly} the same constrained variable as $\match[{j,i}]$. Constraint
-\eqref{C6} states that  a match between skippers $\sigma[{i}]$ and
-$\sigma[{j}]$ takes place at time $k$ (i.e.\ $\match[{i,j}] = k$) if and only
-if  skipper $\sigma[{i}]$'s $k^{th}$ time slot is skipper $\sigma[{j}]$ and
-conversely that skipper $\sigma[{j}]$'s $k^{th}$ time slot is skipper
-$\sigma[{i}]$). Variables \eqref{V6} and constraints \eqref{C7} then convert
-this from time slots to flights, i.e.\ $\modMatch[{i,j}]$ is the flight in
-which skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet for a match. Finally,
-constraint \eqref{C8} ensures that each skipper's match occurs in different
-flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows
-to be all different also ensures that columns are all different.
+\paragraph{Match perspective:} We are now in a position to model criteria 1
+(each skipper sails against every other skipper) and optimisation criteria 10
+(minimise boat changes).  In the second half of Figure~\ref{model:stage1} we
+present a match perspective of the schedule, using a two dimensional array of
+variables $\match$ \eqref{V5}, where $\match[{i,j}]$ is the time slot that
+skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet in a match. Only the half above
+the diagonal is represented, and the lower half is made up of exactly the same
+variables, i.e.\ $\match[{i,j}]$ is \emph{exactly} the same constrained
+variable as $\match[{j,i}]$. Constraint \eqref{C6} states that  a match between
+skippers $\sigma[{i}]$ and $\sigma[{j}]$ takes place at time $k$ (i.e.\
+$\match[{i,j}] = k$) if and only if  skipper $\sigma[{i}]$'s $k^{th}$ time slot
+is skipper $\sigma[{j}]$ and conversely that skipper $\sigma[{j}]$'s $k^{th}$
+time slot is skipper $\sigma[{i}]$). Variables \eqref{V6} and constraints
+\eqref{C7} then convert this from time slots to flights, i.e.\
+$\modMatch[{i,j}]$ is the flight in which skippers $\sigma[{i}]$ and
+$\sigma[{j}]$ meet for a match. Finally, constraint \eqref{C8} ensures that
+each skipper's match occurs in different flights. Also, since $\modMatch[{i,j}]
+\equiv \modMatch[{j,i}]$, setting rows to be all different also ensures that
+columns are all different.
 
-We now take a temporal view \eqref{V7}, such that $\timeVar[{\tau}]$ is a pair
-$(i,j)$, stating that at time $\tau$ skippers $\sigma[{i}]$ and $\sigma[{j}]$
-are in a match. We channel between the match perspective and the
-temporal perspective using \eqref{C9}.
+\paragraph{Temporal perspective:} We now take a temporal view \eqref{V7}, such
+that $\timeVar[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers
+$\sigma[{i}]$ and $\sigma[{j}]$ are in a match. We channel between the match
+perspective and the temporal perspective using \eqref{C9}.
 
-Finally we have the optimisation criteria (criteria 10) to minimise the number
-of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
+\paragraph{Optimisation criteria:} Finally we have the optimisation criteria
+(criteria 10) to minimise the number of boat changes. This is handled by
+\eqref{V8} and \eqref{C10}.
 

### 2015-03-25 paper.tex
Use the same table layout
my introduction & section 2

--- 2015-03-25 paper.tex
@@
 \usepackage{framed}
-\usepackage{tikz}
 \usepackage{coffee2}
 
-\usetikzlibrary{shapes, shapes.multipart, arrows, positioning}
+\usepackage{color}
+\newcommand{\todo}[1]{\textcolor{blue}{#1}}
 
@@
 
-\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
-\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
-\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
-\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
-\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}
-
-\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
-\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
-\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
-\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
-\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
-\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
-\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
-\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}
-
 \begin{document}
@@
 %\toctitle{}
-\author{Craig MacDonald \and Ciaran McCreesh \and Alice Miller \and Patrick Prosser}
+\author{Craig Macdonald \and Ciaran McCreesh \and Alice Miller \and Patrick Prosser}
 \institute{University of Glasgow, Glasgow, Scotland \\ \email{patrick.prosser@glasgow.ac.uk}}
-\authorrunning{MacDonald, McCreesh, Miller, Prosser}
+\authorrunning{Macdonald, McCreesh, Miller, Prosser}
 \maketitle
@@
 \begin{abstract} 
-The quick brown duck jumped over the lazy pig. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog.
+\todo{The quick brown duck jumped over the lazy pig. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog.}
 \end{abstract}
 
-\section{Introduction}
-\coffee{1}
+\section{Introduction}\coffee{1}
+Round robin competition scehdules represent a rich area for applications of constraint programming.
+This work describes a particular round robin competition format that arises from sailing, known as match racing.
+In particular, the competitors, known formally as {\em skippers} compete against each other in a series of matches taking place in rounds (known as {\em flights}).
+For a match, each skipper is placed in a boat.
 
-\section{Problem Definition: Round Robin Pairing Lists}
+The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the competiting skippers are scheduled into flights and matches, known as pairing lists.
+Several of these criteria are applicable when the number of skippers exceeds the number of available boats, in which case skippers have to change in and out of boats, and are allowed time in the schedule to check and fine-tune the boat they change into.
 
-In the ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
-M.2 Recommended Criteria for Round Robin Pairing Lists, the following criteria
-are given:
+While the number of boats and skippers involved is typically not numerous (e.g.\ upto 10 of each), the creations of valid schedules satisfying all constraints is unachievable without automation.
+Hence, this paper documents our efforts in automating the creation of valid schedules.
+This is achieved \todo{through ...
+symmettry breaking ...,  etc.
+We believe that the methods detailed here are applicable to other problems (example?), and are of interest to the community.
+}
 
+\todo{Therefore the contributions of this paper are hunner'-fold: TODO}
+
+The remainder of this paper is structured as follows: Section~\ref{sec:definition} provides an overview of the criteria outlined for creating match racing pairing lists; Section~\ref{sec:samples} discusses several sample schedules, while concluding remarks follow in Section~\ref{sec:conclusions}.
+
+\section{Problem Definition: Round Robin Pairing Lists}\label{sec:definition}
+
+In the match racing format of sailing events, the criteria for generated match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
+M.2 Recommended Criteria for Round Robin Pairing Lists. We detail these criteria below.
+
+\begin{framed}
 \begin{enumerate}
 \item Each skipper sails against each other skipper once.
-\item When there is an even number of flights, each skipper has the same number
-    of port and starboard assignments.
-\item When there is an odd number of flights, the first half of the skippers
+\item *When skippers have an even number of matches, they have the same number of port and starboard assignments.
+\item *When skippers have an odd number of matches, the first half of the skippers
     will have one more starboard assignment.
+%\item When there is an even number of flights, each skipper has the same number
+%    of port and starboard assignments.
+%\item When there is an odd number of flights, the first half of the skippers
+%    will have one more starboard assignment.
 \item No skipper in the last match of a flight should be in the first match of
@@
 \end{enumerate}
-
 Note that criteria 10, 11 and 12 only apply when there are fewer boats than
 skippers.
+\end{framed}
 
-\section{The Constraint Models}
+Firstly, we note that we have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}.
+We further outline the key aspects of the criteria, which motivate and permit understanding of our proposal solution.
+
+In particular, the order of matches within a flight are constrained, as well as the order of flights, to permit fair schedules that provide the opportunity for skippers to change boats, etc.
+
+Next, we note that skippers can be ranked prior to an event -- based on their performance in previous events~\footnote{\url{http://www.sailing.org/rankings/match/}} -- which is used to seed the skippers.
+The ordering of skippers within a match signifies their starting position (port or starboard) -- as skippers allocated the starboard starting position gain a small competitive advantage in that match - criteria 8 accomplishes the seedings.
+
+Finally, it can be observed that criteria 10 is ambigious: - this could be interpreted on an schedule basis: i.e.\ to minimise the overall number of changes in the entire pairing list schedule; or alterantively as well as a fair, but minimal number of changes across all skippers.
+In our work, we take the latter viewpoint.
+
+In the following, we detail the constraint models (Section~\ref{sec:models}), while some example schedules are presented in Section~\ref{sec:samples}.
+
+\section{The Constraint Models}\label{sec:models}
 
@@
 \centering
-    \begin{tikzpicture}
-    \begin{scope}[every node/.style={minimum size=2em,inner sep=1}, xshift=-1cm]
-        \node (DFAS) [draw, circle, fill=white]                     at (0,  0)   { \textsc{S} };
-        \node (DFAF) [draw, circle, fill=uofgcobalt]                at (2,  1.7) { \textsc{F} };
-        \node (DFAM) [draw, circle, fill=uofgsunshine]              at (2,  0)   { \textsc{M} };
-        \node (DFAL) [draw, circle, fill=uofglawn]                  at (2, -1.7) { \textsc{L} };
-        \node (DFAB) [draw, circle, fill=uofgthistle, text=white]   at (4,  0)   { \textsc{B} };
-        \node (DFAE) [draw, circle, fill=uofgpillarbox, text=white] at (6,  0)   { \textsc{E} };
-
-        \draw [->, >=latex, thick] (DFAS) to (DFAF);
-        \draw [->, >=latex, thick] (DFAS) to (DFAM);
-        \draw [->, >=latex, thick] (DFAS) to (DFAL);
-        \draw [->, >=latex, thick] (DFAS) to [out=-25, in=-155] (DFAB);
-
-        \draw [->, >=latex, thick] (DFAF) to [out=60, in=120, looseness=6] (DFAF);
-        \draw [->, >=latex, thick] (DFAF) to [out=-125, in=125] (DFAL);
-        \draw [->, >=latex, thick] (DFAF) to (DFAB);
-        \draw [->, >=latex, thick] (DFAF) to [out=0, in=135] (DFAE);
-
-        \draw [<->, >=latex, thick] (DFAF) to (DFAM);
-
-        \draw [->, >=latex, thick] (DFAM) to [out=60, in=120, looseness=6] (DFAM);
-        \draw [->, >=latex, thick] (DFAM) to [out=-25, in=-155] (DFAE);
-
-        \draw [<->, >=latex, thick] (DFAM) to (DFAB);
-        \draw [<->, >=latex, thick] (DFAM) to (DFAL);
-
-        \draw [->, >=latex, thick] (DFAL) to [out=300, in=240, looseness=6] (DFAL);
-        \draw [->, >=latex, thick] (DFAL) to [out=0, in=225] (DFAE);
-
-        \draw [<->, >=latex, thick] (DFAL) to (DFAB);
-
-        \draw [->, >=latex, thick] (DFAB) to [out=30, in=-30, looseness=6] (DFAB);
-
-        \draw [->, >=latex, thick] (DFAE) to [out=30, in=-30, looseness=6] (DFAE);
-    \end{scope}
-
-    \begin{scope}[yshift=5.5cm, scale=0.85]
-        \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
-            rectangle split part fill={uofglawn,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofglawn,uofgpillarbox}] at (0, 0) {
-            \nodepart[text width=2em, align=center] {one}   \textsc{L}
-            \nodepart[text width=2em, align=center] {two}   \textsc{L}
-            \nodepart[text width=2em, align=center] {three} \textsc{M}
-            \nodepart[text width=2em, align=center] {four}  \textsc{F}
-            \nodepart[text width=2em, align=center] {five}  \textsc{F}
-            \nodepart[text width=2em, align=center] {six}   \textsc{L}
-            \nodepart[text width=2em, align=center, text=white] {seven} \textsc{E}
-        };
-
-        \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
-            \nodepart[text width=0.75em, align=center] {one}
-            \nodepart[text width=0.75em, align=center] {two}
-            \nodepart[text width=0.75em, align=center] {three} 4
-        };
-
-        \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
-            \nodepart[text width=0.75em, align=center] {one}
-            \nodepart[text width=0.75em, align=center] {two}
-            \nodepart[text width=0.75em, align=center] {three} 1
-        };
-
-        \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
-            \nodepart[text width=0.75em, align=center] {one}
-            \nodepart[text width=0.75em, align=center] {two} 0
-            \nodepart[text width=0.75em, align=center] {three}
-        };
-
-        \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
-            \nodepart[text width=0.75em, align=center] {one} 6
-            \nodepart[text width=0.75em, align=center] {two}
-            \nodepart[text width=0.75em, align=center] {three}
-        };
-
-        \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
-            \nodepart[text width=0.75em, align=center] {one} 3
-            \nodepart[text width=0.75em, align=center] {two}
-            \nodepart[text width=0.75em, align=center] {three}
-        };
-
-        \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
-            \nodepart[text width=0.75em, align=center] {one}
-            \nodepart[text width=0.75em, align=center] {two}
-            \nodepart[text width=0.75em, align=center] {three} 2
-        };
-
-        \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
-            rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
-            \nodepart[text width=0.75em, align=center] {one} \phantom{1}
-            \nodepart[text width=0.75em, align=center] {two}
-            \nodepart[text width=0.75em, align=center] {three}
-        };
-
-        \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
-        \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
-        \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
-        \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
-        \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
-        \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
-        \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
-    \end{scope}
-
-    \begin{scope}
-        \node at (-3.8, 0) {
-            \begin{minipage}{4cm}
-            \begin{framed}
-                \centering
-                \begin{tabular}{c@{\hspace{3mm}}c@{\hspace{3mm}}c}
-                    (0, 1) & (2, 3) & \textbf{(4, 5)} \\
-                    (0, 2) & (4, 6) & \textbf{(1, 5)} \\
-                    (2, 6) & \textbf{(0, 5)} & (1, 3) \\
-                    \textbf{(5, 6)} & (0, 3) & (1, 4) \\
-                    \textbf{(3, 5)} & (1, 6) & (2, 4) \\
-                    (3, 6) & (0, 4) & \textbf{(2, 5)} \\
-                    (3, 4) & (1, 2) & (0, 6) \\
-                \end{tabular}
-            \end{framed}
-            \end{minipage}
-        };
-    \end{scope}
-
-    \end{tikzpicture}
+\includegraphics[height=10.2cm,width=13.2cm]{skipper5.pdf}
 \caption{A pictorial representation of a skipper (skipper 5) with multicoloured
@@
 $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
-    in pink and $\END$ in red.}\label{skipper5}
+in pink and $\END$ in red.}
+\label{skipper5}
 \end{figure}
@@
 was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
-schedule presented here is new, not appearing in the ISAF World Sailing
-Umpire's Manual.
+schedule presented here is new, not appearing in the example schedules provided in \cite{isaf}.%ISAF World Sailing Umpire's Manual
 
@@
 
-\section{Sample Schedules}
+\section{Sample Schedules}\label{sec:samples}
 
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusions}
 

### 2015-03-25 paper.tex

--- 2015-03-25 paper.tex
@@
 \usepackage{framed}
+\usepackage{coffee2}
 \usepackage{tikz}
-\usepackage{coffee2}
+
+\usepackage{color}
+\newcommand{\todo}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{SCtable}[2.0][tb]
-    \begin{tabular}{c@{\hspace{1.5em}}ccc}
+    \begin{tabular}{c@{\hspace{1em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
         \toprule
@@
         \node (DFAS) [draw, circle, fill=white]                     at (0,  0)   { \textsc{S} };
-        \node (DFAF) [draw, circle, fill=uofgcobalt]                at (2,  1.7) { \textsc{F} };
+        \node (DFAF) [draw, circle, fill=uofgcobalt]                at (2,  1.5) { \textsc{F} };
         \node (DFAM) [draw, circle, fill=uofgsunshine]              at (2,  0)   { \textsc{M} };
-        \node (DFAL) [draw, circle, fill=uofglawn]                  at (2, -1.7) { \textsc{L} };
+        \node (DFAL) [draw, circle, fill=uofglawn]                  at (2, -1.5) { \textsc{L} };
         \node (DFAB) [draw, circle, fill=uofgthistle, text=white]   at (4,  0)   { \textsc{B} };
@@
 
-    \begin{scope}[yshift=5.5cm, scale=0.85]
+    \begin{scope}[yshift=5cm, scale=0.85]
         \node at (-5, 0) { \textbf{ Skipper 5: } };
@@
         \node at (-3.8, 0) {
-            \begin{minipage}{4cm}
-            \begin{framed}
+            \begin{minipage}{4.5cm}
                 \centering
-                \begin{tabular}{c@{\hspace{3mm}}c@{\hspace{3mm}}c}
-                    (0, 1) & (2, 3) & \textbf{(4, 5)} \\
-                    (0, 2) & (4, 6) & \textbf{(1, 5)} \\
-                    (2, 6) & \textbf{(0, 5)} & (1, 3) \\
-                    \textbf{(5, 6)} & (0, 3) & (1, 4) \\
-                    \textbf{(3, 5)} & (1, 6) & (2, 4) \\
-                    (3, 6) & (0, 4) & \textbf{(2, 5)} \\
-                    (3, 4) & (1, 2) & (0, 6) \\
+                \begin{tabular}{c@{\hspace{1em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
+                    \toprule
+                    Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+                    0 & (0,1) & (2,3) & \textbf{(4,5)} \\
+                    1 & (0,2) & (4,6) & \textbf{(1,5)} \\
+                    2 & (2,6) & \textbf{(0,5)} & (1,3) \\
+                    3 & \textbf{(5,6)} & (0,3) & (1,4) \\
+                    4 & \textbf{(3,5)} & (1,6) & (2,4) \\
+                    5 & (3,6) & (0,4) & \textbf{(2,5)} \\
+                    6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
                 \end{tabular}
-            \end{framed}
             \end{minipage}

### 2015-03-25 paper.tex
Colour in table columns
Reorder a bit

@@
 \usepackage{multicol}
+\usepackage{colortbl}
 \usepackage{booktabs}
@@
 \begin{SCtable}[2.0][tb]
-    \begin{tabular}{c@{\hspace{1em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
+    \setlength{\tabcolsep}{3pt}
+    \begin{tabular}{cccc}
         \toprule
@@
                 \centering
-                \begin{tabular}{c@{\hspace{1em}}c@{\hspace{0.5em}}c@{\hspace{0.5em}}c}
+                \setlength{\tabcolsep}{3pt}
+                \setlength{\aboverulesep}{0pt}
+                \setlength{\belowrulesep}{0pt}
+                \setlength{\extrarowheight}{.75ex}
+                \begin{tabular}{c>{\columncolor{uofgcobalt}}c>{\columncolor{uofgsunshine}}c>{\columncolor{uofglawn}}c}
                     \toprule
-                    Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+                    Flight & \multicolumn{3}{c}{Matches} \\[2pt] \midrule
                     0 & (0,1) & (2,3) & \textbf{(4,5)} \\
@@
 
-Figure \ref{schedChanges} gives a pictorial view of the model, using the 7
-skipper and 6 boat problem. On the right we have the 7 skippers with their
+Figure \ref{schedChanges} gives a pictorial view of the entire model, using the
+7 skipper and 6 boat problem. On the right we have the 7 skippers with their
 states and time slots. Again, top right, we give the schedule actually
@@
 yellow arrows show the channeling between parts of the model.
+
+The schedule presented has 6 boat changes: there are no boat changes in flight
+0 (first flight), in flight 1 skipper 6 has a boat change, in flight 2 skipper
+3 has a boat change, in flight 3 skipper 4, in flight 4 skipper 6, in flight 5
+skipper 0, and flight 6 skipper 1.
+
+\paragraph{Decision variables:} The decision variables are $\timeVar[{0}]$ to
+$\timeVar[{t-1}]$, i.e.\ for each time slot we decide what match takes place. A
+symmetry break is made at the top of search by forcing the first round to
+contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i \in \{0 \nldots
+{m-1}\} : \match[{2i, 2i+1}] = i$.
 
@@
 \end{figure}
-
-The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$, i.e.\ for each
-time slot we decide what match takes place. A symmetry break is made at the top
-of search by forcing the first round to contain the matches $(0,1), (2,3), \nldots$,
-i.e.\ $\forall_{i \in [0 \nldots m-1]} ~ \match[{2i,2i+1}] = i$. The schedule
-presented has 6 boat changes: there are no boat changes in flight 0 (first
-flight), flight 1 skipper 6 has a boat change, flight 2 skipper 3 has a boat
-change, flight 3 it's skipper 4, flight 4 skipper 6, flight 5 skipper 0 and
-last flight skipper 1.
 

### 2015-03-25 paper.tex
Redo stage 2 and 3 models

@@
 
-\subsection{Stages 2 and 3: Minimising Imbalances and Renaming Skippers}
+\subsection{Stage 2: Minimising Imbalances}
 
 Having produced a schedule that minimises boat changes, we then minimise
-criteria 6, imbalance. Assuming the first stage produced a schedule with
-$\beta$ boat changes we post this as a hard constraint in stage 2, i.e.\
-$\totalBoatChanges \leq \beta$. For each skipper $\sigma$ we introduce a
-zero/one variable $position[{i,j}]$  (\ref{posA}) which is 1 if and only if
-skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
-of the  $j^{th}$ flight (\ref{posB}). Imbalance is then computed via
-(\ref{imbA}) for each position, as the absolute amount of over or under
-expected presence in a given position. Finally, (\ref{imbB}) we compute the
-maximum imbalance over all positions for this skipper.
+criteria 6, imbalance, by extending the model as in Figure~\ref{model:stage2}.
+Assuming the first stage produced a schedule with $\beta$ boat changes we post
+this as a hard constraint \eqref{C11} in stage 2. For each skipper $\sigma$ we
+introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is 1 if and
+only if skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the
+$i^{th}$ match of the  $j^{th}$ flight \eqref{C12}. Imbalance \eqref{V10} is then computed
+for each position, as the absolute amount of over or under
+expected presence in a given position \eqref{C13}. Finally, we compute the
+maximum imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
 
-\begin{flalign}
-    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
-    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
-    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{imbA} \\
-    & \sigma.\maxImbalance = \maximum(\sigma.imbalance)  \label{imbB}
-\end{flalign}
+\begin{figure}[tb]
+\setlength{\mathindent}{1em}
+\setlength{\abovedisplayskip}{0pt}
+\setlength{\belowdisplayskip}{0pt}
+\setlength{\abovecaptionskip}{0pt}
+\begin{framed}
+\begin{align}
+    \intertext{The objective value from stage 1 is used as a hard constraint:\smallskip}
+    & \totalBoatChanges \leq \beta \tag{C11} \label{C11}
+\end{align}
+\end{framed}\begin{framed}
+\begin{align}
+    \intertext{A copy of these variables and constraints is created for each skipper $\sigma$:\smallskip}
+    & \forall i \in \{ 0 \nldots m{-}1 \} : \forall j \in \{ 0 \nldots f{-}1 \} : \nonumber \\
+    & \hspace*{1em} \position[{i,j}] \in \{0,1\} \tag{V9} \label{V9} \\
+    & \hspace*{1em} \position[{i,j}] = 1 \Leftrightarrow \timeSlot[{m.j+i}] \geq 0 \tag{C12} \label{C12} \\
+    & \forall i \in \{ 0 \nldots m{-}1 \} : \nonumber \\
+    & \hspace*{1em} \imbalance[{i}] \in \mathbb{N} \label{V10} \tag{V10} \\
+    & \hspace*{1em} \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{C13} \tag{C13} \\
+    & \maxImbalance \in \mathbb{N} \label{V11} \tag{V11} \\
+    & \maxImbalance = \maximum(imbalance) \label{C14} \tag{C14}
+\end{align}
+\end{framed}\begin{framed}
+\begin{align}
+    \intertext{We minimise the maximum imbalance over all skippers:\smallskip}
+    & \forall i \in \{ 0 \nldots n{-}1 \} : \imbalance[{i}] \equiv \sigma[{i}].\maxImbalance \label{V12} \tag{V12} \\
+    & \maxImbalance \in \mathbb{N} \label{V13} \tag{V13} \\
+    & \maxImbalance = \maximum(\imbalance) \label{C15} \tag{C15} \\
+    & \minimise(\maxImbalance) \label{C16} \tag{C16}
+\end{align}
+\end{framed}
+\caption{Additions to the constraint model in Figure~\ref{model:stage1} for
+stage 2. The constant $\beta$ is the minimum number of boat changes found in
+stage 1.}\label{model:stage2}
+\end{figure}
 
-We then capture the maximum imbalance over all skippers (\ref{balAllA} and
-\ref{balAllB}) and minimise this (\ref{balAllC}). As before, the decision
-variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry
-breaking is imposed at top of search.
+We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13}
+and \ref{C15}) and minimise this \eqref{C16}. As before, the decision variables
+are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry breaking is
+imposed at top of search.
 
-\begin{flalign}
-    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
-& \maxImbalance = \maximum(\imbalance) \label{balAllB} \\
-& \minimise(\maxImbalance) \label{balAllC}
-\end{flalign}
+\subsection{Stage 3: Renaming Skippers}
 
 Stage 3 then takes as input the schedule produced in stage 2 and renames
-skippers in the last round of the last flight to be (0,1), satisfying criteria
+skippers in the last round of the last flight to be $(0,1)$, satisfying criteria
 9. This is a simple linear process. The schedule produced for 7 skippers and 6

### 2015-03-25 paper.tex
Restyle table

@@
 
-\begin{table}[tb]
-\begin{center}
-\begin{tabular}{cc} \\
-flight & matches \\ \hline
-0 & (0,6) (2,3) (4,5) \\
-1 & (0,2) (4,1) (6,5) \\
-2 & (2,1) (0,5) (6,3) \\
-3 & (5,1) (0,3) (6,4) \\
-4 & (3,5) (6,1) (2,4) \\
-5 & (3,1) (0,4) (2,5) \\
-6 & (3,4) (6,2) (0,1) \\ \hline
+\begin{SCtable}[2.0][tb]
+    \setlength{\tabcolsep}{3pt}
+    \begin{tabular}{cccc}
+        \toprule
+        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+        0 & (0,6) & (2,3) & (4,5) \\
+        1 & (0,2) & (4,1) & (6,5) \\
+        2 & (2,1) & (0,5) & (6,3) \\
+        3 & (5,1) & (0,3) & (6,4) \\
+        4 & (3,5) & (6,1) & (2,4) \\
+        5 & (3,1) & (0,4) & (2,5) \\
+        6 & (3,4) & (6,2) & (0,1) \\ \bottomrule
     \end{tabular}
-\end{center}
-\caption{Round-robin schedule with 7 skippers, 6 boats and 7 flights. Result of
-stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of
-imbalance is skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in
-position 1 and 1 (mid) in position 2 (last). Perfect balance would be 2 matches
-in each position, only achieved by skipper 2.}
-\label{tab2}
-\end{table}
+    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights,
+        which is the result of stages 1, 2, and 3. It has 6 boat changes
+        and imbalance 1. An example of imbalance is skipper $\sigma[{0}]$
+        with 2 matches in position 0 (first), 3 in position 1 and 1 (mid)
+        in position 2 (last). Perfect balance would be 2 matches in each
+    position, only achieved by skipper 2.}\label{tab2}
+\end{SCtable}
 

### 2015-03-31 paper.tex
Narrower captions
Paragraph spacing
Reorder paragraphs
Worked on intro and discussion

@@
 \usepackage{framed}
-\usepackage{coffee2}
+%\usepackage{coffee2}
 \usepackage{tikz}
@@
 \begin{abstract} 
-\todo{The quick brown duck jumped over the lazy pig. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog. The quick brown duck jumped over the lazy dog.}
+\todo{We encourage industrial and academic users of constraint technology to submit papers on completed or on-going practical projects.
+Papers comparing constraint technology to other optimization techniques (MIP, local search, SAT, etc.) on a realistic application with a sound experimental evaluation are also encouraged.
+Papers which clearly define users' benefits, describe the required effort to build the application and the time frame in which it was delivered, will match the acceptance criteria most closely.
+The novelty of the application domain, while potentially a plus, is not the only deciding acceptance criterion.
+Application papers will be reviewed by a program committee with significant experience in the use of CP in applications.
+The writing of the paper should be guided by providing answers to four main questions: Problem being solved?
+Why CP?
+How CP?
+Added value of CP?
+Formatting, length, and dates for submissions are the same as for the technical track.}
 \end{abstract}
 
-\section{Introduction}\coffee{1}
-Round robin competition scehdules represent a rich area for applications of constraint programming.
-This work describes a particular round robin competition format that arises from sailing, known as match racing.
-In particular, the competitors, known formally as {\em skippers} compete against each other in a series of matches taking place in rounds (known as {\em flights}).
-For a match, each skipper is placed in a boat.
+\section{Introduction}
+%\coffee{1}
+This work describes a round robin competition format that arises from sailing, known as match racing.
+Competitors, i.e.
+{\em skippers}, compete against each other in a series of matches taking place in rounds, known as {\em flights}.
+A match is composed of two skippers, with each skipper in a boat on his own.
+Skippers in a match set off together, one on the port side, the other starboard, and first home wins that match.
+ISAF World Sailing rules dictate what makes a legal schedule and what criteria to optimise.
+This is a rich set of rules, 13 in all, and as far as we know, all published schedules have been produced by hand.
+This is a daunting task.
+A close inspection of these schedules reveals that most are illegal, violating many of the match race rules, and some that are legal are far from optimal.
 
-The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the competiting skippers are scheduled into flights and matches, known as pairing lists.
-Several of these criteria are applicable when the number of skippers exceeds the number of available boats, in which case skippers have to change in and out of boats, and are allowed time in the schedule to check and fine-tune the boat they change into.
-
-While the number of boats and skippers involved is typically not numerous (e.g.\ upto 10 of each), the creations of valid schedules satisfying all constraints is unachievable without automation.
-Hence, this paper documents our efforts in automating the creation of valid schedules.
-This is achieved \todo{through ...
-symmettry breaking ...,  etc.
-We believe that the methods detailed here are applicable to other problems (example?), and are of interest to the community.
-}
-
-\todo{Therefore the contributions of this paper are hunner'-fold: TODO}
-
-The remainder of this paper is structured as follows: Section~\ref{sec:definition} provides an overview of the criteria outlined for creating match racing pairing lists; Section~\ref{sec:samples} discusses several sample schedules, while concluding remarks follow in Section~\ref{sec:conclusions}.
+This paper describes the scheduling problem.
+We present a constraint programming solution to this problem, and document how this model was constructed incrementally.
+We believe this illustrates how adaptable constraint programming is, i.e.
+given a fairly robust model this can be incrementally developed to address all of the required criteria.
+Our schedules are then constructed in a sequence of stages, not dissimilar to the hybrid and decomposition based approaches in \cite{lombardi2012}.
+Some ISAF published schedules are presented along with some of our own, some of these being new.
+Having a constraint program for this problem has a number of unexpected advantages, in particular, we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
+That is, the constraint program can be used help design the next set of umpire's rules.
 
 \section{Problem Definition: Round Robin Pairing Lists}\label{sec:definition}
+The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the competing skippers are scheduled into flights and matches, known as pairing lists.
+Several of these criteria are applicable when the number of skippers exceeds the number of available boats, in which case skippers have to change in and out of boats, and are allowed time in the schedule to check and fine-tune the boat they change into.
+Typically, matches set off at 5 minute intervals with each match taking about 20 minutes.
+Therefore, if we have 10 skippers and 10 boats we have 45 matches.
+This results in 9 flights each of 5 matches.
+Each flight takes about 50 minutes, consequently eight or nine flights a day is a reasonable achievement for most umpires.
+Consequently, the number of boats and skippers involved is typically small.
 
-In the match racing format of sailing events, the criteria for generated match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
-M.2 Recommended Criteria for Round Robin Pairing Lists. We detail these criteria below.
+The criteria for generated match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
+M.2 Recommended Criteria for Round Robin Pairing Lists, and are detailed below.
 
@@
 
-Firstly, we note that we have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}.
-We further outline the key aspects of the criteria, which motivate and permit understanding of our proposal solution.
+We have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}.
+Note that the order of matches within a flight is significant and is constrained, as is the order of flights within a schedule and the position of skippers within a match.
+This permits fair schedules that provide the opportunity for skippers to change boats, take fair advantage of wind direction, etc.
 
-In particular, the order of matches within a flight are constrained, as well as the order of flights, to permit fair schedules that provide the opportunity for skippers to change boats, etc.
+Criteria 12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match (i.e.
+it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange all his kit and set the boat as he likes it prior to casting off, and this is a boat change.
 
@@
 
-Finally, it can be observed that criteria 10 is ambigious: - this could be interpreted on an schedule basis: i.e.\ to minimise the overall number of changes in the entire pairing list schedule; or alterantively as well as a fair, but minimal number of changes across all skippers.
+Criteria 10 is ambiguous: - this could be interpreted on a schedule basis: i.e.\ to minimise the overall number of changes in the entire pairing list schedule; or alternatively as well as a fair, but minimal number of changes across all skippers.
 In our work, we take the latter viewpoint.
 
-In the following, we detail the constraint models (Section~\ref{sec:models}), while some example schedules are presented in Section~\ref{sec:samples}.
+There are some conflicts inherent in the rules.
+Take criteria 4 and 11, assume we have 4 boats, and in flight $i$ the last match is the pair of skippers ($x,y$).
+Criteria 11 dictates that skippers $x$ and $y$ must appear in the next flight, $i+1$, and criteria 4 that neither can be first in the next flight.
+This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating criteria 1.
+Therefore, although not explicitly stated, there are no legal schedules with less than 6 boats.
 
@@
 
-\begin{SCtable}[2.0][tb]
+\begin{SCtable}[1.8][tb]
     \setlength{\tabcolsep}{3pt}
@@
 
-\paragraph{Modelling skippers:} The first thing we model, in the first half of
+\paragraph{Modeling skippers:} The first thing we model, in the first half of
 Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal
@@
 
+\paragraph{Decision variables:} The decision variables are $\timeVar[{0}]$ to
+$\timeVar[{t-1}]$, i.e.\ for each time slot we decide what match takes place. A
+symmetry break is made at the top of search by forcing the first round to
+contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i \in \{0 \nldots
+{m-1}\} : \match[{2i, 2i+1}] = i$.
+
+\bigskip \noindent
 Figure \ref{schedChanges} gives a pictorial view of the entire model, using the
@@
 skipper 0, and flight 6 skipper 1.
-
-\paragraph{Decision variables:} The decision variables are $\timeVar[{0}]$ to
-$\timeVar[{t-1}]$, i.e.\ for each time slot we decide what match takes place. A
-symmetry break is made at the top of search by forcing the first round to
-contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i \in \{0 \nldots
-{m-1}\} : \match[{2i, 2i+1}] = i$.
 
@@
 skippers sequence of competitors. An edge between variables corresponds to a
-matched pair, that must take different values. Bottom right is a sketch by one
-of the authors.}
+matched pair, that must take different values. Bottom right is a sketch by third author.}
 \label{oriented}
@@
 \section{Sample Schedules}\label{sec:samples}
+\begin{center}
+\begin{figure}[h]
+\begin{minipage}[t]{0.3\textwidth}
+\hspace{0.2cm}
+\begin{scriptsize}
+\begin{tabular}{cccc}
+        \toprule
+        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+        0 & (2,7) & (3,0) & (5,4) \\ 
+        1 & (0,2)  & (4,3) & (7,5) \\
+        2 & (0,4) & (7,6) & (5,3) \\
+        3 & (4,6) & (5,0) & (3,1) \\
+        4 & (6,5) & (3,2) & (1,4) \\
+        5 & (6,3) & (4,7) & (2,1) \\
+        6 & (7,3) & (1,6) & (4,2) \\
+       7 & (7,1)  & (2,5) & (6,0) \\
+       8 & (5,1)  & (0,7) & (6,2) \\
+       9 & (1,0)  & & \\ \bottomrule
+          & & & \\
+          & & & \\
+    \end{tabular}
+\end{scriptsize}
+\label{tab3a}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.3\textwidth}
+\hspace{0.2cm}
+\begin{scriptsize}
+\begin{tabular}{cccc}
+        \toprule
+        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+        0 & (0,7) & (3,2) & (5,4) \\ 
+        1 & (0,2) & (7,4) & (5,3) \\
+        2 & (4,0) & (7,3) & (2,5) \\
+        3 & (3,0) & (2,4) & (6,5) \\
+        4 & (4,3) & (5,1) & (8,6) \\
+        5 & (3,1) & (6,2) & (4,8) \\
+        6 & (6,3) & (1,4) & (8,2) \\
+        7 & (4,6) & (2,7) & (1,8) \\
+        8 & (7,6) & (0,8) & (2,1) \\
+        9 & (8,7) & (5,0) & (6,1) \\
+        10 & (8,5) & (1,7) & (0,6) \\
+        11 & (7,5) & (3,8) & (1,0) \\ \bottomrule
+    \end{tabular}
+\end{scriptsize}
+\label{tab3a}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.3\textwidth}
+\begin{scriptsize}
+\begin{tabular}{ccccc}
+        \toprule
+        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
+        0 & (0,6) & (3,2) & (5,4) & (1,7) \\
+        1 & (2,0) & (6,3) & (4,1) & (8,7) \\
+        2 & (6,4) & (0,5) & (7,2) & (3,8) \\
+        3 & (4,7) & (1,8) & (0,3) & (5,2) \\
+        4 & (3,1) & (7,5) & (8,0) & (2,6) \\
+        5 & (3,7) & (4,8) & (2,1) & (6,5) \\
+        6 & (8,2) & (1,6) & (5,3) & (0,4) \\
+        7 & (5,1) & (7,0) & (6,8) & (4,3) \\
+        8 & (8,5) & (2,4) & (7,6) & (1,0) \\ \bottomrule
+        & & & & \\
+        & & & & \\
+        & & & & \\
+    \end{tabular} 
+\end{scriptsize}
+\end{minipage}
+\caption{Three schedules. First is 8 skippers with 6 boats (legal), then 9 skippers with 6 boats (new), finally 9 skippers with 8 boats (new).}
+\label{sr10}
+\end{figure}
+\end{center}
 
@@
 We would like to thank our parents, God, and all his angels.
-\coffee{2}
+%\coffee{2}
 

### 2015-04-01 paper - Copy.tex
new schedules added

--- 2015-03-31 paper.tex
@@
 \usepackage{framed}
-%\usepackage{coffee2}
+\usepackage{coffee2}
 \usepackage{tikz}
@@
 \section{Problem Definition: Round Robin Pairing Lists}\label{sec:definition}
-The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the competing skippers are scheduled into flights and matches, known as pairing lists.
+The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the competiting skippers are scheduled into flights and matches, known as pairing lists.
 Several of these criteria are applicable when the number of skippers exceeds the number of available boats, in which case skippers have to change in and out of boats, and are allowed time in the schedule to check and fine-tune the boat they change into.
@@
 Each flight takes about 50 minutes, consequently eight or nine flights a day is a reasonable achievement for most umpires.
-Consequently, the number of boats and skippers involved is typically small.
+While the number of boats and skippers involved is typically small, the construction of valid schedules satisfying all constraints is, in our experience, computationally hard.
 
 The criteria for generated match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
-M.2 Recommended Criteria for Round Robin Pairing Lists, and are detailed below.
+M.2 Recommended Criteria for Round Robin Pairing Lists. We detail these criteria below.
 
@@
 
-We have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}.
-Note that the order of matches within a flight is significant and is constrained, as is the order of flights within a schedule and the position of skippers within a match.
-This permits fair schedules that provide the opportunity for skippers to change boats, take fair advantage of wind direction, etc.
-
+Firstly, we note that we have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}.
+The order of matches within a flight is significant and is constrained, as is the order of flights.
+This permits fair schedules that provide the opportunity for skippers to change boats, etc.
 Criteria 12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match (i.e.
-it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange all his kit and set the boat as he likes it prior to casting off, and this is a boat change.
+it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange all his kit and set the boat as he likes it, and this is a boat change.
 
@@
 
-Criteria 10 is ambiguous: - this could be interpreted on a schedule basis: i.e.\ to minimise the overall number of changes in the entire pairing list schedule; or alternatively as well as a fair, but minimal number of changes across all skippers.
+Criteria 10 is ambigious: - this could be interpreted on an schedule basis: i.e.\ to minimise the overall number of changes in the entire pairing list schedule; or alterantively as well as a fair, but minimal number of changes across all skippers.
 In our work, we take the latter viewpoint.
@@
 
-\paragraph{Modeling skippers:} The first thing we model, in the first half of
+\paragraph{Modelling skippers:} The first thing we model, in the first half of
 Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal
@@
 skippers sequence of competitors. An edge between variables corresponds to a
-matched pair, that must take different values. Bottom right is a sketch by third author.}
+matched pair, that must take different values. Bottom right is a sketch by one
+of the authors.}
 \label{oriented}
@@
 \section{Sample Schedules}\label{sec:samples}
-\begin{center}
-\begin{figure}[h]
-\begin{minipage}[t]{0.3\textwidth}
-\hspace{0.2cm}
-\begin{scriptsize}
-\begin{tabular}{cccc}
-        \toprule
-        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
-        0 & (2,7) & (3,0) & (5,4) \\ 
-        1 & (0,2)  & (4,3) & (7,5) \\
-        2 & (0,4) & (7,6) & (5,3) \\
-        3 & (4,6) & (5,0) & (3,1) \\
-        4 & (6,5) & (3,2) & (1,4) \\
-        5 & (6,3) & (4,7) & (2,1) \\
-        6 & (7,3) & (1,6) & (4,2) \\
-       7 & (7,1)  & (2,5) & (6,0) \\
-       8 & (5,1)  & (0,7) & (6,2) \\
-       9 & (1,0)  & & \\ \bottomrule
-          & & & \\
-          & & & \\
-    \end{tabular}
-\end{scriptsize}
-\label{tab3a}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.3\textwidth}
-\hspace{0.2cm}
-\begin{scriptsize}
-\begin{tabular}{cccc}
-        \toprule
-        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
-        0 & (0,7) & (3,2) & (5,4) \\ 
-        1 & (0,2) & (7,4) & (5,3) \\
-        2 & (4,0) & (7,3) & (2,5) \\
-        3 & (3,0) & (2,4) & (6,5) \\
-        4 & (4,3) & (5,1) & (8,6) \\
-        5 & (3,1) & (6,2) & (4,8) \\
-        6 & (6,3) & (1,4) & (8,2) \\
-        7 & (4,6) & (2,7) & (1,8) \\
-        8 & (7,6) & (0,8) & (2,1) \\
-        9 & (8,7) & (5,0) & (6,1) \\
-        10 & (8,5) & (1,7) & (0,6) \\
-        11 & (7,5) & (3,8) & (1,0) \\ \bottomrule
-    \end{tabular}
-\end{scriptsize}
-\label{tab3a}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.3\textwidth}
-\begin{scriptsize}
-\begin{tabular}{ccccc}
-        \toprule
-        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
-        0 & (0,6) & (3,2) & (5,4) & (1,7) \\
-        1 & (2,0) & (6,3) & (4,1) & (8,7) \\
-        2 & (6,4) & (0,5) & (7,2) & (3,8) \\
-        3 & (4,7) & (1,8) & (0,3) & (5,2) \\
-        4 & (3,1) & (7,5) & (8,0) & (2,6) \\
-        5 & (3,7) & (4,8) & (2,1) & (6,5) \\
-        6 & (8,2) & (1,6) & (5,3) & (0,4) \\
-        7 & (5,1) & (7,0) & (6,8) & (4,3) \\
-        8 & (8,5) & (2,4) & (7,6) & (1,0) \\ \bottomrule
-        & & & & \\
-        & & & & \\
-        & & & & \\
-    \end{tabular} 
-\end{scriptsize}
-\end{minipage}
-\caption{Three schedules. First is 8 skippers with 6 boats (legal), then 9 skippers with 6 boats (new), finally 9 skippers with 8 boats (new).}
-\label{sr10}
-\end{figure}
-\end{center}
 
@@
 We would like to thank our parents, God, and all his angels.
-%\coffee{2}
+\coffee{2}
 

### 2015-04-01 paper.tex
new schedules added

@@
 This is a daunting task.
-A close inspection of these schedules reveals that most are illegal, violating many of the match race rules, and some that are legal are far from optimal.
+A close inspection of these schedules reveals that most are illegal, violating many of the match race rules, many schedules are missing and some that are legal are far from optimal.
 
 This paper describes the scheduling problem.
-We present a constraint programming solution to this problem, and document how this model was constructed incrementally.
+We present a constraint programming solution and document how this model was constructed incrementally.
 We believe this illustrates how adaptable constraint programming is, i.e.
@@
 Some ISAF published schedules are presented along with some of our own, some of these being new.
-Having a constraint program for this problem has a number of unexpected advantages, in particular, we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
-That is, the constraint program can be used help design the next set of umpire's rules.
+These schedules are esentially blank forms, made available to umpires and competition managers.
+These forms are then filled in with names of actual competitors, i.e.
+these schedules are reusable.
+
+The paper is organised as follows: we present the 13 match racing rules and then the constraint models and four stages of schedule construction, schedules are then presented, there is then a discuss and we conclude.
 
@@
 \section{Sample Schedules}\label{sec:samples}
+
 \begin{center}
 \begin{figure}[h]
-\begin{minipage}[t]{0.3\textwidth}
-\hspace{0.2cm}
-\begin{scriptsize}
+\begin{minipage}[t]{0.5\textwidth}
+\hspace{0.6cm}
+%\begin{scriptsize}
+\begin{tabular}{cccc}
+        \toprule
+        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+        0 & (5,2) & (4,3) & (1,6) \\ 
+        1 & (4,2)  & (6,5) & (3,1) \\
+        2 & (6,4) & (2,1) & (3,5) \\
+        3 & (6,2) & (5,0) & (1,7) \\
+        4 & (5,1) & (0,6) & (2,7) \\
+        5 & (7,5) & (2,0) & (6,3) \\
+        6 & (0,7) & (4,1) & (3,2) \\
+       7 & (7,4)  & (0,3) &  \\
+       8 & (4,0)  & (7,3) &  \\
+       9 & (5,4)  & (7,6) & (1,0) \\ \bottomrule
+          & & & \\
+          & & & \\
+    \end{tabular}
+%\end{scriptsize}
+\label{08-06a}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.5\textwidth}
+\hspace{0.6cm}
+%\begin{scriptsize}
 \begin{tabular}{cccc}
@@
     \end{tabular}
-\end{scriptsize}
-\label{tab3a}
+%\end{scriptsize}
+\label{08-06b}
 \end{minipage}
-\hfill
+\caption{Schedules for 8 skippers and 6 boats. On the left is the published ISAF schedule, and this is illegal. On the right is our schedule, respecting all ISAF criteria..}
+\label{08-06}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h]
 \begin{minipage}[t]{0.3\textwidth}
@@
 \end{minipage}
-\hfill
+%\hfill
 \begin{minipage}[t]{0.3\textwidth}
@@
 \subsection{Discussion}
+Having a constraint program for this problem has a number of unexpected advantages, in particular, we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
+That is, the constraint program can be used help design the next set of umpire's rules.
 

### 2015-04-01 paper.tex
reformatted schedules 09-0*
new 08-06 schedules with critique

@@
 \section{Sample Schedules}\label{sec:samples}
+We present three pairs of schedules.
+The first pair is for 8 skippers and 6 boats, one published by ISAF, the other generated by us.
+Next, we present two new schedules, not appearing in the ISAF manual, for 9 skippers and 6 boats and 9 skippers with 8 boats.
+The last pair is for 10 skippers and 6 boats, again ISAF published and generated by us.
+For each of our schedules, we used 1 day cpu time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
+Stages 3 and 4 (renaming and orientation) completed in less than a second.
 
@@
        9 & (5,4)  & (7,6) & (1,0) \\ \bottomrule
-          & & & \\
-          & & & \\
     \end{tabular}
@@
        9 & (1,0)  & & \\ \bottomrule
-          & & & \\
-          & & & \\
     \end{tabular}
@@
 \end{minipage}
-\caption{Schedules for 8 skippers and 6 boats. On the left is the published ISAF schedule, and this is illegal. On the right is our schedule, respecting all ISAF criteria..}
+\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal) and on the right is our schedule.}
 \label{08-06}
@@
 
+\noindent
+\subsection{8 skippers and 6 boats}
+We first analyse the ISAF schedule (on the left).
+Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on 3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7).
+Criteria 5 (no more than two consecutive port or starboard assignments) are violated for skippers 6 and 7.
+Criteria 6 (imbalance) is violated for skippers 6 and 8.
+Criteria 12  (new boats do not sail first) is violated in flight 9 for skipper 5.
+Finally, the schedule has 8 boat changes.
+Our schedule, on the right, resepects all criteria and has 6 boat changes and a maximum imbalance of 1.
+
 \begin{center}
 \begin{figure}[h]
-\begin{minipage}[t]{0.3\textwidth}
-\hspace{0.2cm}
-\begin{scriptsize}
+\begin{minipage}[t]{0.5\textwidth}
+\hspace{0.6cm}
+%\begin{scriptsize}
 \begin{tabular}{cccc}
@@
     \end{tabular}
-\end{scriptsize}
-\label{tab3a}
+%\end{scriptsize}
+\label{09-06}
 \end{minipage}
 %\hfill
-\begin{minipage}[t]{0.3\textwidth}
-\begin{scriptsize}
+\begin{minipage}[t]{0.5\textwidth}
+\hspace{0.6cm}
+%\begin{scriptsize}
 \begin{tabular}{ccccc}
@@
     \end{tabular} 
-\end{scriptsize}
+%\end{scriptsize}
+\label{09-08}
 \end{minipage}
-\caption{Three schedules. First is 8 skippers with 6 boats (legal), then 9 skippers with 6 boats (new), finally 9 skippers with 8 boats (new).}
-\label{sr10}
+\caption{Two new schedules. On the left, 9 skippers and 6 boats and on the right 9 skippers and 8 boats.}
+\label{09}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[h]
+\begin{minipage}[t]{0.5\textwidth}
+\hspace{0.6cm}
+%\begin{scriptsize}
+\begin{tabular}{cccc}
+ \toprule
+Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+0 & (8,3) &  (1,7) &  (0,9) \\
+1 & (7,3) &  (0,8) &  (1,9) \\
+2 & (0,7) &  (9,3) &  (1,8) \\ 
+3 & (6,2) &  (5,0) &  (7,4) \\
+4 & (5,2) &  (6,4) &  (3,0) \\ 
+5 & (8,6) &  (2,9) &  (4,1) \\ 
+6 & (7,2) &  (4,8) &  (9,6) \\
+7 & (2,4) &  (0,6) &  (7,5) \\ 
+8 & (6,1) &  (5,9) &  (8,2) \\ 
+9 & (9,4) &  (8,7) &  (6,5) \\ 
+10 & (9,7) &  (6,3) &  (8,5) \\ 
+11 & (7,6) &  (3,1) &  (9,8) \\
+12 & (4,3) &  (5,1) &  (2,0) \\ 
+13 & (3,5) &  (4,0) &  (2,1) \\ 
+14 & (5,4) &  (3,2) &  (1,0) \\ \bottomrule
+\end{tabular}
+%\end{scriptsize}
+\label{10-06a}
+\end{minipage}
+%\hfill
+\begin{minipage}[t]{0.5\textwidth}
+\hspace{0.6cm}
+%\begin{scriptsize}
+\begin{tabular}{ccccc}
+\toprule
+Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+0 & (4,7) & (3,2) & (0,5) \\
+1 & (2,4) & (7,0) & (3,5) \\
+2 & (0,4) & (7,3) & (5,2) \\ 
+3 & (4,3) & (0,2) & (5,7) \\ 
+4 & (3,0) & (6,5) & (2,7) \\ 
+5 & (6,3) & (7,1) & (8,2) \\
+6 & (7,6) & (2,1) & (9,8) \\ 
+7 & (2,6) & (8,7) & (4,9) \\ 
+8 & (6,8) & (1,4) & (7,9) \\
+9 & (8,1) & (5,4) & (9,6) \\ 
+10 & (5,1) & (9,2) & (4,6) \\ 
+11 & (1,9) & (6,0) & (8,4) \\ 
+12 & (0,9) & (3,8) & (6,1) \\ 
+13 & (8,0) & (9,5) & (1,3) \\ 
+14 & (5,8) & (9,3) & (1,0) \\ \bottomrule 
+\end{tabular} 
+%\end{scriptsize}
+\label{10-06b}
+\end{minipage}
+\caption{Schedules for 10 skippers and 6 boats. On the left, the ISAF published schedule (illegal) and on the right, our schedule.}
+\label{10-06}
 \end{figure}

### 2015-04-01 paper.tex
additions to discussion and conclusion

@@
 \subsection{8 skippers and 6 boats}
-We first analyse the ISAF schedule (on the left).
+We first analyse the ISAF schedule, Table \ref{08-06} on the left.
 Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on 3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7).
-Criteria 5 (no more than two consecutive port or starboard assignments) are violated for skippers 6 and 7.
+Criteria 5 (no more than two consecutive port or starboard assignments) is violated for skipper 6 (flights 1 to 3) and 7 (flights 7 to 9).
 Criteria 6 (imbalance) is violated for skippers 6 and 8.
@@
 Finally, the schedule has 8 boat changes.
-Our schedule, on the right, resepects all criteria and has 6 boat changes and a maximum imbalance of 1.
+Our schedule, Table \ref{08-06} on the right, respects all criteria and has 6 boat changes and a maximum imbalance of 1.
+
+\subsection{9 skippers}
+Two new schedules are presented in Table \ref{09}, on the left for 6 boats and on the right 8 boats.
+Neither of these schedules appear in the ISAF Umpires' Manual.
+Both schedules respect all criteria.
+For 6 boats there are 8 boat changes (no skipper making more than 1 boat change) and a maximum imbalance of 2.
+For 8 boats there are again 8 boat changes, no skipper with more than 1 boat change, and perfect balance (each skipper 4 times on starboard side and 4 on port side).
 
@@
 \end{center}
+
+\subsection{10 skippers and 6 boats}
+Table \ref{10-06} shows the ISAF schedule on the right for 10 skippers and 6 boats and on the right, our schedule.
+The ISAF schedule violates criteria 5 (no more than 2 consequitive port or starboard assignments) 10 times (twice for skipper 0, 1 and 6 and once for skippers 3, 7, 8 and 9).
+Criteria 12 (new boats do not sail first) is violated 7 times (in flight 3 for skippers 6 and 2, flight 5 for skipper 8, flight 6 for skipper 7, flight 8 for skipper 1, flight 9 for skipper 4 and flight 12 for skipper 4 again).
+There are 22 boat changes, with the minimum changes for a skipper being 1 and the maximum 3.
+Our schedule, right of Table \ref{10-06} satisfies all criteria, has 12 boat changes with the minimum changes for a skipper being 0 and the maximum 2, and a maximum imbalance of 1.
 
@@
 \subsection{Discussion}
-Having a constraint program for this problem has a number of unexpected advantages, in particular, we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
-That is, the constraint program can be used help design the next set of umpire's rules.
+It was anticipated that this problem would be easy to model.
+This naivety was due to "round robin", leading us to believe that we could use some of the models proposed in \cite{trick2002}, \cite{trick2008} and \cite{henz2004}.
+This naivety slowly dissolved as we addressed more and more of the ISAF criteria.
+A number of models we produced were scrapped due to misunderstanding about the actual problem, i.e.
+a communication problem between the authors.
+Eventually this was resolved by presenting the majority of the criteria as a deterministic finite automaton.
+This became our Rosetta Stone, with the surprising benefit that it not only improved the teams communications, it was also a constraint!
+
+The staged approach was taken cautiously.
+We expected that isolating the orientation of schedules as a post-process might leave us with a hard or insoluble problem.
+So far, every schedule we have produced has been oriented with very little search, typically taking less than a second.
+
+We used the choco constraint programming toolkit and one of our goals was to use only toolkit constraints, i.e.
+we wanted to see how far we could go without implementing our own specialised constraints.
+We are pleased to say that we did not have to do anything out of the box, although we did feel that we had used just about every constraint there was.
+
+There are many redundant variables in our model.
+One of our first valid models was essentially that shown in Figure \ref{skipper5}, and did not use $modMatch$ and $match$ variables.
+Performance was hopeless, struggling to produce a 7 skipper 6 boat schedule in days.
+The $modMatch$ and $match$ variables were added.
+This improved domain filtering, and a flattened $match$ array was used as decision variables.
+That is, the decisions where "when do we schedule this match?".
+At this point we had not yet produced a 9 skipper 6 boat schedule and we suspected that the combined criteria might exclude such a schedule.
+A non-constraint model was developed by the fourth author, primarily to prove that there was no schedule for 9 skippers with 6 boats.
+This program used a backtracking search with decision variables being positions within flights, i.e.
+time slots being assigned matches.
+Prior to search, symmetry breaking was performed, and at the top of search the matches in the first flight were set.
+A solution was found in seconds!
+With this experience we added in the $time$ variables, channeled these into the existing model and used these as decision variables, i.e.
+the question now was "what match will we do now?".
+We also anchored the matches in the first flight.
+With these changes we began to produce schedules in acceptable time.
+The model was then built upon, incrementally adding criteria.
+This took a surprisingly short amount of time, sometimes minutes of coding to add in a new feature.
+The model was then enhanced so that it would address optimisation rather than just satisfaction, again a trivial programming task.
+
+We have only reported a handful of our schedules, however there are missing schedules.
+Examples of these missing schedules are 10 skippers and 8 boats, 11 skippers with less than 10 boats, 12 skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with less than 10 boats.
+None of these schedules have been published by the ISAF, although we expect that they can be produced by selectively violating some of constraints.
+We have also not yet encoded criteria 7, addressing the situation of 10 or more boats.
+To do this we will have to modify the DFA constraint used in the first two stages.
 
 \section{Conclusion}\label{sec:conclusions}
+We have produce new and better match race schedules.
+These schedules can be used by anyone that competes under ISAF World Sailing rules.
+Our schedules can be downloaded as blank schedules and then populated with the names of the actual competing skippers.
 
-\section*{Acknowledgments}
-We would like to thank our parents, God, and all his angels.
+So, why did we use constraint programming?
+The answer is obvious:  we are constraint programmers, or to borrow Mark Twain's words "To a man with a hammer, everything looks like a nail." But actually, constraint programming has been a good way to go.
+From an engineering perspective, it has allowed us to prototype solutions quickly and to build solutions incrementally.
+There is also an advantage that we might exploit in the future: we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
+That is, the constraint program might be used to design the next set of umpire's rules.
+
+%\section*{Acknowledgments}
+%We would like to thank our parents, God, and all his angels.
 %\coffee{2}

### 2015-04-01 paper.tex
new abstract and conclusion ... imaginary boat scene

@@
 \begin{abstract} 
-\todo{We encourage industrial and academic users of constraint technology to submit papers on completed or on-going practical projects.
-Papers comparing constraint technology to other optimization techniques (MIP, local search, SAT, etc.) on a realistic application with a sound experimental evaluation are also encouraged.
-Papers which clearly define users' benefits, describe the required effort to build the application and the time frame in which it was delivered, will match the acceptance criteria most closely.
-The novelty of the application domain, while potentially a plus, is not the only deciding acceptance criterion.
-Application papers will be reviewed by a program committee with significant experience in the use of CP in applications.
-The writing of the paper should be guided by providing answers to four main questions: Problem being solved?
-Why CP?
-How CP?
-Added value of CP?
-Formatting, length, and dates for submissions are the same as for the technical track.}
+We present a constraint programming solution to the problem of generating round-robin schedules for dinghy sailing match races.
+Our schedules satisfy the widely used ISAF World Sailing pairing lists match race criteria.
+We show that some published ISAF schedules are in fact illegal, and present corresponding legal instances and schedules that have not previously been published.
+Our schedules can be downloaded as blanks, then populated with actual competitors and used in ISAF competitions.
 \end{abstract}
@@
 
+\begin{center}
+\begin{figure}[tb]
+\hspace{-1cm}
+\includegraphics[height=12cm,width=17.5cm]{dinghy.jpg}
+\vspace{-30mm}
+\caption{Scene from an imaginary dinghy race.}
+\label{dinghy}
+\end{figure}
+\end{center}
+
 \subsection{Discussion}

### 2015-04-02 paper.tex
some changes from me

@@
 Skippers in a match set off together, one on the port side, the other starboard, and first home wins that match.
-ISAF World Sailing rules dictate what makes a legal schedule and what criteria to optimise.
-This is a rich set of rules, 13 in all, and as far as we know, all published schedules have been produced by hand.
+Criteria published by the Interational Sailing Federation (ISAF) dictate what makes a legal match race schedule and what should be optimised.
+This is a rich set of cirteria, 13 in all, and as far as we know, all published schedules have been produced by hand.
 This is a daunting task.
-A close inspection of these schedules reveals that most are illegal, violating many of the match race rules, many schedules are missing and some that are legal are far from optimal.
+A close inspection of these schedules reveals that most are illegal, violating many of the match race scheduling criteria, many schedules are missing and some that are legal are far from optimal.
 
@@
 Some ISAF published schedules are presented along with some of our own, some of these being new.
-These schedules are esentially blank forms, made available to umpires and competition managers.
-These forms are then filled in with names of actual competitors, i.e.
-these schedules are reusable.
+These schedules are esentially blank forms, made available to event organisers, which can be filled in with names of actual competitors, i.e.\ these schedules are reusable.
 
@@
 This results in 9 flights each of 5 matches.
-Each flight takes about 50 minutes, consequently eight or nine flights a day is a reasonable achievement for most umpires.
+Each flight takes about 50 minutes, consequently eight or nine flights a day is a reasonable achievement for most events~\cite{isaf}.
 Consequently, the number of boats and skippers involved is typically small.
 
-The criteria for generated match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
+The criteria for  match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
 M.2 Recommended Criteria for Round Robin Pairing Lists, and are detailed below.
@@
 \begin{framed}
+Principal Criteria in Order of Priority:
 \begin{enumerate}
@@
 Note that criteria 10, 11 and 12 only apply when there are fewer boats than
-skippers.
+skippers; 11 and 12 override 6 when changes are required.
 \end{framed}
@@
 Note that the order of matches within a flight is significant and is constrained, as is the order of flights within a schedule and the position of skippers within a match.
-This permits fair schedules that provide the opportunity for skippers to change boats, take fair advantage of wind direction, etc.
+This permits fair schedules that provide the sufficient changeover time for skippers changing boats, etc.
 
 Criteria 12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match (i.e.
-it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange all his kit and set the boat as he likes it prior to casting off, and this is a boat change.
+it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange all his kit and set the boat to his preference before racing commences, and this is a boat change.
 
-Next, we note that skippers can be ranked prior to an event -- based on their performance in previous events~\footnote{\url{http://www.sailing.org/rankings/match/}} -- which is used to seed the skippers.
+Next, we note that skippers can be ranked prior to an event -- based on their performance in previous events\footnote{\url{http://www.sailing.org/rankings/match/}} -- which is used to seed the skippers.
 The ordering of skippers within a match signifies their starting position (port or starboard) -- as skippers allocated the starboard starting position gain a small competitive advantage in that match - criteria 8 accomplishes the seedings.
@@
 This improved domain filtering, and a flattened $match$ array was used as decision variables.
-That is, the decisions where "when do we schedule this match?".
+That is, the decisions where ``when do we schedule this match?".
 At this point we had not yet produced a 9 skipper 6 boat schedule and we suspected that the combined criteria might exclude such a schedule.
@@
 With this experience we added in the $time$ variables, channeled these into the existing model and used these as decision variables, i.e.
-the question now was "what match will we do now?".
+the question now was ``what match will we do now?".
 We also anchored the matches in the first flight.
@@
 We have produce new and better match race schedules.
-These schedules can be used by anyone that competes under ISAF World Sailing rules.
+These schedules can be used by anyone that competes under the criteria published by ISAF.
 Our schedules can be downloaded as blank schedules and then populated with the names of the actual competing skippers.
@@
 So, why did we use constraint programming?
-The answer is obvious:  we are constraint programmers, or to borrow Mark Twain's words "To a man with a hammer, everything looks like a nail." But actually, constraint programming has been a good way to go.
+The answer is obvious:  we are constraint programmers, or to borrow Mark Twain's words ``To a man with a hammer, everything looks like a nail." But actually, constraint programming has been a good way to go.
 From an engineering perspective, it has allowed us to prototype solutions quickly and to build solutions incrementally.
 There is also an advantage that we might exploit in the future: we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
-That is, the constraint program might be used to design the next set of umpire's rules.
+That is, the constraint program might be used to design the next set of criteria for match race schedules, or allow the event organiser to decide which criteria he may sacrifice to ensure a faster schedule with less boat changes.
 

### 2015-04-07 paper.tex
Formatting changes only

@@
 \begin{abstract}
-We present a constraint programming solution to the problem of generating round-robin schedules for dinghy sailing match races.
-Our schedules satisfy the widely used ISAF World Sailing pairing lists match race criteria.
-We show that some published ISAF schedules are in fact illegal, and present corresponding legal instances and schedules that have not previously been published.
-Our schedules can be downloaded as blanks, then populated with actual competitors and used in ISAF competitions.
+We present a constraint programming solution to the problem of generating round-robin schedules for
+dinghy sailing match races. Our schedules satisfy the widely used ISAF World Sailing pairing lists
+match race criteria. We show that some published ISAF schedules are in fact illegal, and present
+corresponding legal instances and schedules that have not previously been published. Our schedules
+can be downloaded as blanks, then populated with actual competitors and used in ISAF competitions.
 \end{abstract}
@@
 \section{Introduction}
-%\coffee{1}
-This work describes a round robin competition format that arises from sailing, known as match racing.
-Competitors, i.e.
-{\em skippers}, compete against each other in a series of matches taking place in rounds, known as {\em flights}.
-A match is composed of two skippers, with each skipper in a boat on his own.
-Skippers in a match set off together, one on the port side, the other starboard, and first home wins that match.
-Criteria published by the Interational Sailing Federation (ISAF) dictate what makes a legal match race schedule and what should be optimised.
-This is a rich set of cirteria, 13 in all, and as far as we know, all published schedules have been produced by hand.
-This is a daunting task.
-A close inspection of these schedules reveals that most are illegal, violating many of the match race scheduling criteria, many schedules are missing and some that are legal are far from optimal.
 
-This paper describes the scheduling problem.
-We present a constraint programming solution and document how this model was constructed incrementally.
-We believe this illustrates how adaptable constraint programming is, i.e.
-given a fairly robust model this can be incrementally developed to address all of the required criteria.
-Our schedules are then constructed in a sequence of stages, not dissimilar to the hybrid and decomposition based approaches in \cite{lombardi2012}.
-Some ISAF published schedules are presented along with some of our own, some of these being new.
-These schedules are esentially blank forms, made available to event organisers, which can be filled in with names of actual competitors, i.e.\ these schedules are reusable.
+This work describes a round robin competition format that arises from sailing, known as match
+racing. Competitors, i.e. {\em skippers}, compete against each other in a series of matches taking
+place in rounds, known as {\em flights}.  A match is composed of two skippers, with each skipper in
+a boat on his own. Skippers in a match set off together, one on the port side, the other starboard,
+and first home wins that match. Criteria published by the Interational Sailing Federation (ISAF)
+dictate what makes a legal match race schedule and what should be optimised. This is a rich set of
+cirteria, 13 in all, and as far as we know, all published schedules have been produced by hand. This
+is a daunting task. A close inspection of these schedules reveals that most are illegal, violating
+many of the match race scheduling criteria, many schedules are missing and some that are legal are
+far from optimal.
 
-The paper is organised as follows: we present the 13 match racing rules and then the constraint models and four stages of schedule construction, schedules are then presented, there is then a discuss and we conclude.
+This paper describes the scheduling problem. We present a constraint programming solution and
+document how this model was constructed incrementally. We believe this illustrates how adaptable
+constraint programming is, i.e. given a fairly robust model this can be incrementally developed to
+address all of the required criteria. Our schedules are then constructed in a sequence of stages,
+not dissimilar to the hybrid and decomposition based approaches in \cite{lombardi2012}. Some ISAF
+published schedules are presented along with some of our own, some of these being new.  These
+schedules are esentially blank forms, made available to event organisers, which can be filled in
+with names of actual competitors, i.e.\ these schedules are reusable.
+
+The paper is organised as follows: we present the 13 match racing rules and then the constraint
+models and four stages of schedule construction, schedules are then presented, there is then a
+discuss and we conclude.
 
 \section{Problem Definition: Round Robin Pairing Lists}\label{sec:definition}
-The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the competing skippers are scheduled into flights and matches, known as pairing lists.
-Several of these criteria are applicable when the number of skippers exceeds the number of available boats, in which case skippers have to change in and out of boats, and are allowed time in the schedule to check and fine-tune the boat they change into.
-Typically, matches set off at 5 minute intervals with each match taking about 20 minutes.
-Therefore, if we have 10 skippers and 10 boats we have 45 matches.
-This results in 9 flights each of 5 matches.
-Each flight takes about 50 minutes, consequently eight or nine flights a day is a reasonable achievement for most events~\cite{isaf}.
-Consequently, the number of boats and skippers involved is typically small.
 
-The criteria for  match racing schedules (pairing lists) are given in ISAF ``International Umpires' and Match Racing Manual'' \cite{isaf}, section
-M.2 Recommended Criteria for Round Robin Pairing Lists, and are detailed below.
+The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the
+competing skippers are scheduled into flights and matches, known as pairing lists. Several of these
+criteria are applicable when the number of skippers exceeds the number of available boats, in which
+case skippers have to change in and out of boats, and are allowed time in the schedule to check and
+fine-tune the boat they change into. Typically, matches set off at 5 minute intervals with each
+match taking about 20 minutes. Therefore, if we have 10 skippers and 10 boats we have 45 matches.
+This results in 9 flights each of 5 matches.  Each flight takes about 50 minutes, consequently eight
+or nine flights a day is a reasonable achievement for most events~\cite{isaf}. Consequently, the
+number of boats and skippers involved is typically small.
+
+The criteria for  match racing schedules (pairing lists) are given in ISAF ``International Umpires'
+and Match Racing Manual'' \cite{isaf}, section M.2 Recommended Criteria for Round Robin Pairing
+Lists, and are detailed below.
 
@@
 \item Each skipper sails against each other skipper once.
-\item *When skippers have an even number of matches, they have the same number of port and starboard assignments.
-\item *When skippers have an odd number of matches, the first half of the skippers
-    will have one more starboard assignment.
-%\item When there is an even number of flights, each skipper has the same number
-%    of port and starboard assignments.
-%\item When there is an odd number of flights, the first half of the skippers
-%    will have one more starboard assignment.
-\item No skipper in the last match of a flight should be in the first match of
-    the next flight.
-\item No skipper should have more than two consecutive port or starboard
+\item *When skippers have an even number of matches, they have the same number of port and starboard
     assignments.
-\item Each skipper should be assigned to match 1, match 2, etc. in a flight as
-    equally as possible.
-\item In flights with five or more matches, no skipper should be in the
-    next-to-last match in a flight and then in the first match of the next
-    flight.
-\item If possible, a skipper should be starboard when meeting the nearest
-    lowest ranked skipper (i.e.\ \#1 will be starboard against \#2, \#3 will be
-    starboard against \#4).
+\item *When skippers have an odd number of matches, the first half of the skippers will have one
+    more starboard assignment.
+\item No skipper in the last match of a flight should be in the first match of the next flight.
+\item No skipper should have more than two consecutive port or starboard assignments.
+\item Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
+\item In flights with five or more matches, no skipper should be in the next-to-last match in a
+    flight and then in the first match of the next flight.
+\item If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper
+    (i.e.\ \#1 will be starboard against \#2, \#3 will be starboard against \#4).
 \item Close-ranked skippers meet in the last flight.
@@
 \end{enumerate}
-Note that criteria 10, 11 and 12 only apply when there are fewer boats than
-skippers; 11 and 12 override 6 when changes are required.
+Note that criteria 10, 11 and 12 only apply when there are fewer boats than skippers; 11 and 12
+override 6 when changes are required.
 \end{framed}
 
-We have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}.
-Note that the order of matches within a flight is significant and is constrained, as is the order of flights within a schedule and the position of skippers within a match.
-This permits fair schedules that provide the sufficient changeover time for skippers changing boats, etc.
+We have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}. Note that the
+order of matches within a flight is significant and is constrained, as is the order of flights
+within a schedule and the position of skippers within a match. This permits fair schedules that
+provide the sufficient changeover time for skippers changing boats, etc.
 
-Criteria 12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match (i.e.
-it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange all his kit and set the boat to his preference before racing commences, and this is a boat change.
+Criteria 12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match
+(i.e. it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a
+boat, rearrange all his kit and set the boat to his preference before racing commences, and this is
+a boat change.
 
-Next, we note that skippers can be ranked prior to an event -- based on their performance in previous events\footnote{\url{http://www.sailing.org/rankings/match/}} -- which is used to seed the skippers.
-The ordering of skippers within a match signifies their starting position (port or starboard) -- as skippers allocated the starboard starting position gain a small competitive advantage in that match - criteria 8 accomplishes the seedings.
+Next, we note that skippers can be ranked prior to an event -- based on their performance in
+previous events\footnote{\url{http://www.sailing.org/rankings/match/}} -- which is used to seed the
+skippers. The ordering of skippers within a match signifies their starting position (port or
+starboard) -- as skippers allocated the starboard starting position gain a small competitive
+advantage in that match - criteria 8 accomplishes the seedings.
 
-Criteria 10 is ambiguous: - this could be interpreted on a schedule basis: i.e.\ to minimise the overall number of changes in the entire pairing list schedule; or alternatively as well as a fair, but minimal number of changes across all skippers.
-In our work, we take the latter viewpoint.
+Criteria 10 is ambiguous: - this could be interpreted on a schedule basis: i.e.\ to minimise the
+overall number of changes in the entire pairing list schedule; or alternatively as well as a fair,
+but minimal number of changes across all skippers. In our work, we take the latter viewpoint.
 
-There are some conflicts inherent in the rules.
-Take criteria 4 and 11, assume we have 4 boats, and in flight $i$ the last match is the pair of skippers ($x,y$).
-Criteria 11 dictates that skippers $x$ and $y$ must appear in the next flight, $i+1$, and criteria 4 that neither can be first in the next flight.
-This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating criteria 1.
-Therefore, although not explicitly stated, there are no legal schedules with less than 6 boats.
+There are some conflicts inherent in the rules. Take criteria 4 and 11, assume we have 4 boats, and
+in flight $i$ the last match is the pair of skippers ($x,y$). Criteria 11 dictates that skippers $x$
+and $y$ must appear in the next flight, $i+1$, and criteria 4 that neither can be first in the next
+flight. This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating
+criteria 1. Therefore, although not explicitly stated, there are no legal schedules with less than 6
+boats.
 
@@
 
-The schedules are produced in four stages. The first stage produces a schedule
-that respects criteria 1, 4, 11 and 12, and minimises criteria 10 (boat
-changes). The second stage constructs a schedule that respects criteria 1, 4,
-11, 12 (again), has criteria 10 as a hard constraint generated from first
-stage, and minimises criteria 6 (balance). This results in a schedule that
-attempts to minimise boat changes \emph{and} balance. The third stage satisfies
-criteria 9, and is a simple translation of the schedule produced in stage 2.
-The final stage orients skippers within matches to address criteria 2, 3, 5
-and 8.
+The schedules are produced in four stages. The first stage produces a schedule that respects
+criteria 1, 4, 11 and 12, and minimises criteria 10 (boat changes). The second stage constructs a
+schedule that respects criteria 1, 4, 11, 12 (again), has criteria 10 as a hard constraint generated
+from first stage, and minimises criteria 6 (balance). This results in a schedule that attempts to
+minimise boat changes \emph{and} balance. The third stage satisfies criteria 9, and is a simple
+translation of the schedule produced in stage 2.  The final stage orients skippers within matches to
+address criteria 2, 3, 5 and 8.
 
-We now describe the constraint models and processes used in each stage. In the
-text below we assume there are $n$ skippers and $b$ boats, with $m = b/2$
-matches in a flight. In total there are $t = n(n-1)/2$ matches and $f = \lceil
-n(n-1)/m  \rceil$ flights. We use the schedule in Table~\ref{tab1}, for 7
-skippers and 6 boats, to help illustrate the constraint models. Our
-descriptions of the models omit some minor details, however the models are
-available to download\footnote{?? give us a link to the models}.
+We now describe the constraint models and processes used in each stage. In the text below we assume
+there are $n$ skippers and $b$ boats, with $m = b/2$ matches in a flight. In total there are $t =
+n(n-1)/2$ matches and $f = \lceil n(n-1)/m  \rceil$ flights. We use the schedule in
+Table~\ref{tab1}, for 7 skippers and 6 boats, to help illustrate the constraint models. Our
+descriptions of the models omit some minor details, however the models are available to
+download\footnote{?? give us a link to the models}.
 
@@
     \end{tabular}
-    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.
-        Skippers are numbered 0 to 6. Note that the order of skippers within a flight
-        is significant, as is position within a match (port or starboard). This
-        schedule is the result of stages 1 and 2, and has yet to be renumbered and
-        oriented (stages 3 and 4).} \label{tab1}
+    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights.  Skippers are numbered 0
+        to 6. Note that the order of skippers within a flight is significant, as is position within
+        a match (port or starboard). This schedule is the result of stages 1 and 2, and has yet to
+        be renumbered and oriented (stages 3 and 4).} \label{tab1}
 \end{SCtable}
@@
 \paragraph{Modeling skippers:} The first thing we model, in the first half of
-Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal
-view of his schedule in the array of constrained integer variables
-$\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state view in the array of
-constraint integer variables $\state[0]$ to $\state[{f-1}]$. The state of this
-skipper in flight $i$ is found in $\state[i]$, and this corresponds to
-timeslots $\timeSlot[{i \cdot m}]$ to $\timeSlot[{m(i+1)-1}]$.
+Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal view of his schedule
+in the array of constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state view
+in the array of constraint integer variables $\state[0]$ to $\state[{f-1}]$. The state of this
+skipper in flight $i$ is found in $\state[i]$, and this corresponds to timeslots $\timeSlot[{i \cdot
+m}]$ to $\timeSlot[{m(i+1)-1}]$.
 
@@
 \end{framed}
-\caption{Our constraint model, from a skipper perspective (top) and a match and
-temporal perspective (below). The number of skippers is $n$, and $m$ is the
-number of matches in a flight. The number of flights is $f = \lceil n(n-1)/m
-\rceil$, and there are $t = n(n-1)/2$ matches in total.}\label{model:stage1}
+\caption{Our constraint model, from a skipper perspective (top) and a match and temporal perspective
+(below). The number of skippers is $n$, and $m$ is the number of matches in a flight. The number of
+flights is $f = \lceil n(n-1)/m \rceil$, and there are $t = n(n-1)/2$ matches in
+total.}\label{model:stage1}
 \end{figure}
 
-In \eqref{var:timeSlot} the array $\timeSlot$ is defined and in
-\eqref{var:state}, $\state$ is defined. If variable $\timeSlot[{i}] = k$ and $k
-\geq 0$ then this skipper is in a match with skipper~$k$ at time~$i$. Variable
-$\state[{i}]$ gives the state of this skipper in flight~$i$. The cases in
-\eqref{C1} say that a skipper can be in a match in the first time slot in the
-flight, or in the middle of the flight\footnote{\ldots actually, not first and
-not last.}, or in the last time slot of the flight. Alternatively, if all time
-slots in a flight are equal to $-1$ then the skipper is in a bye, and if all time
-slots in a flight are equal to $-2$ then the skipper has finished all his
-matches.
+In \eqref{var:timeSlot} the array $\timeSlot$ is defined and in \eqref{var:state}, $\state$ is
+defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with
+skipper~$k$ at time~$i$. Variable $\state[{i}]$ gives the state of this skipper in flight~$i$. The
+cases in \eqref{C1} say that a skipper can be in a match in the first time slot in the flight, or in
+the middle of the flight\footnote{\ldots actually, not first and not last.}, or in the last time
+slot of the flight. Alternatively, if all time slots in a flight are equal to $-1$ then the skipper
+is in a bye, and if all time slots in a flight are equal to $-2$ then the skipper has finished all
+his matches.
 
-We must then ensure that each skipper $\sigma$ is in a match with all other
-skippers $\{0, \nldots, n-1\} \setminus \{\sigma\}$. This is \eqref{C2}, which
-may be implemented by imposing a global cardinality constraint \cite{globCard}
-on the array $\timeSlot$.
+We must then ensure that each skipper $\sigma$ is in a match with all other skippers $\{0, \nldots,
+n-1\} \setminus \{\sigma\}$. This is \eqref{C2}, which may be implemented by imposing a global
+cardinality constraint \cite{globCard} on the array $\timeSlot$.
 
-\paragraph{State transitions:} The $\state$ variables are then used to impose
-match race criteria 4 (if last in flight $i$ then not first in flight $i+1$),
-criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$) and
-criteria 12 (if flight $i$ is a bye then flight $i$ is not first).  These
-criteria are imposed by \eqref{C3}, which is a deterministic finite automata
-(DFA) constraint \cite{Pesant04}. The transitions for the DFA are shown
-pictorially in Figure~\ref{skipper5}: arcs represent a transition from one
-state to another. The DFA is encoded as a set of transition objects $\langle
-q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to
-state $q_{j}$ when encountering input $\iota$. In addition we specify the
-accepting states, which are all states except the start state (white) and the
-bye state (pink).  This constraint also ensures that if a skipper has finished
-his matches in flight $i$ (i.e.\ $\END$) then he has finished his matches in
+\paragraph{State transitions:} The $\state$ variables are then used to impose match race criteria 4
+(if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not
+in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first).
+These criteria are imposed by \eqref{C3}, which is a deterministic finite automata (DFA) constraint
+\cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
+represent a transition from one state to another. The DFA is encoded as a set of transition objects
+$\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to state $q_{j}$
+when encountering input $\iota$. In addition we specify the accepting states, which are all states
+except the start state (white) and the bye state (pink).  This constraint also ensures that if a
+skipper has finished his matches in flight $i$ (i.e.\ $\END$) then he has finished his matches in
 flight $i+1$ (and so on).
 
-Figure~\ref{skipper5} also shows the skipper-oriented variables and constraints
-corresponding to skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array
-is presented as coloured boxes, and below that is the $\timeSlot$ array. The
-arrows represent the channeling constraints \eqref{C1}. The
-$\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue
-for $\FIRST$, red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of
-Table~\ref{tab1} is reproduced with the matches for skipper 5 emboldened.
+Figure~\ref{skipper5} also shows the skipper-oriented variables and constraints corresponding to
+skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array is presented as coloured boxes, and
+below that is the $\timeSlot$ array. The arrows represent the channeling constraints \eqref{C1}. The
+$\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue for $\FIRST$,
+red for $\LAST$ and (not shown) pink for $\BYE$. The schedule of Table~\ref{tab1} is reproduced with
+the matches for skipper 5 emboldened.
 
-\paragraph{Boat changes:} A boat change occurs when a skipper has been in a
-$\BYE$ state in flight $i$ and then is in a match in the next flight $i+1$.
-This is encoded using the array of zero/one variables \eqref{V3}, and the
-constraint \eqref{C4}, and accumulated into $\totalChanges$
+\paragraph{Boat changes:} A boat change occurs when a skipper has been in a $\BYE$ state in flight
+$i$ and then is in a match in the next flight $i+1$.  This is encoded using the array of zero/one
+variables \eqref{V3}, and the constraint \eqref{C4}, and accumulated into $\totalChanges$
 (\ref{V4},~\ref{C5}).
@@
     \end{tikzpicture}
-    \caption{A pictorial representation of a skipper (skipper 5) with multicoloured
-        state and grey timeslots. The schedule for skipper 5 is in bold and the
-        deterministic finite automata for criteria 4, 11 and 12 is drawn with state
-        $\START$ in white, $\FIRST$ in blue, $\MID$ in yellow, $\LAST$ in green, $\BYE$
-    in pink and $\END$ in red.}\label{skipper5}
+    \caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey
+        timeslots. The schedule for skipper 5 is in bold and the deterministic finite automata for
+        criteria 4, 11 and 12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
+        yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}\label{skipper5}
 \end{figure}
 
-\paragraph{Match perspective:} We are now in a position to model criteria 1
-(each skipper sails against every other skipper) and optimisation criteria 10
-(minimise boat changes).  In the second half of Figure~\ref{model:stage1} we
-present a match perspective of the schedule, using a two dimensional array of
-variables $\match$ \eqref{V5}, where $\match[{i,j}]$ is the time slot that
-skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet in a match. Only the half above
-the diagonal is represented, and the lower half is made up of exactly the same
-variables, i.e.\ $\match[{i,j}]$ is \emph{exactly} the same constrained
-variable as $\match[{j,i}]$. Constraint \eqref{C6} states that  a match between
-skippers $\sigma[{i}]$ and $\sigma[{j}]$ takes place at time $k$ (i.e.\
-$\match[{i,j}] = k$) if and only if  skipper $\sigma[{i}]$'s $k^{th}$ time slot
-is skipper $\sigma[{j}]$ and conversely that skipper $\sigma[{j}]$'s $k^{th}$
-time slot is skipper $\sigma[{i}]$). Variables \eqref{V6} and constraints
-\eqref{C7} then convert this from time slots to flights, i.e.\
-$\modMatch[{i,j}]$ is the flight in which skippers $\sigma[{i}]$ and
-$\sigma[{j}]$ meet for a match. Finally, constraint \eqref{C8} ensures that
-each skipper's match occurs in different flights. Also, since $\modMatch[{i,j}]
-\equiv \modMatch[{j,i}]$, setting rows to be all different also ensures that
-columns are all different.
+\paragraph{Match perspective:} We are now in a position to model criteria 1 (each skipper sails
+against every other skipper) and optimisation criteria 10 (minimise boat changes).  In the second
+half of Figure~\ref{model:stage1} we present a match perspective of the schedule, using a two
+dimensional array of variables $\match$ \eqref{V5}, where $\match[{i,j}]$ is the time slot that
+skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet in a match. Only the half above the diagonal is
+represented, and the lower half is made up of exactly the same variables, i.e.\ $\match[{i,j}]$ is
+\emph{exactly} the same constrained variable as $\match[{j,i}]$. Constraint \eqref{C6} states that
+a match between skippers $\sigma[{i}]$ and $\sigma[{j}]$ takes place at time $k$ (i.e.\
+$\match[{i,j}] = k$) if and only if  skipper $\sigma[{i}]$'s $k^{th}$ time slot is skipper
+$\sigma[{j}]$ and conversely that skipper $\sigma[{j}]$'s $k^{th}$ time slot is skipper
+$\sigma[{i}]$). Variables \eqref{V6} and constraints \eqref{C7} then convert this from time slots to
+flights, i.e.\ $\modMatch[{i,j}]$ is the flight in which skippers $\sigma[{i}]$ and $\sigma[{j}]$
+meet for a match. Finally, constraint \eqref{C8} ensures that each skipper's match occurs in
+different flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows to be all
+different also ensures that columns are all different.
 
-\paragraph{Temporal perspective:} We now take a temporal view \eqref{V7}, such
-that $\timeVar[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers
-$\sigma[{i}]$ and $\sigma[{j}]$ are in a match. We channel between the match
-perspective and the temporal perspective using \eqref{C9}.
+\paragraph{Temporal perspective:} We now take a temporal view \eqref{V7}, such that
+$\timeVar[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $\sigma[{i}]$ and
+$\sigma[{j}]$ are in a match. We channel between the match perspective and the temporal perspective
+using \eqref{C9}.
 
-\paragraph{Optimisation criteria:} Finally we have the optimisation criteria
-(criteria 10) to minimise the number of boat changes. This is handled by
-\eqref{V8} and \eqref{C10}.
+\paragraph{Optimisation criteria:} Finally we have the optimisation criteria (criteria 10) to
+minimise the number of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
 
-\paragraph{Decision variables:} The decision variables are $\timeVar[{0}]$ to
-$\timeVar[{t-1}]$, i.e.\ for each time slot we decide what match takes place. A
-symmetry break is made at the top of search by forcing the first round to
-contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i \in \{0 \nldots
-{m-1}\} : \match[{2i, 2i+1}] = i$.
+\paragraph{Decision variables:} The decision variables are $\timeVar[{0}]$ to $\timeVar[{t-1}]$,
+i.e.\ for each time slot we decide what match takes place. A symmetry break is made at the top of
+search by forcing the first round to contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i
+\in \{0 \nldots {m-1}\} : \match[{2i, 2i+1}] = i$.
 
-\bigskip \noindent
-Figure \ref{schedChanges} gives a pictorial view of the entire model, using the
-7 skipper and 6 boat problem. On the right we have the 7 skippers with their
-states and time slots. Again, top right, we give the schedule actually
-produced.  Middle left we have the $\match$ array and at the bottom the
-$\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The
+\bigskip \noindent Figure \ref{schedChanges} gives a pictorial view of the entire model, using the 7
+skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots.
+Again, top right, we give the schedule actually produced.  Middle left we have the $\match$ array
+and at the bottom the $\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The
 yellow arrows show the channeling between parts of the model.
 
-The schedule presented has 6 boat changes: there are no boat changes in flight
-0 (first flight), in flight 1 skipper 6 has a boat change, in flight 2 skipper
-3 has a boat change, in flight 3 skipper 4, in flight 4 skipper 6, in flight 5
-skipper 0, and flight 6 skipper 1.
+The schedule presented has 6 boat changes: there are no boat changes in flight 0 (first flight), in
+flight 1 skipper 6 has a boat change, in flight 2 skipper 3 has a boat change, in flight 3 skipper
+4, in flight 4 skipper 6, in flight 5 skipper 0, and flight 6 skipper 1.
 
@@
 \includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
-\caption{A pictorial representation of the entire model of the schedule for 7
-skippers and 6 boats. The schedule is reproduced top right. On the right we
-have the 7 skippers, on top left the $\modMatch$ array, at the bottom
-$\timeVar$ and middle left the $\match$ array. The yellow arrows signify
-channeling between parts of the model.}
+\caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats.
+The schedule is reproduced top right. On the right we have the 7 skippers, on top left the
+$\modMatch$ array, at the bottom $\timeVar$ and middle left the $\match$ array. The yellow arrows
+signify channeling between parts of the model.}
 \label{schedChanges}
@@
 
-Having produced a schedule that minimises boat changes, we then minimise
-criteria 6, imbalance, by extending the model as in Figure~\ref{model:stage2}.
-Assuming the first stage produced a schedule with $\beta$ boat changes we post
-this as a hard constraint \eqref{C11} in stage 2. For each skipper $\sigma$ we
-introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is 1 if and
-only if skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the
-$i^{th}$ match of the  $j^{th}$ flight \eqref{C12}. Imbalance \eqref{V10} is then computed
-for each position, as the absolute amount of over or under
-expected presence in a given position \eqref{C13}. Finally, we compute the
-maximum imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
+Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance, by
+extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage produced a schedule
+with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage 2. For each skipper
+$\sigma$ we introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is 1 if and only if
+skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match of the  $j^{th}$
+flight \eqref{C12}. Imbalance \eqref{V10} is then computed for each position, as the absolute amount
+of over or under expected presence in a given position \eqref{C13}. Finally, we compute the maximum
+imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
 
@@
 \end{framed}
-\caption{Additions to the constraint model in Figure~\ref{model:stage1} for
-stage 2. The constant $\beta$ is the minimum number of boat changes found in
-stage 1.}\label{model:stage2}
+\caption{Additions to the constraint model in Figure~\ref{model:stage1} for stage 2. The constant
+$\beta$ is the minimum number of boat changes found in stage 1.}\label{model:stage2}
 \end{figure}
 
-We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13}
-and \ref{C15}) and minimise this \eqref{C16}. As before, the decision variables
-are $\timeVar[{0}]$ to $\timeVar[{t-1}]$ and the same symmetry breaking is
-imposed at top of search.
+We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13} and \ref{C15}) and
+minimise this \eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
+$\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
 
@@
 
-Stage 3 then takes as input the schedule produced in stage 2 and renames
-skippers in the last round of the last flight to be $(0,1)$, satisfying criteria
-9. This is a simple linear process. The schedule produced for 7 skippers and 6
-boats is shown in Table~\ref{tab2}.
+Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round
+of the last flight to be $(0,1)$, satisfying criteria 9. This is a simple linear process. The
+schedule produced for 7 skippers and 6 boats is shown in Table~\ref{tab2}.
 
@@
     \end{tabular}
-    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights,
-        which is the result of stages 1, 2, and 3. It has 6 boat changes
-        and imbalance 1. An example of imbalance is skipper $\sigma[{0}]$
-        with 2 matches in position 0 (first), 3 in position 1 and 1 (mid)
-        in position 2 (last). Perfect balance would be 2 matches in each
-    position, only achieved by skipper 2.}\label{tab2}
+    \caption{A round-robin schedule with 7 skippers, 6 boats and 7 flights, which is the result of
+        stages 1, 2, and 3. It has 6 boat changes and imbalance 1. An example of imbalance is
+        skipper $\sigma[{0}]$ with 2 matches in position 0 (first), 3 in position 1 and 1 (mid) in
+        position 2 (last). Perfect balance would be 2 matches in each position, only achieved by
+    skipper 2.}\label{tab2}
 \end{SCtable}
@@
 
-The final stage, stage 4, orients skippers within matches, such that they are
-either port (red) or starboard (green). This is done to satisfy criteria 2 and
-3, 5 and 8. A sketch of the constraint model is given with a supporting
-diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained integer
-variables, of length $n-1$, is produced for each skipper. These correspond to
-the sequence of skippers they meet in matches. For example, taking the schedule
-in Table~\ref{tab2}, skipper $\sigma[{2}]$ meets skippers in order:
-3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order 4,6,0,1,3,2.  Therefore,
-skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
-$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each
-skipper to enforce criteria 2 and 3 (equal number of port and starboard
-matches). Criteria 8 is enforced by posting constraints such that in a match
-($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher indexed skipper
-(lower ranked) is on the port side. A DFA constraint is posted for criteria 5
-(restricting sequences of port and starboard assignments).
+The final stage, stage 4, orients skippers within matches, such that they are either port (red) or
+starboard (green). This is done to satisfy criteria 2 and 3, 5 and 8. A sketch of the constraint
+model is given with a supporting diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained
+integer variables, of length $n-1$, is produced for each skipper. These correspond to the sequence
+of skippers they meet in matches. For example, taking the schedule in Table~\ref{tab2}, skipper
+$\sigma[{2}]$ meets skippers in order: 3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order
+4,6,0,1,3,2.  Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
+$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each skipper to enforce criteria
+2 and 3 (equal number of port and starboard matches). Criteria 8 is enforced by posting constraints
+such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher indexed
+skipper (lower ranked) is on the port side. A DFA constraint is posted for criteria 5 (restricting
+sequences of port and starboard assignments).
 
-In Figure~\ref{oriented}, port is red and starboard green. The sequence of
-zero/one variables for each skipper is shown on the left. Bottom right is the
-DFA, and top right is the final schedule produced from stages 1 to 4. The
-schedule has 6 boat changes and a maximum imbalance of 1. Three days CPU time
-was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
-schedule presented here is new, not appearing in the example schedules provided in \cite{isaf}.%ISAF World Sailing Umpire's Manual
+In Figure~\ref{oriented}, port is red and starboard green. The sequence of zero/one variables for
+each skipper is shown on the left. Bottom right is the DFA, and top right is the final schedule
+produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. Three
+days CPU time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
+schedule presented here is new, not appearing in the example schedules provided in \cite{isaf}.%ISAF
+World Sailing Umpire's Manual
 
@@
 \includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
-\caption{A pictorial representation of the orientation process, stage 4. Top
-right is the actual oriented schedule. Below that is the dfa to satisfy
-criteria 5. On the left is the zero/one variables, a row representing a
-skippers sequence of competitors. An edge between variables corresponds to a
-matched pair, that must take different values. Bottom right is a sketch by third author.}
-\label{oriented}
+\caption{A pictorial representation of the orientation process, stage 4. Top right is the actual
+oriented schedule. Below that is the dfa to satisfy criteria 5. On the left is the zero/one
+variables, a row representing a skippers sequence of competitors. An edge between variables
+corresponds to a matched pair, that must take different values. Bottom right is a sketch by third
+author.}\label{oriented}
 \end{figure}
@@
 \section{Sample Schedules}\label{sec:samples}
-We present three pairs of schedules.
-The first pair is for 8 skippers and 6 boats, one published by ISAF, the other generated by us.
-Next, we present two new schedules, not appearing in the ISAF manual, for 9 skippers and 6 boats and 9 skippers with 8 boats.
-The last pair is for 10 skippers and 6 boats, again ISAF published and generated by us.
-For each of our schedules, we used 1 day cpu time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
-Stages 3 and 4 (renaming and orientation) completed in less than a second.
+
+We present three pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
+ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF
+manual, for 9 skippers and 6 boats and 9 skippers with 8 boats. The last pair is for 10 skippers and
+6 boats, again ISAF published and generated by us. For each of our schedules, we used 1 day cpu time
+for the first stage (minimising boat changes) then a further 2 days to minimise imbalance. Stages 3
+and 4 (renaming and orientation) completed in less than a second.
 
@@
 \end{minipage}
-\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal) and on the right is our schedule.}
+\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal)
+and on the right is our schedule.}
 \label{08-06}
@@
 \subsection{8 skippers and 6 boats}
-We first analyse the ISAF schedule, Table \ref{08-06} on the left.
-Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on 3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7).
-Criteria 5 (no more than two consecutive port or starboard assignments) is violated for skipper 6 (flights 1 to 3) and 7 (flights 7 to 9).
-Criteria 6 (imbalance) is violated for skippers 6 and 8.
-Criteria 12  (new boats do not sail first) is violated in flight 9 for skipper 5.
-Finally, the schedule has 8 boat changes.
-Our schedule, Table \ref{08-06} on the right, respects all criteria and has 6 boat changes and a maximum imbalance of 1.
+
+We first analyse the ISAF schedule, Table \ref{08-06} on the
+left. Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on
+3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7). Criteria 5 (no
+more than two consecutive port or starboard assignments) is violated for skipper 6 (flights 1 to 3)
+and 7 (flights 7 to 9). Criteria 6 (imbalance) is violated for skippers 6 and 8. Criteria 12  (new
+boats do not sail first) is violated in flight 9 for skipper 5. Finally, the schedule has 8 boat
+changes. Our schedule, Table \ref{08-06} on the right, respects all criteria and has 6 boat changes
+and a maximum imbalance of 1.
 
 \subsection{9 skippers}
-Two new schedules are presented in Table \ref{09}, on the left for 6 boats and on the right 8 boats.
-Neither of these schedules appear in the ISAF Umpires' Manual.
-Both schedules respect all criteria.
-For 6 boats there are 8 boat changes (no skipper making more than 1 boat change) and a maximum imbalance of 2.
-For 8 boats there are again 8 boat changes, no skipper with more than 1 boat change, and perfect balance (each skipper 4 times on starboard side and 4 on port side).
+
+Two new schedules are presented in Table \ref{09}, on the left for 6 boats
+and on the right 8 boats. Neither of these schedules appear in the ISAF Umpires' Manual. Both
+schedules respect all criteria. For 6 boats there are 8 boat changes (no skipper making more than 1
+boat change) and a maximum imbalance of 2. For 8 boats there are again 8 boat changes, no skipper
+with more than 1 boat change, and perfect balance (each skipper 4 times on starboard side and 4 on
+port side).
 
@@
 \subsection{10 skippers and 6 boats}
-Table \ref{10-06} shows the ISAF schedule on the right for 10 skippers and 6 boats and on the right, our schedule.
-The ISAF schedule violates criteria 5 (no more than 2 consequitive port or starboard assignments) 10 times (twice for skipper 0, 1 and 6 and once for skippers 3, 7, 8 and 9).
-Criteria 12 (new boats do not sail first) is violated 7 times (in flight 3 for skippers 6 and 2, flight 5 for skipper 8, flight 6 for skipper 7, flight 8 for skipper 1, flight 9 for skipper 4 and flight 12 for skipper 4 again).
-There are 22 boat changes, with the minimum changes for a skipper being 1 and the maximum 3.
-Our schedule, right of Table \ref{10-06} satisfies all criteria, has 12 boat changes with the minimum changes for a skipper being 0 and the maximum 2, and a maximum imbalance of 1.
+
+Table \ref{10-06} shows the ISAF schedule on the right for 10 skippers and 6 boats and on the right,
+our schedule.  The ISAF schedule violates criteria 5 (no more than 2 consequitive port or starboard
+assignments) 10 times (twice for skipper 0, 1 and 6 and once for skippers 3, 7, 8 and 9).  Criteria
+12 (new boats do not sail first) is violated 7 times (in flight 3 for skippers 6 and 2, flight 5 for
+skipper 8, flight 6 for skipper 7, flight 8 for skipper 1, flight 9 for skipper 4 and flight 12 for
+skipper 4 again). There are 22 boat changes, with the minimum changes for a skipper being 1 and the
+maximum 3. Our schedule, right of Table \ref{10-06} satisfies all criteria, has 12 boat changes with
+the minimum changes for a skipper being 0 and the maximum 2, and a maximum imbalance of 1.
 
@@
 \subsection{Discussion}
-It was anticipated that this problem would be easy to model.
-This naivety was due to "round robin", leading us to believe that we could use some of the models proposed in \cite{trick2002}, \cite{trick2008} and \cite{henz2004}.
-This naivety slowly dissolved as we addressed more and more of the ISAF criteria.
-A number of models we produced were scrapped due to misunderstanding about the actual problem, i.e.
-a communication problem between the authors.
-Eventually this was resolved by presenting the majority of the criteria as a deterministic finite automaton.
-This became our Rosetta Stone, with the surprising benefit that it not only improved the teams communications, it was also a constraint!
 
-The staged approach was taken cautiously.
-We expected that isolating the orientation of schedules as a post-process might leave us with a hard or insoluble problem.
-So far, every schedule we have produced has been oriented with very little search, typically taking less than a second.
+It was anticipated that this problem would be easy to model. This naivety was due to "round robin",
+leading us to believe that we could use some of the models proposed in \cite{trick2002},
+\cite{trick2008} and \cite{henz2004}. This naivety slowly dissolved as we addressed more and more of
+the ISAF criteria. A number of models we produced were scrapped due to misunderstanding about the
+actual problem, i.e. a communication problem between the authors. Eventually this was resolved by
+presenting the majority of the criteria as a deterministic finite automaton. This became our Rosetta
+Stone, with the surprising benefit that it not only improved the teams communications, it was also a
+constraint!
 
-We used the choco constraint programming toolkit and one of our goals was to use only toolkit constraints, i.e.
-we wanted to see how far we could go without implementing our own specialised constraints.
-We are pleased to say that we did not have to do anything out of the box, although we did feel that we had used just about every constraint there was.
+The staged approach was taken cautiously. We expected that isolating the orientation of schedules as
+a post-process might leave us with a hard or insoluble problem. So far, every schedule we have
+produced has been oriented with very little search, typically taking less than a second.
 
-There are many redundant variables in our model.
-One of our first valid models was essentially that shown in Figure \ref{skipper5}, and did not use $modMatch$ and $match$ variables.
-Performance was hopeless, struggling to produce a 7 skipper 6 boat schedule in days.
-The $modMatch$ and $match$ variables were added.
-This improved domain filtering, and a flattened $match$ array was used as decision variables.
-That is, the decisions where ``when do we schedule this match?".
-At this point we had not yet produced a 9 skipper 6 boat schedule and we suspected that the combined criteria might exclude such a schedule.
-A non-constraint model was developed by the fourth author, primarily to prove that there was no schedule for 9 skippers with 6 boats.
-This program used a backtracking search with decision variables being positions within flights, i.e.
-time slots being assigned matches.
-Prior to search, symmetry breaking was performed, and at the top of search the matches in the first flight were set.
-A solution was found in seconds!
-With this experience we added in the $time$ variables, channeled these into the existing model and used these as decision variables, i.e.
-the question now was ``what match will we do now?".
-We also anchored the matches in the first flight.
-With these changes we began to produce schedules in acceptable time.
-The model was then built upon, incrementally adding criteria.
-This took a surprisingly short amount of time, sometimes minutes of coding to add in a new feature.
-The model was then enhanced so that it would address optimisation rather than just satisfaction, again a trivial programming task.
+We used the choco constraint programming toolkit and one of our goals was to use only toolkit
+constraints, i.e. we wanted to see how far we could go without implementing our own specialised
+constraints. We are pleased to say that we did not have to do anything out of the box, although we
+did feel that we had used just about every constraint there was.
 
-We have only reported a handful of our schedules, however there are missing schedules.
-Examples of these missing schedules are 10 skippers and 8 boats, 11 skippers with less than 10 boats, 12 skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with less than 10 boats.
-None of these schedules have been published by the ISAF, although we expect that they can be produced by selectively violating some of constraints.
-We have also not yet encoded criteria 7, addressing the situation of 10 or more boats.
-To do this we will have to modify the DFA constraint used in the first two stages.
+There are many redundant variables in our model. One of our first valid models was essentially that
+shown in Figure \ref{skipper5}, and did not use $modMatch$ and $match$ variables. Performance was
+hopeless, struggling to produce a 7 skipper 6 boat schedule in days. The $modMatch$ and $match$
+variables were added. This improved domain filtering, and a flattened $match$ array was used as
+decision variables. That is, the decisions where ``when do we schedule this match?".  At this point
+we had not yet produced a 9 skipper 6 boat schedule and we suspected that the combined criteria
+might exclude such a schedule. A non-constraint model was developed by the fourth author, primarily
+to prove that there was no schedule for 9 skippers with 6 boats. This program used a backtracking
+search with decision variables being positions within flights, i.e. time slots being assigned
+matches. Prior to search, symmetry breaking was performed, and at the top of search the matches in
+the first flight were set. A solution was found in seconds! With this experience we added in the
+$time$ variables, channeled these into the existing model and used these as decision variables, i.e.
+the question now was ``what match will we do now?". We also anchored the matches in the first
+flight. With these changes we began to produce schedules in acceptable time. The model was then
+built upon, incrementally adding criteria. This took a surprisingly short amount of time, sometimes
+minutes of coding to add in a new feature. The model was then enhanced so that it would address
+optimisation rather than just satisfaction, again a trivial programming task.
+
+We have only reported a handful of our schedules, however there are missing schedules. Examples of
+these missing schedules are 10 skippers and 8 boats, 11 skippers with less than 10 boats, 12
+skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with less than 10 boats. None of these
+schedules have been published by the ISAF, although we expect that they can be produced by
+selectively violating some of constraints. We have also not yet encoded criteria 7, addressing the
+situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the
+first two stages.
 
 \section{Conclusion}\label{sec:conclusions}
-We have produce new and better match race schedules.
-These schedules can be used by anyone that competes under the criteria published by ISAF.
-Our schedules can be downloaded as blank schedules and then populated with the names of the actual competing skippers.
 
-So, why did we use constraint programming?
-The answer is obvious:  we are constraint programmers, or to borrow Mark Twain's words ``To a man with a hammer, everything looks like a nail." But actually, constraint programming has been a good way to go.
-From an engineering perspective, it has allowed us to prototype solutions quickly and to build solutions incrementally.
-There is also an advantage that we might exploit in the future: we can now investigate the effect different criteria have on our ability to produce schedules and how relaxation of those affect optimisation criteria.
-That is, the constraint program might be used to design the next set of criteria for match race schedules, or allow the event organiser to decide which criteria he may sacrifice to ensure a faster schedule with less boat changes.
+We have produce new and better match race schedules. These schedules can be used by anyone that
+competes under the criteria published by ISAF. Our schedules can be downloaded as blank schedules
+and then populated with the names of the actual competing skippers.
 
-%\section*{Acknowledgments}
-%We would like to thank our parents, God, and all his angels.
-%\coffee{2}
+So, why did we use constraint programming? The answer is obvious:  we are constraint programmers, or
+to borrow Mark Twain's words ``To a man with a hammer, everything looks like a nail." But actually,
+constraint programming has been a good way to go. From an engineering perspective, it has allowed us
+to prototype solutions quickly and to build solutions incrementally. There is also an advantage that
+we might exploit in the future: we can now investigate the effect different criteria have on our
+ability to produce schedules and how relaxation of those affect optimisation criteria. That is, the
+constraint program might be used to design the next set of criteria for match race schedules, or
+allow the event organiser to decide which criteria he may sacrifice to ensure a faster schedule with
+less boat changes.
 

### 2015-04-07 paper.tex
Spelling

@@
 a boat on his own. Skippers in a match set off together, one on the port side, the other starboard,
-and first home wins that match. Criteria published by the Interational Sailing Federation (ISAF)
+and first home wins that match. Criteria published by the International Sailing Federation (ISAF)
 dictate what makes a legal match race schedule and what should be optimised. This is a rich set of
-cirteria, 13 in all, and as far as we know, all published schedules have been produced by hand. This
+criteria, 13 in all, and as far as we know, all published schedules have been produced by hand. This
 is a daunting task. A close inspection of these schedules reveals that most are illegal, violating
@@
 published schedules are presented along with some of our own, some of these being new.  These
-schedules are esentially blank forms, made available to event organisers, which can be filled in
+schedules are essentially blank forms, made available to event organisers, which can be filled in
 with names of actual competitors, i.e.\ these schedules are reusable.
@@
 Table \ref{10-06} shows the ISAF schedule on the right for 10 skippers and 6 boats and on the right,
-our schedule.  The ISAF schedule violates criteria 5 (no more than 2 consequitive port or starboard
+our schedule.  The ISAF schedule violates criteria 5 (no more than 2 consecutive port or starboard
 assignments) 10 times (twice for skipper 0, 1 and 6 and once for skippers 3, 7, 8 and 9).  Criteria

### 2015-04-07 paper.tex
Unused
LaTeX tweaks

@@
 \usepackage{framed}
-%\usepackage{coffee2}
 \usepackage{tikz}
-
-\usepackage{color}
-\newcommand{\todo}[1]{\textcolor{blue}{#1}}
 
@@
 This work describes a round robin competition format that arises from sailing, known as match
-racing. Competitors, i.e. {\em skippers}, compete against each other in a series of matches taking
-place in rounds, known as {\em flights}.  A match is composed of two skippers, with each skipper in
+racing. Competitors, i.e.\ \emph{skippers}, compete against each other in a series of matches taking
+place in rounds, known as \emph{flights}.  A match is composed of two skippers, with each skipper in
 a boat on his own. Skippers in a match set off together, one on the port side, the other starboard,
@@
 is a daunting task. A close inspection of these schedules reveals that most are illegal, violating
-many of the match race scheduling criteria, many schedules are missing and some that are legal are
+many of the match race scheduling criteria, many schedules are missing, and some that are legal are
 far from optimal.
@@
 document how this model was constructed incrementally. We believe this illustrates how adaptable
-constraint programming is, i.e. given a fairly robust model this can be incrementally developed to
+constraint programming is, i.e.\ given a fairly robust model this can be incrementally developed to
 address all of the required criteria. Our schedules are then constructed in a sequence of stages,
@@
 
-Next, we note that skippers can be ranked prior to an event -- based on their performance in
-previous events\footnote{\url{http://www.sailing.org/rankings/match/}} -- which is used to seed the
+Next, we note that skippers can be ranked prior to an event, based on their performance in
+previous events\footnote{\url{http://www.sailing.org/rankings/match/}}, which is used to seed the
 skippers. The ordering of skippers within a match signifies their starting position (port or
-starboard) -- as skippers allocated the starboard starting position gain a small competitive
-advantage in that match - criteria 8 accomplishes the seedings.
+starboard), as skippers allocated the starboard starting position gain a small competitive
+advantage in that match---criteria 8 accomplishes the seedings.
 
-Criteria 10 is ambiguous: - this could be interpreted on a schedule basis: i.e.\ to minimise the
+Criteria 10 is ambiguous: this could be interpreted on a schedule basis: i.e.\ to minimise the
 overall number of changes in the entire pairing list schedule; or alternatively as well as a fair,
@@
 days CPU time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
-schedule presented here is new, not appearing in the example schedules provided in \cite{isaf}.%ISAF
-World Sailing Umpire's Manual
+schedule presented here is new, not appearing in the example schedules provided in \cite{isaf}.
 
@@
 manual, for 9 skippers and 6 boats and 9 skippers with 8 boats. The last pair is for 10 skippers and
-6 boats, again ISAF published and generated by us. For each of our schedules, we used 1 day cpu time
+6 boats, again ISAF published and generated by us. For each of our schedules, we used 1 day CPU time
 for the first stage (minimising boat changes) then a further 2 days to minimise imbalance. Stages 3
@@
 \begin{minipage}[t]{0.5\textwidth}
-\hspace{0.6cm}
-%\begin{scriptsize}
+    \centering
 \begin{tabular}{cccc}
@@
     \end{tabular}
-%\end{scriptsize}
 \label{08-06a}
@@
     \end{tabular}
-%\end{scriptsize}
 \label{08-06b}
 \end{minipage}
-\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal)
+\caption{Schedules for 8 skippers and 6 boats. On the left, the published ISAF schedule (illegal),
 and on the right is our schedule.}
@@
 
-\noindent
-\subsection{8 skippers and 6 boats}
-
-We first analyse the ISAF schedule, Table \ref{08-06} on the
+\paragraph{8 skippers and 6 boats:} We first analyse the ISAF schedule, Table~\ref{08-06} on the
 left. Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on
@@
 boats do not sail first) is violated in flight 9 for skipper 5. Finally, the schedule has 8 boat
-changes. Our schedule, Table \ref{08-06} on the right, respects all criteria and has 6 boat changes
+changes. Our schedule, Table~\ref{08-06} on the right, respects all criteria and has 6 boat changes
 and a maximum imbalance of 1.
 
-\subsection{9 skippers}
-
-Two new schedules are presented in Table \ref{09}, on the left for 6 boats
+\paragraph{9 skippers}: Two new schedules are presented in Table~\ref{09}, on the left for 6 boats
 and on the right 8 boats. Neither of these schedules appear in the ISAF Umpires' Manual. Both
@@
 \begin{minipage}[t]{0.5\textwidth}
-\hspace{0.6cm}
-%\begin{scriptsize}
+\centering
 \begin{tabular}{cccc}
@@
     \end{tabular}
-%\end{scriptsize}
+\centering
 \label{09-06}
 \end{minipage}
-%\hfill
+\hfill
 \begin{minipage}[t]{0.5\textwidth}
-\hspace{0.6cm}
-%\begin{scriptsize}
+\centering
 \begin{tabular}{ccccc}
@@
     \end{tabular}
-%\end{scriptsize}
 \label{09-08}
 \end{minipage}
-\caption{Two new schedules. On the left, 9 skippers and 6 boats and on the right 9 skippers and 8 boats.}
+\caption{Two new schedules. On the left, 9 skippers and 6 boats, and on the right 9 skippers and 8 boats.}
 \label{09}
@@
 
-\subsection{10 skippers and 6 boats}
-
-Table \ref{10-06} shows the ISAF schedule on the right for 10 skippers and 6 boats and on the right,
-our schedule.  The ISAF schedule violates criteria 5 (no more than 2 consecutive port or starboard
-assignments) 10 times (twice for skipper 0, 1 and 6 and once for skippers 3, 7, 8 and 9).  Criteria
-12 (new boats do not sail first) is violated 7 times (in flight 3 for skippers 6 and 2, flight 5 for
-skipper 8, flight 6 for skipper 7, flight 8 for skipper 1, flight 9 for skipper 4 and flight 12 for
-skipper 4 again). There are 22 boat changes, with the minimum changes for a skipper being 1 and the
-maximum 3. Our schedule, right of Table \ref{10-06} satisfies all criteria, has 12 boat changes with
-the minimum changes for a skipper being 0 and the maximum 2, and a maximum imbalance of 1.
+\paragraph{10 skippers and 6 boats:} Table \ref{10-06} shows the ISAF schedule on the right for 10
+skippers and 6 boats and on the right, our schedule.  The ISAF schedule violates criteria 5 (no more
+than 2 consecutive port or starboard assignments) 10 times (twice for skipper 0, 1 and 6 and once
+for skippers 3, 7, 8 and 9).  Criteria 12 (new boats do not sail first) is violated 7 times (in
+flight 3 for skippers 6 and 2, flight 5 for skipper 8, flight 6 for skipper 7, flight 8 for skipper
+1, flight 9 for skipper 4 and flight 12 for skipper 4 again). There are 22 boat changes, with the
+minimum changes for a skipper being 1 and the maximum 3. Our schedule, right of Table \ref{10-06}
+satisfies all criteria, has 12 boat changes with the minimum changes for a skipper being 0 and the
+maximum 2, and a maximum imbalance of 1.
 
@@
 \end{tabular}
-%\end{scriptsize}
 \label{10-06a}
 \end{minipage}
-%\hfill
+\hfill
 \begin{minipage}[t]{0.5\textwidth}
-\hspace{0.6cm}
-%\begin{scriptsize}
+\centering
 \begin{tabular}{ccccc}
@@
 \end{tabular}
-%\end{scriptsize}
 \label{10-06b}
 \end{minipage}
-\caption{Schedules for 10 skippers and 6 boats. On the left, the ISAF published schedule (illegal) and on the right, our schedule.}
+\caption{Schedules for 10 skippers and 6 boats. On the left, the ISAF published schedule (illegal),
+and on the right, our schedule.}
 \label{10-06}
@@
 
-\subsection{Discussion}
+\section{Discussion}
 
-It was anticipated that this problem would be easy to model. This naivety was due to "round robin",
-leading us to believe that we could use some of the models proposed in \cite{trick2002},
+It was anticipated that this problem would be easy to model. This naivety was due to ``round
+robin'', leading us to believe that we could use some of the models proposed in \cite{trick2002},
 \cite{trick2008} and \cite{henz2004}. This naivety slowly dissolved as we addressed more and more of
 the ISAF criteria. A number of models we produced were scrapped due to misunderstanding about the
-actual problem, i.e. a communication problem between the authors. Eventually this was resolved by
+actual problem, i.e.\ a communication problem between the authors. Eventually this was resolved by
 presenting the majority of the criteria as a deterministic finite automaton. This became our Rosetta
@@
 We used the choco constraint programming toolkit and one of our goals was to use only toolkit
-constraints, i.e. we wanted to see how far we could go without implementing our own specialised
+constraints, i.e.\ we wanted to see how far we could go without implementing our own specialised
 constraints. We are pleased to say that we did not have to do anything out of the box, although we
@@
 There are many redundant variables in our model. One of our first valid models was essentially that
-shown in Figure \ref{skipper5}, and did not use $modMatch$ and $match$ variables. Performance was
-hopeless, struggling to produce a 7 skipper 6 boat schedule in days. The $modMatch$ and $match$
-variables were added. This improved domain filtering, and a flattened $match$ array was used as
-decision variables. That is, the decisions where ``when do we schedule this match?".  At this point
+shown in Figure~\ref{skipper5}, and did not use $\modMatch$ and $\match$ variables. Performance was
+hopeless, struggling to produce a 7 skipper 6 boat schedule in days. The $\modMatch$ and $\match$
+variables were added. This improved domain filtering, and a flattened $\match$ array was used as
+decision variables. That is, the decisions where ``when do we schedule this match?''.  At this point
 we had not yet produced a 9 skipper 6 boat schedule and we suspected that the combined criteria
@@
 to prove that there was no schedule for 9 skippers with 6 boats. This program used a backtracking
-search with decision variables being positions within flights, i.e. time slots being assigned
+search with decision variables being positions within flights, i.e.\ time slots being assigned
 matches. Prior to search, symmetry breaking was performed, and at the top of search the matches in
 the first flight were set. A solution was found in seconds! With this experience we added in the
-$time$ variables, channeled these into the existing model and used these as decision variables, i.e.
-the question now was ``what match will we do now?". We also anchored the matches in the first
+$time$ variables, channeled these into the existing model and used these as decision variables,
+i.e.\ the question now was ``what match will we do now?''. We also anchored the matches in the first
 flight. With these changes we began to produce schedules in acceptable time. The model was then
@@
 So, why did we use constraint programming? The answer is obvious:  we are constraint programmers, or
-to borrow Mark Twain's words ``To a man with a hammer, everything looks like a nail." But actually,
+to borrow Mark Twain's words ``To a man with a hammer, everything looks like a nail''. But actually,
 constraint programming has been a good way to go. From an engineering perspective, it has allowed us

### 2015-04-07 paper.tex
Indenting
Automaton, criterion

@@
 \begin{framed}
-Principal Criteria in Order of Priority:
+\noindent Principal Criteria in Order of Priority:
 \begin{enumerate}
@@
 \end{enumerate}
-Note that criteria 10, 11 and 12 only apply when there are fewer boats than skippers; 11 and 12
-override 6 when changes are required.
+Note that criteria~10, 11 and~12 only apply when there are fewer boats than skippers; 11 and~12
+override~6 when changes are required.
 \end{framed}
 
-We have rephrased criteria 2 \& 3 (denoted *) to clarify an error in \cite{isaf}. Note that the
+We have rephrased criteria~2 and~3 (denoted *) to clarify an error in \cite{isaf}. Note that the
 order of matches within a flight is significant and is constrained, as is the order of flights
@@
 
-Criteria 12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match
+Criterion~12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match
 (i.e. it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a
@@
 starboard), as skippers allocated the starboard starting position gain a small competitive
-advantage in that match---criteria 8 accomplishes the seedings.
+advantage in that match---criterion~8 accomplishes the seedings.
 
-Criteria 10 is ambiguous: this could be interpreted on a schedule basis: i.e.\ to minimise the
+Criterion~10 is ambiguous: this could be interpreted on a schedule basis: i.e.\ to minimise the
 overall number of changes in the entire pairing list schedule; or alternatively as well as a fair,
@@
 
-There are some conflicts inherent in the rules. Take criteria 4 and 11, assume we have 4 boats, and
-in flight $i$ the last match is the pair of skippers ($x,y$). Criteria 11 dictates that skippers $x$
-and $y$ must appear in the next flight, $i+1$, and criteria 4 that neither can be first in the next
+There are some conflicts inherent in the rules. Take criteria~4 and~11, assume we have 4 boats, and
+in flight $i$ the last match is the pair of skippers ($x,y$). Criterion~11 dictates that skippers $x$
+and $y$ must appear in the next flight, $i+1$, and criterion~4 that neither can be first in the next
 flight. This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating
-criteria 1. Therefore, although not explicitly stated, there are no legal schedules with less than 6
+criterion~1. Therefore, although not explicitly stated, there are no legal schedules with less than 6
 boats.
@@
 The schedules are produced in four stages. The first stage produces a schedule that respects
-criteria 1, 4, 11 and 12, and minimises criteria 10 (boat changes). The second stage constructs a
-schedule that respects criteria 1, 4, 11, 12 (again), has criteria 10 as a hard constraint generated
-from first stage, and minimises criteria 6 (balance). This results in a schedule that attempts to
-minimise boat changes \emph{and} balance. The third stage satisfies criteria 9, and is a simple
+criteria~1, 4, 11 and~12, and minimises criteria~10 (boat changes). The second stage constructs a
+schedule that respects criteria~1, 4, 11, 12 (again), has criterion~10 as a hard constraint generated
+from first stage, and minimises criterion~6 (balance). This results in a schedule that attempts to
+minimise boat changes \emph{and} balance. The third stage satisfies criterion~9, and is a simple
 translation of the schedule produced in stage 2.  The final stage orients skippers within matches to
-address criteria 2, 3, 5 and 8.
+address criteria~2, 3, 5 and~8.
 
@@
 
-\paragraph{State transitions:} The $\state$ variables are then used to impose match race criteria 4
-(if last in flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$ then not
-in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then flight $i$ is not first).
-These criteria are imposed by \eqref{C3}, which is a deterministic finite automata (DFA) constraint
+\paragraph{State transitions:} The $\state$ variables are then used to impose match race criterion~4
+(if last in flight $i$ then not first in flight $i+1$), criterion~11 (if last in flight $i$ then not
+in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i$ is not first).
+These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint
 \cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
@@
     \caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey
-        timeslots. The schedule for skipper 5 is in bold and the deterministic finite automata for
-        criteria 4, 11 and 12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
+        timeslots. The schedule for skipper 5 is in bold and the deterministic finite automaton for
+        criteria~4, 11 and~12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
         yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}\label{skipper5}
@@
 
-\paragraph{Match perspective:} We are now in a position to model criteria 1 (each skipper sails
-against every other skipper) and optimisation criteria 10 (minimise boat changes).  In the second
+\paragraph{Match perspective:} We are now in a position to model criterion~1 (each skipper sails
+against every other skipper) and optimisation criterion~10 (minimise boat changes).  In the second
 half of Figure~\ref{model:stage1} we present a match perspective of the schedule, using a two
@@
 
-\paragraph{Optimisation criteria:} Finally we have the optimisation criteria (criteria 10) to
+\paragraph{Optimisation criteria:} Finally we have the optimisation criterion (criterion~10) to
 minimise the number of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
@@
 
-Having produced a schedule that minimises boat changes, we then minimise criteria 6, imbalance, by
+Having produced a schedule that minimises boat changes, we then minimise criterion~6, imbalance, by
 extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage produced a schedule
@@
 Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round
-of the last flight to be $(0,1)$, satisfying criteria 9. This is a simple linear process. The
+of the last flight to be $(0,1)$, satisfying criterion~9. This is a simple linear process. The
 schedule produced for 7 skippers and 6 boats is shown in Table~\ref{tab2}.
@@
 The final stage, stage 4, orients skippers within matches, such that they are either port (red) or
-starboard (green). This is done to satisfy criteria 2 and 3, 5 and 8. A sketch of the constraint
+starboard (green). This is done to satisfy criteria~2 and~3, 5 and~8. A sketch of the constraint
 model is given with a supporting diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained
@@
 4,6,0,1,3,2.  Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
-$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each skipper to enforce criteria
-2 and 3 (equal number of port and starboard matches). Criteria 8 is enforced by posting constraints
-such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher indexed
-skipper (lower ranked) is on the port side. A DFA constraint is posted for criteria 5 (restricting
-sequences of port and starboard assignments).
+$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each skipper to enforce
+criteria~2 and~3 (equal number of port and starboard matches). Criterion~8 is enforced by posting
+constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher
+indexed skipper (lower ranked) is on the port side. A DFA constraint is posted for criterion~5
+(restricting sequences of port and starboard assignments).
 
@@
 \caption{A pictorial representation of the orientation process, stage 4. Top right is the actual
-oriented schedule. Below that is the dfa to satisfy criteria 5. On the left is the zero/one
+oriented schedule. Below that is the DFA to satisfy criterion~5. On the left is the zero/one
 variables, a row representing a skippers sequence of competitors. An edge between variables
@@
 \paragraph{8 skippers and 6 boats:} We first analyse the ISAF schedule, Table~\ref{08-06} on the
-left. Criteria 4 (skippers in last match in a flight cannot be first in next flight) is violated on
-3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7). Criteria 5 (no
+left. Criterion~4 (skippers in last match in a flight cannot be first in next flight) is violated on
+3 occasions (skipper 1 in flight 3, skipper 7 in flight 4, skipper 0 in flight 7). Criterion~5 (no
 more than two consecutive port or starboard assignments) is violated for skipper 6 (flights 1 to 3)
-and 7 (flights 7 to 9). Criteria 6 (imbalance) is violated for skippers 6 and 8. Criteria 12  (new
+and 7 (flights 7 to 9). Criterion~6 (imbalance) is violated for skippers 6 and 8. Criterion~12  (new
 boats do not sail first) is violated in flight 9 for skipper 5. Finally, the schedule has 8 boat
@@
 \paragraph{10 skippers and 6 boats:} Table \ref{10-06} shows the ISAF schedule on the right for 10
-skippers and 6 boats and on the right, our schedule.  The ISAF schedule violates criteria 5 (no more
+skippers and 6 boats and on the right, our schedule.  The ISAF schedule violates criterion~5 (no more
 than 2 consecutive port or starboard assignments) 10 times (twice for skipper 0, 1 and 6 and once
-for skippers 3, 7, 8 and 9).  Criteria 12 (new boats do not sail first) is violated 7 times (in
+for skippers 3, 7, 8 and 9).  Criterion~12 (new boats do not sail first) is violated 7 times (in
 flight 3 for skippers 6 and 2, flight 5 for skipper 8, flight 6 for skipper 7, flight 8 for skipper
@@
 schedules have been published by the ISAF, although we expect that they can be produced by
-selectively violating some of constraints. We have also not yet encoded criteria 7, addressing the
+selectively violating some of constraints. We have also not yet encoded criterion~7, addressing the
 situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the

### 2015-04-07 paper.tex
Alice doesn't like that paragraph

@@
 
-The paper is organised as follows: we present the 13 match racing rules and then the constraint
-models and four stages of schedule construction, schedules are then presented, there is then a
-discuss and we conclude.
+The paper is organised as follows: we introduce the 13 match racing rules, then explain the
+constraint models and four stages of schedule construction, and then schedules are presented. We
+finish with discussion and a conclusion.
 

### 2015-04-07 paper.tex
Most of Alice's changes

@@
 flight. This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating
-criterion~1. Therefore, although not explicitly stated, there are no legal schedules with less than 6
+criterion~1. Therefore, although not explicitly stated, there are no legal schedules with fewer than 6
 boats.
@@
 skipper~$k$ at time~$i$. Variable $\state[{i}]$ gives the state of this skipper in flight~$i$. The
-cases in \eqref{C1} say that a skipper can be in a match in the first time slot in the flight, or in
-the middle of the flight\footnote{\ldots actually, not first and not last.}, or in the last time
+cases in \eqref{C1} state that a skipper can be in a match in the first time slot in the flight, or in
+the middle of the flight\footnote{i.e.\ not first and not last.}, or in the last time
 slot of the flight. Alternatively, if all time slots in a flight are equal to $-1$ then the skipper
@@
 (if last in flight $i$ then not first in flight $i+1$), criterion~11 (if last in flight $i$ then not
-in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i$ is not first).
+in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i+1$ is not first).
 These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint
 \cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
-represent a transition from one state to another. The DFA is encoded as a set of transition objects
+represent a possible transition from one state to another. The DFA is encoded as a set of transition objects
 $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to state $q_{j}$
@@
 except the start state (white) and the bye state (pink).  This constraint also ensures that if a
-skipper has finished his matches in flight $i$ (i.e.\ $\END$) then he has finished his matches in
-flight $i+1$ (and so on).
+skipper has finished his matches in flight $i$ (i.e.\ is in state $\END$) then he will also have
+finished his matches in flight $i+1$ (and so on).
 
 Figure~\ref{skipper5} also shows the skipper-oriented variables and constraints corresponding to
-skipper 5 in the Table~\ref{tab1} schedule. The $\state$ array is presented as coloured boxes, and
+skipper 5 in the schedule shown in Table~\ref{tab1}. The $\state$ array is presented as coloured boxes, and
 below that is the $\timeSlot$ array. The arrows represent the channeling constraints \eqref{C1}. The
@@
 half of Figure~\ref{model:stage1} we present a match perspective of the schedule, using a two
-dimensional array of variables $\match$ \eqref{V5}, where $\match[{i,j}]$ is the time slot that
+dimensional array of variables $\match$ \eqref{V5}, where $\match[{i,j}]$ is the time slot in which
 skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet in a match. Only the half above the diagonal is
@@
 
-Having produced a schedule that minimises boat changes, we then minimise criterion~6, imbalance, by
-extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage produced a schedule
-with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage 2. For each skipper
-$\sigma$ we introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is 1 if and only if
-skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match of the  $j^{th}$
-flight \eqref{C12}. Imbalance \eqref{V10} is then computed for each position, as the absolute amount
-of over or under expected presence in a given position \eqref{C13}. Finally, we compute the maximum
-imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
+Having produced a schedule that minimises boat changes, we then minimise imbalance (i.e.\ apply
+criterion~6) by extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage
+produces a schedule with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage
+2. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is
+1 if and only if skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
+of the  $j^{th}$ flight \eqref{C12}. Imbalance \eqref{V10} is then computed for each position, as
+the absolute amount over or under the expected presence in a given position \eqref{C13}. Finally, we
+compute the maximum imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
 
@@
 4,6,0,1,3,2.  Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
-$\sigma[{5}]$ 5$^{th}$ variable. There are summation constraints on each skipper to enforce
+$\sigma[{5}]$'s 5$^{th}$ variable. There are summation constraints on each skipper to enforce
 criteria~2 and~3 (equal number of port and starboard matches). Criterion~8 is enforced by posting
@@
 \paragraph{9 skippers}: Two new schedules are presented in Table~\ref{09}, on the left for 6 boats
-and on the right 8 boats. Neither of these schedules appear in the ISAF Umpires' Manual. Both
+and on the right for 8 boats. Neither of these schedules appear in the ISAF Umpires' Manual. Both
 schedules respect all criteria. For 6 boats there are 8 boat changes (no skipper making more than 1
@@
 
-It was anticipated that this problem would be easy to model. This naivety was due to ``round
-robin'', leading us to believe that we could use some of the models proposed in \cite{trick2002},
-\cite{trick2008} and \cite{henz2004}. This naivety slowly dissolved as we addressed more and more of
-the ISAF criteria. A number of models we produced were scrapped due to misunderstanding about the
-actual problem, i.e.\ a communication problem between the authors. Eventually this was resolved by
-presenting the majority of the criteria as a deterministic finite automaton. This became our Rosetta
-Stone, with the surprising benefit that it not only improved the teams communications, it was also a
-constraint!
+It was anticipated that this problem would be easy to model. This naivety was due to the use of the
+term ``round robin'' for these schedules, leading us to believe that we could use some of the models
+proposed in \cite{trick2002}, \cite{trick2008} and \cite{henz2004}. This naivety slowly dissolved as
+we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
+misunderstanding about the actual problem, i.e.\ a communication problem between the authors.
+Eventually this was resolved by presenting the majority of the criteria as a deterministic finite
+automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
+teams communications, it was also a constraint!
 
@@
 might exclude such a schedule. A non-constraint model was developed by the fourth author, primarily
-to prove that there was no schedule for 9 skippers with 6 boats. This program used a backtracking
-search with decision variables being positions within flights, i.e.\ time slots being assigned
-matches. Prior to search, symmetry breaking was performed, and at the top of search the matches in
-the first flight were set. A solution was found in seconds! With this experience we added in the
-$time$ variables, channeled these into the existing model and used these as decision variables,
-i.e.\ the question now was ``what match will we do now?''. We also anchored the matches in the first
-flight. With these changes we began to produce schedules in acceptable time. The model was then
-built upon, incrementally adding criteria. This took a surprisingly short amount of time, sometimes
-minutes of coding to add in a new feature. The model was then enhanced so that it would address
-optimisation rather than just satisfaction, again a trivial programming task.
+to attempt to prove that there was no schedule for 9 skippers with 6 boats. This program used a
+backtracking search with decision variables being positions within flights, i.e.\ time slots being
+assigned to matches. At the top of search, the matches in the first flight were set, and symmetry
+breaking was used to reduce the number of legal second flights. A solution was found in seconds!
+With this experience we added in the $\timeVar$ variables, channeled these into the existing model
+and used these as decision variables, i.e.\ the question now was ``what match will we do now?''. We
+also anchored the matches in the first flight. With these changes we began to produce schedules in
+acceptable time. The model was then built upon, incrementally adding criteria. This took a
+surprisingly short amount of time, sometimes minutes of coding to add in a new feature. The model
+was then enhanced so that it would address optimisation rather than just satisfaction, again a
+trivial programming task.
 

### 2015-04-07 paper.tex
Craig doesn't like fairlys

@@
 document how this model was constructed incrementally. We believe this illustrates how adaptable
-constraint programming is, i.e.\ given a fairly robust model this can be incrementally developed to
+constraint programming is, i.e.\ given a robust model this can be incrementally developed to
 address all of the required criteria. Our schedules are then constructed in a sequence of stages,

### 2015-04-07 paper.tex
Some of Craig's comments

@@
 Note that criteria~10, 11 and~12 only apply when there are fewer boats than skippers; 11 and~12
-override~6 when changes are required.
+override~6 when changes are required, and~13 applies when there are more boats than skippers.
 \end{framed}
@@
 
-Criterion~12 defines what is meant by a boat change: if in flight $i$ this skipper is not in a match
-(i.e. it is a bye for this skipper) but is in a match in flight $i+1$ then he has to get into a
-boat, rearrange all his kit and set the boat to his preference before racing commences, and this is
-a boat change.
+Criterion~12 discusses boat changes: if in flight $i$ this skipper is not in a match (i.e. it is a
+bye for this skipper) but is in a match in flight $i+1$ then he has to get into a boat, rearrange
+all his kit and set the boat to his preference before racing commences, and this is a boat change.
 
@@
 flight. This forces skippers $x$ and $y$ to compete in flight $i+1$ as the last match, violating
-criterion~1. Therefore, although not explicitly stated, there are no legal schedules with fewer than 6
-boats.
+criterion~1. Therefore, although not explicitly stated, it is not possible to satisfy every criteria
+with fewer than 6 boats.
 
@@
 
-The schedules are produced in four stages. The first stage produces a schedule that respects
+Our approach produces schedules in four stages. The first stage produces a schedule that respects
 criteria~1, 4, 11 and~12, and minimises criteria~10 (boat changes). The second stage constructs a
@@
 search by forcing the first round to contain the matches $(0,1), (2,3), \nldots$, i.e.\ $\forall i
-\in \{0 \nldots {m-1}\} : \match[{2i, 2i+1}] = i$.
+\in \{0 \nldots {m-1}\} : \match[{2i, 2i+1}] = i$. (This is independent of criterion~9, which will
+be enforced in a subsequent stage by renumbering.)
 
-\bigskip \noindent Figure \ref{schedChanges} gives a pictorial view of the entire model, using the 7
+\bigskip \noindent Figure~\ref{schedChanges} gives a pictorial view of the entire model, using the 7
 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots.

### 2015-04-08 paper.tex
Shrink some hboxes
Redraw another picture

@@
 
-\usetikzlibrary{shapes, shapes.multipart, arrows, positioning}
+\usetikzlibrary{shapes, shapes.multipart, arrows, positioning, calc}
 
@@
     \centering
-\includegraphics[height=10.2cm,width=13.2cm]{oriented.pdf}
+    \begin{tikzpicture}
+        \begin{scope}[every node/.style={minimum size=2em,inner sep=1}]
+            \node (R0N)                                                at (0.4,  0) { 0: };
+            \node (R00) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 1,  0)$) { 6 };
+            \node (R01) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 2,  0)$) { 2 };
+            \node (R02) [draw, circle, fill=uofglawn]                  at ($(1.2 * 3,  0)$) { 5 };
+            \node (R03) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4,  0)$) { 3 };
+            \node (R04) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 5,  0)$) { 4 };
+            \node (R05) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6,  0)$) { 1 };
+
+            \node (R1N)                                                at (0.4, -1) { 1: };
+            \node (R10) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -1)$) { 4 };
+            \node (R11) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -1)$) { 2 };
+            \node (R12) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -1)$) { 5 };
+            \node (R13) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -1)$) { 6 };
+            \node (R14) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 5, -1)$) { 3 };
+            \node (R15) [draw, circle, fill=uofglawn]                  at ($(1.2 * 6, -1)$) { 0 };
+
+            \node (R2N)                                                at (0.4, -2) { 2: };
+            \node (R20) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -2)$) { 3 };
+            \node (R21) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -2)$) { 0 };
+            \node (R22) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -2)$) { 1 };
+            \node (R23) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 4, -2)$) { 4 };
+            \node (R24) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -2)$) { 5 };
+            \node (R25) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6, -2)$) { 6 };
+
+            \node (R3N)                                                at (0.4, -3) { 3: };
+            \node (R30) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 1, -3)$) { 2 };
+            \node (R31) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -3)$) { 6 };
+            \node (R32) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -3)$) { 0 };
+            \node (R33) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 4, -3)$) { 5 };
+            \node (R34) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -3)$) { 1 };
+            \node (R35) [draw, circle, fill=uofglawn]                  at ($(1.2 * 6, -3)$) { 4 };
+
+            \node (R4N)                                                at (0.4, -4) { 4: };
+            \node (R40) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -4)$) { 5 };
+            \node (R41) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 2, -4)$) { 1 };
+            \node (R42) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -4)$) { 6 };
+            \node (R43) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -4)$) { 2 };
+            \node (R44) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -4)$) { 0 };
+            \node (R45) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6, -4)$) { 3 };
+
+            \node (R5N)                                                at (0.4, -5) { 5: };
+            \node (R50) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 1, -5)$) { 4 };
+            \node (R51) [draw, circle, fill=uofglawn]                  at ($(1.2 * 2, -5)$) { 6 };
+            \node (R52) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -5)$) { 0 };
+            \node (R53) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -5)$) { 1 };
+            \node (R54) [draw, circle, fill=uofglawn]                  at ($(1.2 * 5, -5)$) { 3 };
+            \node (R55) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 6, -5)$) { 2 };
+
+            \node (R6N)                                                at (0.4, -6) { 6: };
+            \node (R60) [draw, circle, fill=uofglawn]                  at ($(1.2 * 1, -6)$) { 0 };
+            \node (R61) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 2, -6)$) { 5 };
+            \node (R62) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 3, -6)$) { 3 };
+            \node (R63) [draw, circle, fill=uofglawn]                  at ($(1.2 * 4, -6)$) { 4 };
+            \node (R64) [draw, circle, fill=uofgpillarbox, text=white] at ($(1.2 * 5, -6)$) { 1 };
+            \node (R65) [draw, circle, fill=uofglawn]                  at ($(1.2 * 6, -6)$) { 2 };
+
+            \draw [thick] (R00) to [out=300, in=90] ($(R30) + (0.6, 0)$) to [out=270, in=60] (R60);
+            \draw [thick] (R10) to [out=300, in=120] (R41);
+            \draw [thick] (R20) to                   (R30);
+            \draw [thick] (R40) to                   (R50);
+
+            \draw [thick] (R01) to [out=230, in=130] (R21);
+            \draw [thick] (R11) to                   (R22);
+            \draw [thick] (R31) to [out=300, in=120] (R62);
+            \draw [thick] (R51) to                   (R61);
+
+            \draw [thick] (R02) to [out=245, in=115] (R52);
+            \draw [thick] (R12) to [out=300, in=120] (R53);
+            \draw [thick] (R32) to [out=45,  in=225] (R03);
+            \draw [thick] (R42) to                   (R63);
+
+            \draw [thick] (R13) to [out=300, in=120] (R64);
+            \draw [thick] (R23) to [out=230, in=130] (R43);
+            \draw [thick] (R33) to                   (R54);
+
+            \draw [thick] (R04) to [out=245, in=115] (R44);
+            \draw [thick] (R14) to [out=310, in=50]  (R34);
+            \draw [thick] (R24) to [out=300, in=120] (R55);
+
+            \draw [thick] (R05) to                   (R15);
+            \draw [thick] (R25) to [out=245, in=115] (R65);
+            \draw [thick] (R35) to                   (R45);
+        \end{scope}
+
+        \begin{scope}[every node/.style={minimum size=2em,inner sep=1}, xshift=8.7cm, yshift=-5cm]
+            \node (DFAI)  [draw, circle, fill=white]                     at (0,  0)   { \phantom{$P_1$} };
+            \node (DFAP1) [draw, circle, fill=uofgpillarbox, text=white] at (1,  0.6) { $P_1$ };
+            \node (DFAP2) [draw, circle, fill=uofgpillarbox, text=white] at (2,  0.6) { $P_2$ };
+            \node (DFAS1) [draw, circle, fill=uofglawn]                  at (1, -0.6) { $S_1$ };
+            \node (DFAS2) [draw, circle, fill=uofglawn]                  at (2, -0.6) { $S_2$ };
+
+            \draw [->, >=latex, thick]  (DFAI)  to (DFAP1);
+            \draw [->, >=latex, thick]  (DFAI)  to (DFAS1);
+            \draw [->, >=latex, thick]  (DFAP1) to (DFAP2);
+            \draw [<->, >=latex, thick] (DFAP1) to (DFAS1);
+            \draw [->, >=latex, thick]  (DFAS1) to (DFAS2);
+            \draw [->, >=latex, thick]  (DFAP2) to (DFAS1);
+            \draw [->, >=latex, thick]  (DFAS2) to (DFAP1);
+        \end{scope}
+
+        \begin{scope}
+            \node [anchor=north west] at (7.5, 0.3) {
+                \begin{minipage}{4.5cm}
+                    \centering
+                    \setlength{\tabcolsep}{3pt}
+                    \begin{tabular}{cccc}
+                        \toprule
+                        Flight & \multicolumn{3}{c}{Matches} \\[2pt] \midrule
+                        0 & (0,6) & (3,2) & (5,4) \\
+                        1 & (0,2) & (4,1) & (6,5) \\
+                        2 & (2,1) & (5,0) & (6,3) \\
+                        3 & (1,5) & (3,0) & (4,6) \\
+                        4 & (3,5) & (6,1) & (2,4) \\
+                        5 & (1,3) & (0,4) & (5,2) \\
+                        6 & (4,3) & (2,6) & (1,0) \\ \bottomrule
+                    \end{tabular}
+                \end{minipage}
+            };
+        \end{scope}
+
+    \end{tikzpicture}
     \caption{A pictorial representation of the orientation process, stage 4. Top right is the actual
         oriented schedule. Below that is the DFA to satisfy criterion~5. On the left is the zero/one
-variables, a row representing a skippers sequence of competitors. An edge between variables
-corresponds to a matched pair, that must take different values. Bottom right is a sketch by third
-author.}\label{oriented}
+        variables, a row representing a skipper's sequence of competitors. An edge between variables
+        corresponds to a matched pair, that must take different values.}\label{oriented}
 \end{figure}
@@
 \begin{figure}[h]
-\begin{minipage}[t]{0.5\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
     \centering
@@
 \hfill
-\begin{minipage}[t]{0.5\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
     \centering
@@
 \begin{figure}[h]
-\begin{minipage}[t]{0.5\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
 \centering
@@
 \hfill
-\begin{minipage}[t]{0.5\textwidth}
+\begin{minipage}[t]{0.48\textwidth}
 \centering

### 2015-04-08 paper.tex
Spacing

@@
 place in rounds, known as \emph{flights}.  A match is composed of two skippers, with each skipper in
-a boat on his own. Skippers in a match set off together, one on the port side, the other starboard,
+a boat on their own. Skippers in a match set off together, one on the port side, the other starboard,
 and first home wins that match. Criteria published by the International Sailing Federation (ISAF)
@@
 many of the match race scheduling criteria, many schedules are missing, and some that are legal are
-far from optimal.
+far from ISAF definition of optimality.
 
@@
 
+Criteron~6 allows us to measure the \emph{balance} of a schedule.
+Perfect balance would be when a skipper has as many matches in first position in flights as in second position in flights, and so on.
+For example, if we had 9 skippers and 8 boats, each skipper would have 8 matches and could be in the first, second, third or fourth match of a flight.
+In perfect balance, each of the 8 skippers would appear twice in each position.
+Balance is one of our optimisation criteria.
+
+Criterion~13 uses the term \emph{blanks} where conventionally we use the term \emph{bye}. That is, a blank is a bye and a bye is a flight where a skipper does not compete (and is ashore).
+
 Criterion~12 discusses boat changes: if in flight $i$ this skipper is not in a match (i.e. it is a
@@
 n(n-1)/2$ matches and $f = \lceil n(n-1)/m  \rceil$ flights. We use the schedule in
-Table~\ref{tab1}, for 7 skippers and 6 boats, to help illustrate the constraint models. Our
-descriptions of the models omit some minor details, however the models are available to
-download\footnote{?? give us a link to the models}.
+Table~\ref{tab1}, for 7 skippers and 6 boats, to help illustrate the constraint models.
 
@@
 \paragraph{Modeling skippers:} The first thing we model, in the first half of
-Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal view of his schedule
+Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal view of the schedule
 in the array of constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state view
 in the array of constraint integer variables $\state[0]$ to $\state[{f-1}]$. The state of this
-skipper in flight $i$ is found in $\state[i]$, and this corresponds to timeslots $\timeSlot[{i \cdot
+skipper in flight $i$ is found in $\state[i]$, and this corresponds to time slots $\timeSlot[{i \cdot
 m}]$ to $\timeSlot[{m(i+1)-1}]$.
@@
 slot of the flight. Alternatively, if all time slots in a flight are equal to $-1$ then the skipper
-is in a bye, and if all time slots in a flight are equal to $-2$ then the skipper has finished all
-his matches.
+is in a bye (i.e. not in a match in this flight), and if all time slots in a flight are equal to $-2$ then the skipper has finished all matches.
 
 We must then ensure that each skipper $\sigma$ is in a match with all other skippers $\{0, \nldots,
-n-1\} \setminus \{\sigma\}$. This is \eqref{C2}, which may be implemented by imposing a global
+n-1\} \setminus \{\sigma\}$. This is \eqref{C2}, which is enforced by imposing a global
 cardinality constraint \cite{globCard} on the array $\timeSlot$.
@@
 except the start state (white) and the bye state (pink).  This constraint also ensures that if a
-skipper has finished his matches in flight $i$ (i.e.\ is in state $\END$) then he will also have
-finished his matches in flight $i+1$ (and so on).
+skipper has finished all matches in flight $i$ (i.e.\ is in state $\END$) then that skipper will also have
+finished all matches in flight $i+1$ (and so on).
 
@@
                         \toprule
-                        Flight & \multicolumn{3}{c}{Matches} \\[2pt] \midrule
+                        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
                         0 & (0,6) & (3,2) & (5,4) \\
@@
 
-We present three pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
+We present four pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
 ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF
-manual, for 9 skippers and 6 boats and 9 skippers with 8 boats. The last pair is for 10 skippers and
-6 boats, again ISAF published and generated by us. For each of our schedules, we used 1 day CPU time
-for the first stage (minimising boat changes) then a further 2 days to minimise imbalance. Stages 3
-and 4 (renaming and orientation) completed in less than a second.
+manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and
+6 boats, again ISAF published and generated by us. Finalyy, we show what is a relatively easy problem, 8 skippers and 8 boats. 
+For each of our schedules (with the exception of the "easy-8" problem), we used 1 day CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
+Stages 3 and 4 (renaming and orientation) completed in less than a second.
 
@@
 more than two consecutive port or starboard assignments) is violated for skipper 6 (flights 1 to 3)
-and 7 (flights 7 to 9). Criterion~6 (imbalance) is violated for skippers 6 and 8. Criterion~12  (new
+and skipper 7 (flights 7 to 9). Criterion~6 (imbalance) is violated for skippers 6 and 8. Criterion~12  (new
 boats do not sail first) is violated in flight 9 for skipper 5. Finally, the schedule has 8 boat
@@
 boat change) and a maximum imbalance of 2. For 8 boats there are again 8 boat changes, no skipper
-with more than 1 boat change, and perfect balance (each skipper 4 times on starboard side and 4 on
-port side).
+with more than 1 boat change, and each skipper 4 times on starboard side and 4 on port side.
 
@@
 skippers and 6 boats and on the right, our schedule.  The ISAF schedule violates criterion~5 (no more
-than 2 consecutive port or starboard assignments) 10 times (twice for skipper 0, 1 and 6 and once
+than 2 consecutive port or starboard assignments) ten times (twice for skippers 0, 1 and 6 and once
 for skippers 3, 7, 8 and 9).  Criterion~12 (new boats do not sail first) is violated 7 times (in
@@
 1, flight 9 for skipper 4 and flight 12 for skipper 4 again). There are 22 boat changes, with the
-minimum changes for a skipper being 1 and the maximum 3. Our schedule, right of Table \ref{10-06}
+minimum changes for a skipper being 1 and the maximum 3. Our schedule, right of Table \ref{10-06},
 satisfies all criteria, has 12 boat changes with the minimum changes for a skipper being 0 and the
@@
 \begin{center}
+\begin{figure}[h]
+\begin{minipage}[t]{0.48\textwidth}
+    \centering
+\begin{tabular}{ccccc}
+        \toprule
+        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
+0 & (5,2) & (4,3) & (1,6) & (0,7) \\
+1 & (2,4) & (0,6) & (1,7) & (5,3) \\
+2 & (0,5) & (7,2) & (6,3) & (4,1) \\
+3 & (7,3) & (5,1) & (4,0) & (6,2) \\
+4 & (3,0) & (4,7) & (6,5) & (2,1) \\
+5 & (6,4) & (7,5) & (2,0) & (3,1) \\
+6 & (7,6) & (5,4) & (3,2) & (1,0) \\ \bottomrule
+    \end{tabular}
+\label{08-08a}
+\end{minipage}
+\hfill
+\begin{minipage}[t]{0.48\textwidth}
+    \centering
+\begin{tabular}{ccccc}
+        \toprule
+        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
+0 & (4,3) & (2,0) & (1,5) & (7,6) \\
+1 & (3,2) & (0,4) & (6,1) & (5,7) \\ 
+2 & (4,1) & (7,3) & (5,2) & (0,6) \\
+3 & (1,7) & (6,5) & (3,0) & (2,4) \\ 
+4 & (0,5) & (4,6) & (7,2) & (3,1) \\
+5 & (7,0) & (2,1) & (6,3) & (5,4) \\ 
+6 & (6,2) & (5,3) & (4,7) & (1,0) \\ \bottomrule
+    \end{tabular}
+\label{08-08b}
+\end{minipage}
+\caption{Schedules for 8 skippers and 8 boats. On the left, the published ISAF schedule (illegal),
+and on the right, our schedule.}
+\label{08-08}
+\end{figure}
+\end{center}
+
+\paragraph{8 skippers and 8 boats (easy-8):} Table \ref{08-08} shows the ISAF schedule on the right for 8
+skippers and 8 boats and on the right, our schedule.
+The ISAF schedule violates criterion~4 (last match in a flight cannot be first in next flight) for skipper 5 in flights 1 and 2.
+Also, criterion 5 (no skipper should have more than 2 consecutive port or starboard assignments) is violated for skippers 0, 1, 3, 4 and 6.
+Furthermore, skipper 1 appears in the last match of four flights resulting in significant imbalance.
+Our schedule, on the right, satisfies all criteria, is optimal (maximum imbalance of 1) and took less than 10 seconds in total (all stages) to produce.
+
+\begin{center}
 \begin{figure}[tb]
@@
 we had not yet produced a 9 skipper 6 boat schedule and we suspected that the combined criteria
-might exclude such a schedule. A non-constraint model was developed by the fourth author, primarily
+might exclude such a schedule. A non-constraint model was developed, primarily
 to attempt to prove that there was no schedule for 9 skippers with 6 boats. This program used a
@@
 constraint program might be used to design the next set of criteria for match race schedules, or
-allow the event organiser to decide which criteria he may sacrifice to ensure a faster schedule with
+allow the event organiser to decide which criteria to sacrifice to ensure a faster schedule with
 less boat changes.

### 2015-04-08 paper.tex
Clarified blank/bye, removed "he", deleted "... omit minor details ...", creared up "balance"

@@
 many of the match race scheduling criteria, many schedules are missing, and some that are legal are
-far from ISAF definition of optimality.
+far from optimal.
 
@@
 In perfect balance, each of the 8 skippers would appear twice in each position.
-Balance is one of our optimisation criteria.
 
@@
                         \toprule
-                        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+                        Flight & \multicolumn{3}{c}{Matches} \\[2pt] \midrule
                         0 & (0,6) & (3,2) & (5,4) \\
@@
 
-We present four pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
+We present three pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
 ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF
-manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and
-6 boats, again ISAF published and generated by us. Finalyy, we show what is a relatively easy problem, 8 skippers and 8 boats. 
-For each of our schedules (with the exception of the "easy-8" problem), we used 1 day CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
-Stages 3 and 4 (renaming and orientation) completed in less than a second.
+manual, for 9 skippers and 6 boats and 9 skippers with 8 boats. The last pair is for 10 skippers and
+6 boats, again ISAF published and generated by us. For each of our schedules, we used 1 day CPU time
+for the first stage (minimising boat changes) then a further 2 days to minimise imbalance. Stages 3
+and 4 (renaming and orientation) completed in less than a second.
 
@@
 \begin{center}
-\begin{figure}[h]
-\begin{minipage}[t]{0.48\textwidth}
-    \centering
-\begin{tabular}{ccccc}
-        \toprule
-        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
-0 & (5,2) & (4,3) & (1,6) & (0,7) \\
-1 & (2,4) & (0,6) & (1,7) & (5,3) \\
-2 & (0,5) & (7,2) & (6,3) & (4,1) \\
-3 & (7,3) & (5,1) & (4,0) & (6,2) \\
-4 & (3,0) & (4,7) & (6,5) & (2,1) \\
-5 & (6,4) & (7,5) & (2,0) & (3,1) \\
-6 & (7,6) & (5,4) & (3,2) & (1,0) \\ \bottomrule
-    \end{tabular}
-\label{08-08a}
-\end{minipage}
-\hfill
-\begin{minipage}[t]{0.48\textwidth}
-    \centering
-\begin{tabular}{ccccc}
-        \toprule
-        Flight & \multicolumn{4}{c}{Matches} \\ \midrule
-0 & (4,3) & (2,0) & (1,5) & (7,6) \\
-1 & (3,2) & (0,4) & (6,1) & (5,7) \\ 
-2 & (4,1) & (7,3) & (5,2) & (0,6) \\
-3 & (1,7) & (6,5) & (3,0) & (2,4) \\ 
-4 & (0,5) & (4,6) & (7,2) & (3,1) \\
-5 & (7,0) & (2,1) & (6,3) & (5,4) \\ 
-6 & (6,2) & (5,3) & (4,7) & (1,0) \\ \bottomrule
-    \end{tabular}
-\label{08-08b}
-\end{minipage}
-\caption{Schedules for 8 skippers and 8 boats. On the left, the published ISAF schedule (illegal),
-and on the right, our schedule.}
-\label{08-08}
-\end{figure}
-\end{center}
-
-\paragraph{8 skippers and 8 boats (easy-8):} Table \ref{08-08} shows the ISAF schedule on the right for 8
-skippers and 8 boats and on the right, our schedule.
-The ISAF schedule violates criterion~4 (last match in a flight cannot be first in next flight) for skipper 5 in flights 1 and 2.
-Also, criterion 5 (no skipper should have more than 2 consecutive port or starboard assignments) is violated for skippers 0, 1, 3, 4 and 6.
-Furthermore, skipper 1 appears in the last match of four flights resulting in significant imbalance.
-Our schedule, on the right, satisfies all criteria, is optimal (maximum imbalance of 1) and took less than 10 seconds in total (all stages) to produce.
-
-\begin{center}
 \begin{figure}[tb]

### 2015-04-08 paper.tex
added 08-08 schedule with critique

--- 2015-04-08 paper.tex
@@
         Flight & \multicolumn{4}{c}{Matches} \\ \midrule
-0 & (4,3) & (2,0) & (1,5) & (7,6) \\
-1 & (3,2) & (0,4) & (6,1) & (5,7) \\ 
-2 & (4,1) & (7,3) & (5,2) & (0,6) \\
-3 & (1,7) & (6,5) & (3,0) & (2,4) \\ 
-4 & (0,5) & (4,6) & (7,2) & (3,1) \\
-5 & (7,0) & (2,1) & (6,3) & (5,4) \\ 
-6 & (6,2) & (5,3) & (4,7) & (1,0) \\ \bottomrule
+0 & (2,5) & (4,3) & (6,1) & (7,0) \\
+1 & (4,2) & (6,0) & (7,1) & (5,3) \\ 
+2 & (0,5) & (2,7) & (3,6) & (1,4) \\ 
+3 & (3,7) & (5,1) & (4,0) & (6,2) \\ 
+4 & (0,3) & (7,4) & (6,5) & (2,1) \\
+5 & (4,6) & (5,7) & (0,2) & (1,3) \\ 
+6 & (7,6) & (5,4) & (3,2) & (1,0)  \\ \bottomrule
     \end{tabular}
@@
 Furthermore, skipper 1 appears in the last match of four flights resulting in significant imbalance.
-Our schedule, on the right, satisfies all criteria, is optimal (maximum imbalance of 1) and took less than 10 seconds in total (all stages) to produce.
+Our schedule, on the right, satisfies all criteria, is optimal and took less than 10 seconds in total (all stages) to produce.
 

### 2015-04-10 paper.tex
updated table 08-08 due to paranoia
Tried to clear up what we mean by "optimal" in 08-08
Redraw schedule figure

--- 2015-04-08 paper.tex
@@
 \usepackage{tikz}
+\usepackage{pdflscape}
+\usepackage{afterpage}
 
@@
 
-\begin{figure}[tb]
+\afterpage{\clearpage\begin{landscape}
+\begin{figure}[p]
     \centering
-\includegraphics[height=10.2cm,width=13.2cm]{schedule.pdf}
+    \begin{tikzpicture}
+        \begin{scope}
+            \node (Time) at (-2, 0) { $\timeVar$ };
+            \node (Time0) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (0, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (0,1)
+                \nodepart[text width=1.5em, align=center] {two}   (2,3)
+                \nodepart[text width=1.5em, align=center] {three} (4,5)
+            };
+            \node (Time1) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (2.2, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (0,2)
+                \nodepart[text width=1.5em, align=center] {two}   (4,6)
+                \nodepart[text width=1.5em, align=center] {three} (1,5)
+            };
+            \node (Time2) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (4.4, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (2,6)
+                \nodepart[text width=1.5em, align=center] {two}   (0,5)
+                \nodepart[text width=1.5em, align=center] {three} (1,3)
+            };
+            \node (Time3) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (6.6, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (5,6)
+                \nodepart[text width=1.5em, align=center] {two}   (0,3)
+                \nodepart[text width=1.5em, align=center] {three} (1,4)
+            };
+            \node (Time4) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (8.8, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (3,5)
+                \nodepart[text width=1.5em, align=center] {two}   (1,6)
+                \nodepart[text width=1.5em, align=center] {three} (2,4)
+            };
+            \node (Time5) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (11.0, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (3,6)
+                \nodepart[text width=1.5em, align=center] {two}   (0,4)
+                \nodepart[text width=1.5em, align=center] {three} (2,5)
+            };
+            \node (Time6) [font=\tiny, anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3] at (13.2, 0) {
+                \nodepart[text width=1.5em, align=center] {one}   (3,4)
+                \nodepart[text width=1.5em, align=center] {two}   (1,2)
+                \nodepart[text width=1.5em, align=center] {three} (0,6)
+            };
+        \end{scope}
+
+        \begin{scope}[yshift=5cm, xshift=-3.5cm]
+            \node [anchor=north west] (MatchTable) at (0, 0) {
+                \begin{minipage}{4.5cm}
+                    \centering
+                    \setlength{\aboverulesep}{0pt}
+                    \setlength{\belowrulesep}{0pt}
+                    \setlength{\extrarowheight}{.75ex}
+                    \setlength{\tabcolsep}{2pt}
+                    \begin{tabular}{cccccccc}
+                        & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\ \cmidrule{2-8}
+                        \multicolumn{1}{l@{\hspace{1em}}|}{0} & ~-~ & 0 & 3 & 10 & 16 & 7 & 20 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{1} & & ~-~ & 19 & 8 & 11 & 5 & 13 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{2} & & & ~-~ & 1 & 14 & 17 & 6 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{3} & & & & ~-~ & 18 & 12 & 15 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{4} & & & & & ~-~ & 2 & 4 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{5} & & & & & & ~-~ & 9 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{6} & & & & & & & ~-~ \\
+                    \end{tabular}
+                \end{minipage}
+            };
+            \node [above=-0.1 of MatchTable.north west, anchor=south west] (Match) { $\match$ };
+        \end{scope}
+
+        \begin{scope}[yshift=9.9cm, xshift=-3.5cm]
+            \node [anchor=north west] (ModMatchTable) at (0, 0) {
+                \begin{minipage}{4.5cm}
+                    \centering
+                    \setlength{\tabcolsep}{2pt}
+                    \setlength{\aboverulesep}{0pt}
+                    \setlength{\belowrulesep}{0pt}
+                    \setlength{\extrarowheight}{.75ex}
+                    \begin{tabular}{cccccccc}
+                        & 0 & 1 & 2 & 3 & 4 & 5 & 6 \\ \cmidrule{2-8}
+                        \multicolumn{1}{l@{\hspace{1em}}|}{0} & ~-~ & 0 & 1 & 3 & 5 & 2 & 6 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{1} & 0 & ~-~ & 6 & 2 & 3 & 1 & 4 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{2} & 1 & 6 & ~-~ & 0 & 4 & 5 & 2 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{3} & 3 & 2 & 0 & ~-~ & 6 & 4 & 5 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{4} & 5 & 3 & 4 & 6 & ~-~ & 0 & 1 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{5} & 2 & 1 & 5 & 4 & 0 & ~-~ & 3 \\
+                        \multicolumn{1}{l@{\hspace{1em}}|}{6} & 6 & 4 & 2 & 5 & 1 & 3 & ~-~ \\
+                    \end{tabular}
+                \end{minipage}
+            };
+            \node [above=-0.1 of ModMatchTable.north west, anchor=south west] (ModMatch) { $\modMatch$ };
+        \end{scope}
+
+        \begin{scope}[yshift=10.2cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~0}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofgcobalt,uofgcobalt,uofgsunshine,uofgsunshine,uofgthistle,uofgsunshine,uofglawn}] at (0, 0) {
+                \nodepart[text width=2em, align=center] {one}   \textsc{F}
+                \nodepart[text width=2em, align=center] {two}   \textsc{F}
+                \nodepart[text width=2em, align=center] {three} \textsc{M}
+                \nodepart[text width=2em, align=center] {four}  \textsc{M}
+                \nodepart[text width=2em, align=center, text=white] {five} \textsc{B}
+                \nodepart[text width=2em, align=center] {six}   \textsc{M}
+                \nodepart[text width=2em, align=center] {seven} \textsc{L}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 1
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 2
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 5
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 3
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 4
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 6
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}[yshift=8.8cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~1}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofgcobalt,uofglawn,uofglawn,uofglawn,uofgsunshine,uofgthistle,uofgsunshine}] at (0, 0) {
+                \nodepart[text width=2em, align=center] {one}   \textsc{F}
+                \nodepart[text width=2em, align=center] {two}   \textsc{L}
+                \nodepart[text width=2em, align=center] {three} \textsc{L}
+                \nodepart[text width=2em, align=center] {four}  \textsc{L}
+                \nodepart[text width=2em, align=center] {five}  \textsc{M}
+                \nodepart[text width=2em, align=center, text=white] {six}   \textsc{B}
+                \nodepart[text width=2em, align=center] {seven} \textsc{M}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 0
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 5
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 3
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 4
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 6
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 2
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}[yshift=7.4cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~2}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofgsunshine,uofgcobalt,uofgcobalt,uofgthistle,uofglawn,uofglawn,uofgsunshine}] at (0, 0) {
+                \nodepart[text width=2em, align=center] {one}   \textsc{M}
+                \nodepart[text width=2em, align=center] {two}   \textsc{F}
+                \nodepart[text width=2em, align=center] {three} \textsc{F}
+                \nodepart[text width=2em, align=center, text=white] {four}  \textsc{B}
+                \nodepart[text width=2em, align=center] {five}  \textsc{L}
+                \nodepart[text width=2em, align=center] {six}   \textsc{L}
+                \nodepart[text width=2em, align=center] {seven} \textsc{M}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 3
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 0
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 6
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 4
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 5
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 1
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}[yshift=6.0cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~3}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofgsunshine,uofgthistle,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofgcobalt}] at (0, 0) {
+                \nodepart[text width=2em, align=center] {one}   \textsc{M}
+                \nodepart[text width=2em, align=center, text=white] {two}   \textsc{B}
+                \nodepart[text width=2em, align=center] {three} \textsc{L}
+                \nodepart[text width=2em, align=center] {four}  \textsc{M}
+                \nodepart[text width=2em, align=center] {five}  \textsc{F}
+                \nodepart[text width=2em, align=center] {six}   \textsc{F}
+                \nodepart[text width=2em, align=center] {seven} \textsc{F}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 2
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 1
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 0
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 5
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 6
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 4
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}[yshift=4.6cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~4}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofglawn,uofgsunshine,uofgthistle,uofglawn,uofglawn,uofgsunshine,uofgcobalt}] at (0, 0) {
+                \nodepart[text width=2em, align=center] {one}   \textsc{L}
+                \nodepart[text width=2em, align=center] {two}   \textsc{M}
+                \nodepart[text width=2em, align=center, text=white] {three} \textsc{B}
+                \nodepart[text width=2em, align=center] {four}  \textsc{L}
+                \nodepart[text width=2em, align=center] {five}  \textsc{L}
+                \nodepart[text width=2em, align=center] {six}   \textsc{M}
+                \nodepart[text width=2em, align=center] {seven} \textsc{F}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 5
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 6
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 1
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 2
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 0
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 3
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}[yshift=3.2cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~5}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofglawn,uofglawn,uofgsunshine,uofgcobalt,uofgcobalt,uofglawn,uofgpillarbox}] at (0, 0) {
+                \nodepart[text width=2em, align=center] {one}   \textsc{L}
+                \nodepart[text width=2em, align=center] {two}   \textsc{L}
+                \nodepart[text width=2em, align=center] {three} \textsc{M}
+                \nodepart[text width=2em, align=center] {four}  \textsc{F}
+                \nodepart[text width=2em, align=center] {five}  \textsc{F}
+                \nodepart[text width=2em, align=center] {six}   \textsc{L}
+                \nodepart[text width=2em, align=center, text=white] {seven} \textsc{E}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 4
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 1
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 0
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 6
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 3
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 2
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}[yshift=1.8cm, xshift=6cm, scale=0.42, every node/.style={transform shape}]
+            \node at (-5, 0) { $\mathit{Skipper~6}$ };
+
+            \node (AllArray) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=7,
+            rectangle split part fill={uofgthistle,uofgsunshine,uofgcobalt,uofgcobalt,uofgsunshine,uofgcobalt,uofglawn}] at (0, 0) {
+                \nodepart[text width=2em, align=center, text=white] {one}   \textsc{B}
+                \nodepart[text width=2em, align=center] {two}   \textsc{M}
+                \nodepart[text width=2em, align=center] {three} \textsc{F}
+                \nodepart[text width=2em, align=center] {four}  \textsc{F}
+                \nodepart[text width=2em, align=center] {five}  \textsc{M}
+                \nodepart[text width=2em, align=center] {six}   \textsc{F}
+                \nodepart[text width=2em, align=center] {seven} \textsc{L}
+            };
+
+            \node (Array1) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-6, -2) {
+                \nodepart[text width=0.75em, align=center] {one} \phantom{1}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array2) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-4, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 4
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array3) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (-2, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 2
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array4) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (0, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 5
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array5) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (2, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two} 1
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array6) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (4, -2) {
+                \nodepart[text width=0.75em, align=center] {one} 3
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three}
+            };
+
+            \node (Array7) [anchor=center, draw, rectangle split, rectangle split horizontal, rectangle split parts=3,
+                rectangle split part fill={black!10!white,black!10!white,black!10!white}]  at (6, -2) {
+                \nodepart[text width=0.75em, align=center] {one}
+                \nodepart[text width=0.75em, align=center] {two}
+                \nodepart[text width=0.75em, align=center] {three} 0
+            };
+
+            \draw [<->, thick, >=latex] (AllArray.one south) to [in=50, out=230] (Array1.two north);
+            \draw [<->, thick, >=latex] (AllArray.two south) to [in=70, out=250] (Array2.two north);
+            \draw [<->, thick, >=latex] (AllArray.three south) to [in=90, out=270] (Array3.two north);
+            \draw [<->, thick, >=latex] (AllArray.four south) to [in=90, out=270] (Array4.two north);
+            \draw [<->, thick, >=latex] (AllArray.five south) to [in=90, out=270] (Array5.two north);
+            \draw [<->, thick, >=latex] (AllArray.six south) to [in=110, out=290] (Array6.two north);
+            \draw [<->, thick, >=latex] (AllArray.seven south) to [in=130, out=310] (Array7.two north);
+        \end{scope}
+
+        \begin{scope}
+            \node [anchor=north west] (Schedule) at (10.5, 8) {
+                \begin{minipage}{4.5cm}
+                    \centering
+                    \setlength{\tabcolsep}{3pt}
+                    \begin{tabular}{cccc}
+                        \toprule
+                        Flight & \multicolumn{3}{c}{Matches} \\ \midrule
+                        0 & (0,1) & (2,3) & (4,5) \\
+                        1 & (0,2) & (4,6) & (1,5) \\
+                        2 & (2,6) & (0,5) & (1,3) \\
+                        3 & (5,6) & (0,3) & (1,4) \\
+                        4 & (3,5) & (1,6) & (2,4) \\
+                        5 & (3,6) & (0,4) & (2,5) \\
+                        6 & (3,4) & (1,2) & (0,6) \\ \bottomrule
+                    \end{tabular}
+                \end{minipage}
+            };
+            \node [above=0 of Schedule.north west, anchor=south west] (Match) { \hspace*{1em}$\mathit{schedule}$ };
+        \end{scope}
+
+        \begin{scope}
+            \draw [<->, thick, >=latex] (-0.5, 5.1) to (-0.5, 5.7);
+            \draw [<->, thick, >=latex] (-0.5, 0.4) to (-0.5, 1.0);
+            \draw [<->, thick, >=latex] (1.6, 2.6) to (2.3, 2.6);
+        \end{scope}
+
+    \end{tikzpicture}
     \caption{A pictorial representation of the entire model of the schedule for 7 skippers and 6 boats.
-The schedule is reproduced top right. On the right we have the 7 skippers, on top left the
-$\modMatch$ array, at the bottom $\timeVar$ and middle left the $\match$ array. The yellow arrows
-signify channeling between parts of the model.}
+        The schedule is reproduced on the right. In the centre we have the 7 skippers, on left the
+        $\modMatch$ and $\match$ arrays, and along the bottom the $\timeVar$
+    array. The arrows signify channeling between parts of the model.}
     \label{schedChanges}
 \end{figure}
+\end{landscape}}
 

### 2015-04-13 paper.tex
Mucking around

@@
 
-\title{Constructing Sailing Match Race Schedules: Round Robin Pairing Lists}
+\title{Constructing Sailing Match Race Schedules: Round-Robin Pairing Lists}
 \titlerunning{Match Race Scheduling}
@@
 
-This work describes a round robin competition format that arises from sailing, known as match
+This work describes a round-robin competition format that arises from sailing, known as match
 racing. Competitors, i.e.\ \emph{skippers}, compete against each other in a series of matches taking
@@
 many of the match race scheduling criteria, many schedules are missing, and some that are legal are
-far from ISAF definition of optimality.
+far from the ISAF definition of optimality.
 
@@
 document how this model was constructed incrementally. We believe this illustrates how adaptable
-constraint programming is, i.e.\ given a robust model this can be incrementally developed to
-address all of the required criteria. Our schedules are then constructed in a sequence of stages,
-not dissimilar to the hybrid and decomposition based approaches in \cite{lombardi2012}. Some ISAF
+constraint programming is: a robust model can be developed incrementally to address all of the
+required criteria. Our schedules are then constructed in a sequence of stages, not dissimilar to the
+hybrid and decomposition based approaches by Lombardi and Milano \cite{lombardi2012}. Some ISAF
 published schedules are presented along with some of our own, some of these being new.  These
@@
 
-\section{Problem Definition: Round Robin Pairing Lists}\label{sec:definition}
+\section{Problem Definition: Round-Robin Pairing Lists}\label{sec:definition}
 
@@
 match taking about 20 minutes. Therefore, if we have 10 skippers and 10 boats we have 45 matches.
-This results in 9 flights each of 5 matches.  Each flight takes about 50 minutes, consequently eight
-or nine flights a day is a reasonable achievement for most events~\cite{isaf}. Consequently, the
-number of boats and skippers involved is typically small.
+This results in 9 flights each of 5 matches.  Each flight takes about 50 minutes, so eight or nine
+flights a day is a reasonable achievement for most events~\cite{isaf}. Consequently, the number of
+boats and skippers involved is typically small.
 
 The criteria for  match racing schedules (pairing lists) are given in ISAF ``International Umpires'
-and Match Racing Manual'' \cite{isaf}, section M.2 Recommended Criteria for Round Robin Pairing
-Lists, and are detailed below.
+and Match Racing Manual'' \cite{isaf}, section M.2 ``Recommended Criteria for Round Robin Pairing
+Lists'', and are detailed below.
 
@@
 \item Each skipper sails against each other skipper once.
-\item *When skippers have an even number of matches, they have the same number of port and starboard
+\item[2*.] When skippers have an even number of matches, they have the same number of port and starboard
     assignments.
-\item *When skippers have an odd number of matches, the first half of the skippers will have one
+\item[3*.] When skippers have an odd number of matches, the first half of the skippers will have one
     more starboard assignment.
@@
 
-We have rephrased criteria~2 and~3 (denoted *) to clarify an error in \cite{isaf}. Note that the
-order of matches within a flight is significant and is constrained, as is the order of flights
-within a schedule and the position of skippers within a match. This permits fair schedules that
-provide the sufficient changeover time for skippers changing boats, etc.
+We have rephrased criteria~2 and~3 (denoted *) to clarify an error in the manual \cite{isaf}. Note
+that the order of matches within a flight is significant and is constrained, as is the order of
+flights within a schedule and the position of skippers within a match. This permits fair schedules
+that provide the sufficient changeover time for skippers changing boats, etc.
 
@@
 \paragraph{Modeling skippers:} The first thing we model, in the first half of
-Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has a temporal view of the schedule
-in the array of constrained integer variables $\timeSlot[0]$ to $\timeSlot[{t-1}]$, and a state view
-in the array of constraint integer variables $\state[0]$ to $\state[{f-1}]$. The state of this
-skipper in flight $i$ is found in $\state[i]$, and this corresponds to time slots $\timeSlot[{i \cdot
-m}]$ to $\timeSlot[{m(i+1)-1}]$.
+Figure~\ref{model:stage1}, is a skipper. Each skipper $\sigma$ has both a temporal view of their
+schedule (``who, if anyone, am I racing in the match at time $t$?''), and a state view (``where am
+I racing within flight $f$?'').  The temporal view is via the array $\timeSlot$ defined in
+\eqref{var:timeSlot}. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a
+match with skipper~$k$ at time~$i$.
+
+Variable $\state[{i}]$ \eqref{var:state} gives the state of this skipper in flight~$i$,
+corresponding to time slots $\timeSlot[{m \cdot i}]$ to $\timeSlot[{m(i+1)-1}]$.
+The cases in \eqref{C1} state that a skipper can be in a match in the first time slot in the flight,
+or in the middle of the flight\footnote{i.e.\ not first and not last.}, or in the last time slot of
+the flight. Alternatively, if all time slots in a flight are equal to $-1$ then the skipper is in a
+bye (i.e. not in a match in this flight), and if all time slots in a flight are equal to $-2$ then
+the skipper has finished all matches.
 
@@
     & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} : \nonumber \\
-    & \hspace*{1em} \match[{i,j}] \in \{0..t{-}1\} \tag{V5} \label{V5} \\
+    & \hspace*{1em} \match[{i,j}] \in \{0 \nldots t{-}1\} \tag{V5} \label{V5} \\
     & \hspace*{1em} \match[{j,i}] \equiv \match[{i,j}] \nonumber \\
@@
     & \forall i \in \{0 \nldots n{-}2\} : \forall j \in \{ i{+}1 \nldots n{-}1 \} \nonumber : \\
-    & \hspace*{1em} \modMatch[{i,j}] \in \{0..f{-}1\} \label{V6} \tag{V6} \\
+    & \hspace*{1em} \modMatch[{i,j}] \in \{0 \nldots f{-}1\} \label{V6} \tag{V6} \\
     & \hspace*{1em} \modMatch[{j,i}] \equiv \modMatch[{i,j}] \nonumber  \\
@@
 
-In \eqref{var:timeSlot} the array $\timeSlot$ is defined and in \eqref{var:state}, $\state$ is
-defined. If variable $\timeSlot[{i}] = k$ and $k \geq 0$ then this skipper is in a match with
-skipper~$k$ at time~$i$. Variable $\state[{i}]$ gives the state of this skipper in flight~$i$. The
-cases in \eqref{C1} state that a skipper can be in a match in the first time slot in the flight, or in
-the middle of the flight\footnote{i.e.\ not first and not last.}, or in the last time
-slot of the flight. Alternatively, if all time slots in a flight are equal to $-1$ then the skipper
-is in a bye (i.e. not in a match in this flight), and if all time slots in a flight are equal to $-2$ then the skipper has finished all matches.
-
 We must then ensure that each skipper $\sigma$ is in a match with all other skippers $\{0, \nldots,
@@
 $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to state $q_{j}$
-when encountering input $\iota$. In addition we specify the accepting states, which are all states
+when encountering input~$\iota$. In addition we specify the accepting states, which are all states
 except the start state (white) and the bye state (pink).  This constraint also ensures that if a
@@
 skipper and 6 boat problem. On the right we have the 7 skippers with their states and time slots.
-Again, top right, we give the schedule actually produced.  Middle left we have the $\match$ array
-and at the bottom the $\timeVar$ array. Above the $match$ array we have the $\modMatch$ array. The
-yellow arrows show the channeling between parts of the model.
+Again, on the right we give the schedule actually produced. On the left we have the $\modMatch$ and
+$\match$ arrays, and at the bottom the $\timeVar$ array. The arrows show the channeling between
+parts of the model.
 
@@
 
-\afterpage{\clearpage\begin{landscape}
+\afterpage{\begin{landscape}
 \begin{figure}[p]
@@
 \end{figure}
-\end{landscape}}
-
-\subsection{Stage 2: Minimising Imbalances}
-
-Having produced a schedule that minimises boat changes, we then minimise imbalance (i.e.\ apply
-criterion~6) by extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage
-produces a schedule with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage
-2. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is
-1 if and only if skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
-of the  $j^{th}$ flight \eqref{C12}. Imbalance \eqref{V10} is then computed for each position, as
-the absolute amount over or under the expected presence in a given position \eqref{C13}. Finally, we
-compute the maximum imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
-
-\begin{figure}[tb]
+\end{landscape}
+
+\begin{figure}[p]
 \setlength{\mathindent}{1em}
@@
 
-We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13} and \ref{C15}) and
-minimise this \eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
-$\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
-
-\subsection{Stage 3: Renaming Skippers}
-
-Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round
-of the last flight to be $(0,1)$, satisfying criterion~9. This is a simple linear process. The
-schedule produced for 7 skippers and 6 boats is shown in Table~\ref{tab2}.
-
-\begin{SCtable}[1.8][tb]
+\begin{SCtable}[1.8][p]
     \setlength{\tabcolsep}{3pt}
@@
 \end{SCtable}
+\clearpage % I feel oh so very dirty
+}
+
+\subsection{Stage 2: Minimising Imbalances}
+
+Having produced a schedule that minimises boat changes, we then minimise imbalance (i.e.\ apply
+criterion~6) by extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage
+produces a schedule with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage
+2. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is
+1 if and only if skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
+of the  $j^{th}$ flight \eqref{C12}. Imbalance \eqref{V10} is then computed for each position, as
+the absolute amount over or under the expected presence in a given position \eqref{C13}. Finally, we
+compute the maximum imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
+
+We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13} and \ref{C15}) and
+minimise this \eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
+$\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
+
+\subsection{Stage 3: Renaming Skippers}
+
+Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round
+of the last flight to be $(0,1)$, satisfying criterion~9. This is a simple linear process. The
+schedule produced for 7 skippers and 6 boats is shown in Table~\ref{tab2}.
 
 \subsection{Stage 4: Orienting Matches}
-
-The final stage, stage 4, orients skippers within matches, such that they are either port (red) or
-starboard (green). This is done to satisfy criteria~2 and~3, 5 and~8. A sketch of the constraint
-model is given with a supporting diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained
-integer variables, of length $n-1$, is produced for each skipper. These correspond to the sequence
-of skippers they meet in matches. For example, taking the schedule in Table~\ref{tab2}, skipper
-$\sigma[{2}]$ meets skippers in order: 3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order
-4,6,0,1,3,2.  Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
-$\sigma[{5}]$'s 5$^{th}$ variable. There are summation constraints on each skipper to enforce
-criteria~2 and~3 (equal number of port and starboard matches). Criterion~8 is enforced by posting
-constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher
-indexed skipper (lower ranked) is on the port side. A DFA constraint is posted for criterion~5
-(restricting sequences of port and starboard assignments).
-
-In Figure~\ref{oriented}, port is red and starboard green. The sequence of zero/one variables for
-each skipper is shown on the left. Bottom right is the DFA, and top right is the final schedule
-produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. Three
-days CPU time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
-schedule presented here is new, not appearing in the example schedules provided in \cite{isaf}.
 
@@
 
+The final stage, stage 4, orients skippers within matches, such that they are either port (red) or
+starboard (green). This is done to satisfy criteria~2 and~3, 5 and~8. A sketch of the constraint
+model is given with a supporting diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained
+integer variables, of length $n-1$, is produced for each skipper. These correspond to the sequence
+of skippers they meet in matches. For example, taking the schedule in Table~\ref{tab2}, skipper
+$\sigma[{2}]$ meets skippers in order: 3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order
+4,6,0,1,3,2.  Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
+$\sigma[{5}]$'s 5$^{th}$ variable. There are summation constraints on each skipper to enforce
+criteria~2 and~3 (equal number of port and starboard matches). Criterion~8 is enforced by posting
+constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher
+indexed skipper (lower ranked) is on the port side. A DFA constraint is posted for criterion~5
+(restricting sequences of port and starboard assignments).
+
+In Figure~\ref{oriented}, port is red and starboard green. The sequence of zero/one variables for
+each skipper is shown on the left. Bottom right is the DFA, and top right is the final schedule
+produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. Three
+days CPU time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
+schedule presented here is new, not appearing in the example schedules provided in the manual
+\cite{isaf}.
+
 \section{Sample Schedules}\label{sec:samples}
@@
 ISAF, the other generated by us. Next, we present two new schedules, not appearing in the ISAF
-manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and
-6 boats, again ISAF published and generated by us. Finalyy, we show what is a relatively easy problem, 8 skippers and 8 boats. 
-For each of our schedules (with the exception of the "easy-8" problem), we used 1 day CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
+manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and 6 boats, again
+ISAF published and generated by us. Finally, we show what is a relatively easy problem, 8 skippers
+and 8 boats.  For each of our schedules (with the exception of the "easy-8" problem), we used 1 day
+CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
 Stages 3 and 4 (renaming and orientation) completed in less than a second.
 
-\begin{center}
-\begin{figure}[h]
+\begin{figure}[b]
 \begin{minipage}[t]{0.48\textwidth}
@@
 \end{figure}
-\end{center}
 
@@
 
-\paragraph{9 skippers}: Two new schedules are presented in Table~\ref{09}, on the left for 6 boats
+\paragraph{9 skippers:} Two new schedules are presented in Table~\ref{09}, on the left for 6 boats
 and on the right for 8 boats. Neither of these schedules appear in the ISAF Umpires' Manual. Both
@@
 
-\begin{center}
 \begin{figure}[h]
@@
 \end{figure}
-\end{center}
-
-\begin{center}
+
+\paragraph{8 skippers and 8 boats (easy-8):} Table \ref{08-08} shows the ISAF schedule on the right
+for 8 skippers and 8 boats and on the right, our schedule.  The ISAF schedule violates criterion~4
+(last match in a flight cannot be first in next flight) for skipper 5 in flights 1 and 2. Also,
+criterion 5 (no skipper should have more than 2 consecutive port or starboard assignments) is
+violated for skippers 0, 1, 3, 4 and 6. Furthermore, skipper 1 appears in the last match of four
+flights resulting in significant imbalance. Our schedule, on the right, satisfies all criteria, is
+optimal (maximum imbalance of 1) and took less than 10 seconds in total (all stages) to produce.
+
 \begin{figure}[h]
@@
 \end{figure}
-\end{center}
-
-\paragraph{8 skippers and 8 boats (easy-8):} Table \ref{08-08} shows the ISAF schedule on the right for 8
-skippers and 8 boats and on the right, our schedule.
-The ISAF schedule violates criterion~4 (last match in a flight cannot be first in next flight) for skipper 5 in flights 1 and 2.
-Also, criterion 5 (no skipper should have more than 2 consecutive port or starboard assignments) is violated for skippers 0, 1, 3, 4 and 6.
-Furthermore, skipper 1 appears in the last match of four flights resulting in significant imbalance.
-Our schedule, on the right, satisfies all criteria, is optimal (maximum imbalance of 1) and took less than 10 seconds in total (all stages) to produce.
-
-\begin{center}
-\begin{figure}[tb]
-\hspace{-1cm}
-\includegraphics[height=12cm,width=17.5cm]{dinghy.jpg}
-\vspace{-30mm}
-\caption{Scene from an imaginary dinghy race.}
-\label{dinghy}
-\end{figure}
-\end{center}
 
@@
 It was anticipated that this problem would be easy to model. This naivety was due to the use of the
-term ``round robin'' for these schedules, leading us to believe that we could use some of the models
-proposed in \cite{trick2002}, \cite{trick2008} and \cite{henz2004}. This naivety slowly dissolved as
+term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
+already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
 we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
@@
 
+\begin{figure}[tb]
+    \centering
+    \includegraphics[keepaspectratio=true,width=4.6in]{dinghy.jpg}
+\caption{Scene from an imaginary dinghy race.}
+\label{dinghy}
+\end{figure}
+
 We have produce new and better match race schedules. These schedules can be used by anyone that
@@
 allow the event organiser to decide which criteria to sacrifice to ensure a faster schedule with
-less boat changes.
+fewer boat changes.
 

### 2015-04-13 paper.tex
Fix rule numbering

@@
 \begin{enumerate}
-\item Each skipper sails against each other skipper once.
+\item[1.] Each skipper sails against each other skipper once.
 \item[2*.] When skippers have an even number of matches, they have the same number of port and starboard
@@
     more starboard assignment.
-\item No skipper in the last match of a flight should be in the first match of the next flight.
-\item No skipper should have more than two consecutive port or starboard assignments.
-\item Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
-\item In flights with five or more matches, no skipper should be in the next-to-last match in a
+\item[4.] No skipper in the last match of a flight should be in the first match of the next flight.
+\item[5.] No skipper should have more than two consecutive port or starboard assignments.
+\item[6.] Each skipper should be assigned to match 1, match 2, etc. in a flight as equally as possible.
+\item[7.] In flights with five or more matches, no skipper should be in the next-to-last match in a
     flight and then in the first match of the next flight.
-\item If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper
+\item[8.] If possible, a skipper should be starboard when meeting the nearest lowest ranked skipper
     (i.e.\ \#1 will be starboard against \#2, \#3 will be starboard against \#4).
-\item Close-ranked skippers meet in the last flight.
-\item Minimise the number of boat changes.
-\item Skippers in the last match of a flight do not change boats.
-\item Skippers in new boats do not sail in the first match of the next flight.
-\item Skippers have a reasonable sequence of matches and blanks.
+\item[9.] Close-ranked skippers meet in the last flight.
+\item[10.] Minimise the number of boat changes.
+\item[11.] Skippers in the last match of a flight do not change boats.
+\item[12.] Skippers in new boats do not sail in the first match of the next flight.
+\item[13.] Skippers have a reasonable sequence of matches and blanks.
 \end{enumerate}

### 2015-04-14 paper.tex
Corrections

@@
 $\sigma[{j}]$ and conversely that skipper $\sigma[{j}]$'s $k^{th}$ time slot is skipper
-$\sigma[{i}]$). Variables \eqref{V6} and constraints \eqref{C7} then convert this from time slots to
+$\sigma[{i}]$. Variables \eqref{V6} and constraints \eqref{C7} then convert this from time slots to
 flights, i.e.\ $\modMatch[{i,j}]$ is the flight in which skippers $\sigma[{i}]$ and $\sigma[{j}]$
@@
 We have only reported a handful of our schedules, however there are missing schedules. Examples of
-these missing schedules are 10 skippers and 8 boats, 11 skippers with less than 10 boats, 12
-skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with less than 10 boats. None of these
+these missing schedules are 10 skippers and 8 boats, 11 skippers with fewer than 10 boats, 12
+skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with fewer than 10 boats. None of these
 schedules have been published by the ISAF, although we expect that they can be produced by

### 2015-04-14 paper.tex
some minor typos and rephrases from my PoV

@@
 \begin{abstract}
-We present a constraint programming solution to the problem of generating round-robin schedules for
-dinghy sailing match races. Our schedules satisfy the widely used ISAF World Sailing pairing lists
-match race criteria. We show that some published ISAF schedules are in fact illegal, and present
+We present a constraint programming solution to the problem of generating round-robin schedules for sailing match races.
+Our schedules satisfy the critria published by the International Sailing Federation (ISAF) governing body for match race pairing lists.
+We show that some published ISAF schedules are in fact illegal, and present
 corresponding legal instances and schedules that have not previously been published. Our schedules
-can be downloaded as blanks, then populated with actual competitors and used in ISAF competitions.
+can be downloaded as blanks, then populated with actual competitors and used in match racing competitions.
 \end{abstract}
@@
 
-The paper is organised as follows: we introduce the 13 match racing rules, then explain the
+The paper is organised as follows: we introduce the 13 match racing criteria, then explain the
 constraint models and four stages of schedule construction, and then schedules are presented. We
@@
 
-There are some conflicts inherent in the rules. Take criteria~4 and~11, assume we have 4 boats, and
+There are some conflicts inherent in the criteria. Take criteria~4 and~11, assume we have 4 boats, and
 in flight $i$ the last match is the pair of skippers ($x,y$). Criterion~11 dictates that skippers $x$
@@
                     \setlength{\tabcolsep}{2pt}
-                    \setlength{\aboverulesep}{0pt}
+                    \setlength{\aboveep}{0pt}
                     \setlength{\belowrulesep}{0pt}
@@
 manual, for 9 skippers and 6 boats and 9 skippers with 8 boats, then 10 skippers and 6 boats, again
-ISAF published and generated by us. Finally, we show what is a relatively easy problem, 8 skippers
-and 8 boats.  For each of our schedules (with the exception of the "easy-8" problem), we used 1 day
+both published by ISAF and generated by us. Finally, we show what is a relatively easy problem, 8 skippers
+and 8 boats.  For each of our schedules (with the exception of the latter ``easy-8'' problem), we used 1 day
 CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
@@
 
-We have produce new and better match race schedules. These schedules can be used by anyone that
+We have produced new and better match race schedules. These schedules can be used by anyone that
 competes under the criteria published by ISAF. Our schedules can be downloaded as blank schedules

### 2015-04-14 paper.tex
patrick typo

@@
 
-\paragraph{10 skippers and 6 boats:} Table \ref{10-06} shows the ISAF schedule on the right for 10
+\paragraph{10 skippers and 6 boats:} Table \ref{10-06} shows the ISAF schedule on the left for 10
 skippers and 6 boats and on the right, our schedule.  The ISAF schedule violates criterion~5 (no more

### 2015-04-15 paper.tex
I don't think Craig meant to change that
changes by patrick & craig to address craig's comments

@@
 Perfect balance would be when a skipper has as many matches in first position in flights as in second position in flights, and so on.
-For example, if we had 9 skippers and 8 boats, each skipper would have 8 matches and could be in the first, second, third or fourth match of a flight.
+For example, if we had 9 skippers, each skipper would have 8 matches and could be in the first, second, third or fourth match of a flight.
 In perfect balance, each of the 8 skippers would appear twice in each position.
-Balance is one of our optimisation criteria.
+Balance is one of our optimisation criteria, and we do this unconditionally i.e.\ even when there are more skippers than boats.
 
@@
 overall number of changes in the entire pairing list schedule; or alternatively as well as a fair,
-but minimal number of changes across all skippers. In our work, we take the latter viewpoint.
+but minimal number of changes across all skippers. In our work, we minise the overall number of changes.
 
@@
                     \setlength{\tabcolsep}{2pt}
-                    \setlength{\aboveep}{0pt}
+                    \setlength{\aboverulesep}{0pt}
                     \setlength{\belowrulesep}{0pt}
@@
 
-\paragraph{8 skippers and 6 boats:} We first analyse the ISAF schedule, Table~\ref{08-06} on the
+\paragraph{8 skippers and 6 boats:} We first analyse the ISAF schedule, Figure~\ref{08-06} on the
 left. Criterion~4 (skippers in last match in a flight cannot be first in next flight) is violated on
@@
 boats do not sail first) is violated in flight 9 for skipper 5. Finally, the schedule has 8 boat
-changes. Our schedule, Table~\ref{08-06} on the right, respects all criteria and has 6 boat changes
+changes. Our schedule, Figure~\ref{08-06} on the right, respects all criteria and has 6 boat changes
 and a maximum imbalance of 1.
 
-\paragraph{9 skippers:} Two new schedules are presented in Table~\ref{09}, on the left for 6 boats
+\paragraph{9 skippers:} Two new schedules are presented in Figure~\ref{09}, on the left for 6 boats
 and on the right for 8 boats. Neither of these schedules appear in the ISAF Umpires' Manual. Both
@@
 
-\paragraph{10 skippers and 6 boats:} Table \ref{10-06} shows the ISAF schedule on the left for 10
+\paragraph{10 skippers and 6 boats:} Figure~\ref{10-06} shows the ISAF schedule on the left for 10
 skippers and 6 boats and on the right, our schedule.  The ISAF schedule violates criterion~5 (no more
@@
 1, flight 9 for skipper 4 and flight 12 for skipper 4 again). There are 22 boat changes, with the
-minimum changes for a skipper being 1 and the maximum 3. Our schedule, right of Table \ref{10-06},
+minimum changes for a skipper being 1 and the maximum 3. Our schedule, right of Figure~\ref{10-06},
 satisfies all criteria, has 12 boat changes with the minimum changes for a skipper being 0 and the
@@
 
-\paragraph{8 skippers and 8 boats (easy-8):} Table \ref{08-08} shows the ISAF schedule on the right
+\paragraph{8 skippers and 8 boats (easy-8):} Figure~\ref{08-08} shows the ISAF schedule on the right
 for 8 skippers and 8 boats and on the right, our schedule.  The ISAF schedule violates criterion~4
@@
 
-We have only reported a handful of our schedules, however there are missing schedules. Examples of
-these missing schedules are 10 skippers and 8 boats, 11 skippers with fewer than 10 boats, 12
+We have only reported a handful of our schedules, however there are missing schedules i.e.\ unpublished and not yet produced by us. Examples of
+these are 10 skippers and 8 boats, 11 skippers with fewer than 10 boats, 12
 skippers and 8 boats, 13 skippers and 8 boats and 14 skippers with fewer than 10 boats. None of these
@@
 situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the
-first two stages.
+first two stages. In addition, we have yet to address the format of \emph{two-group} round-robin schedules as also found in \cite{isaf}.
 

### 2015-06-02 paper.tex
Don't cite as a noun
removed !

@@
 automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
-teams communications, it was also a constraint!
+teams communications, it was also a constraint.
 
@@
 situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the
-first two stages. In addition, we have yet to address the format of \emph{two-group} round-robin schedules as also found in \cite{isaf}.
+first two stages. In addition, we have yet to address the format of
+\emph{two-group} round-robin schedules as also found in the manual \cite{isaf}.
 

### 2015-06-19 paper.tex
Numerous changes for 3 reviews
too many to mention

@@
 \newcommand{\allDifferent}{\mathrm{allDifferent}}
-\newcommand{\validStateSequence}{\mathrm{validStateSequence}}
+%\newcommand{\validStateSequence}{\mathrm{validStateSequence}}
+\newcommand{\regular}{\mathrm{regular}}
 \newcommand{\minimise}{\mathrm{minimise}}
@@
 We present a constraint programming solution to the problem of generating round-robin schedules for sailing match races.
-Our schedules satisfy the critria published by the International Sailing Federation (ISAF) governing body for match race pairing lists.
+Our schedules satisfy the criteria published by the International Sailing Federation (ISAF) governing body for match race pairing lists.
 We show that some published ISAF schedules are in fact illegal, and present
@@
 \section{Introduction}
-
+\vspace{-2mm}
 This work describes a round-robin competition format that arises from sailing, known as match
@@
 and first home wins that match. Criteria published by the International Sailing Federation (ISAF)
-dictate what makes a legal match race schedule and what should be optimised. This is a rich set of
+dictate what makes a legal match race schedule and what should be optimized. This is a rich set of
 criteria, 13 in all, and as far as we know, all published schedules have been produced by hand. This
@@
 published schedules are presented along with some of our own, some of these being new.  These
-schedules are essentially blank forms, made available to event organisers, which can be filled in
+schedules are essentially blank forms, made available to event organizers, which can be filled in
 with names of actual competitors, i.e.\ these schedules are reusable.
 
-The paper is organised as follows: we introduce the 13 match racing criteria, then explain the
+The paper is organized as follows: we introduce the 13 match racing criteria, then explain the
 constraint models and four stages of schedule construction, and then schedules are presented. We
@@
 \section{Problem Definition: Round-Robin Pairing Lists}\label{sec:definition}
-
+\vspace{-2mm}
 The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the
@@
 fine-tune the boat they change into. Typically, matches set off at 5 minute intervals with each
-match taking about 20 minutes. Therefore, if we have 10 skippers and 10 boats we have 45 matches.
-This results in 9 flights each of 5 matches.  Each flight takes about 50 minutes, so eight or nine
+match taking about 20 minutes. Therefore, if we have 10 skippers and 10 boats we have 45 matches,
+9 flights each of 5 matches, and if each flight takes about 50 minutes,  eight or nine
 flights a day is a reasonable achievement for most events~\cite{isaf}. Consequently, the number of
@@
 \item[9.] Close-ranked skippers meet in the last flight.
-\item[10.] Minimise the number of boat changes.
+\item[10.] Minimize the number of boat changes.
 \item[11.] Skippers in the last match of a flight do not change boats.
@@
 
-Criteron~6 allows us to measure the \emph{balance} of a schedule.
+Criterion~6 allows us to measure the \emph{balance} of a schedule.
 Perfect balance would be when a skipper has as many matches in first position in flights as in second position in flights, and so on.
@@
 In perfect balance, each of the 8 skippers would appear twice in each position.
-Balance is one of our optimisation criteria, and we do this unconditionally i.e.\ even when there are more skippers than boats.
+Balance is one of our optimization criteria, and we do this unconditionally i.e.\ even when there are more skippers than boats.
 
@@
 
-Criterion~10 is ambiguous: this could be interpreted on a schedule basis: i.e.\ to minimise the
+Criterion~10 is ambiguous: this could be interpreted on a schedule basis: i.e.\ to minimize the
 overall number of changes in the entire pairing list schedule; or alternatively as well as a fair,
-but minimal number of changes across all skippers. In our work, we minise the overall number of changes.
+but minimal number of changes across all skippers. In our work, we minimize the overall number of changes.
 
@@
 \section{The Constraint Models}\label{sec:models}
-
+\vspace{-2mm}
 Our approach produces schedules in four stages. The first stage produces a schedule that respects
-criteria~1, 4, 11 and~12, and minimises criteria~10 (boat changes). The second stage constructs a
+criteria~1, 4, 11 and~12, and minimizes criteria~10 (boat changes). The second stage constructs a
 schedule that respects criteria~1, 4, 11, 12 (again), has criterion~10 as a hard constraint generated
-from first stage, and minimises criterion~6 (balance). This results in a schedule that attempts to
-minimise boat changes \emph{and} balance. The third stage satisfies criterion~9, and is a simple
+from first stage, and minimizes criterion~6 (balance). This results in a multi-objective schedule that attempts to
+minimize boat changes \emph{and} balance. The third stage satisfies criterion~9, and is a simple
 translation of the schedule produced in stage 2.  The final stage orients skippers within matches to
@@
 
-\subsection{Stage 1: Minimising Boat Changes}
-
+\subsection{Stage 1: Minimizing Boat Changes}
+\vspace{-1mm}
 \paragraph{Modeling skippers:} The first thing we model, in the first half of
@@
     &\forall i \in \{0 \nldots f{-}1\}: \state[{i}] \in \{\FIRST,\MID,\LAST,\BYE,\END\} \label{var:state} \tag{V2} \\
-    &\forall i \in \{0 \nldots f\}: \label{C1} \tag{C1} \\
+    &\forall i \in \{0 \nldots f{-}1\}: \label{C1} \tag{C1} \\
     &\begin{alignedat}{3}
@@
     &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n{-}1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
-    &\validStateSequence(\state) \label{C3} \tag{C3} \\[0.1cm]
+    & \regular(\state) \label{C3} \tag{C3} \\[0.1cm]
     & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
@@
 (below). The number of skippers is $n$, and $m$ is the number of matches in a flight. The number of
-flights is $f = \lceil n(n-1)/m \rceil$, and there are $t = n(n-1)/2$ matches in
-total.}\label{model:stage1}
+flights is $f = \lceil n(n-1)/m \rceil$, and there are $t = n(n-1)/2$ matches (and time slots) in
+total. In \eqref{V4} we assume $\mathbb{N}$ contains zero.}\label{model:stage1}
 \end{figure}
@@
 in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i+1$ is not first).
-These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint
+These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint, i.e. Pesant's \emph{regular} constraint 
 \cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
@@
 skipper has finished all matches in flight $i$ (i.e.\ is in state $\END$) then that skipper will also have
-finished all matches in flight $i+1$ (and so on).
+finished all matches in flight $i+1$ (and so on). Note that when we have as many boats as skippers directed edge $(\BYE,\LAST)$ becomes bidirectional.
 
@@
 
-        \draw [<->, >=latex, thick] (DFAL) to (DFAB);
+        \draw [<-, >=latex, thick] (DFAL) to (DFAB);
 
@@
     \caption{A pictorial representation of a skipper (skipper 5) with multicoloured state and grey
-        timeslots. The schedule for skipper 5 is in bold and the deterministic finite automaton for
+        timeslots. The schedule for skipper 5 is in bold and the DFA for
         criteria~4, 11 and~12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
@@
 \paragraph{Match perspective:} We are now in a position to model criterion~1 (each skipper sails
-against every other skipper) and optimisation criterion~10 (minimise boat changes).  In the second
+against every other skipper) and optimization criterion~10 (minimize boat changes).  In the second
 half of Figure~\ref{model:stage1} we present a match perspective of the schedule, using a two
@@
 
-\paragraph{Optimisation criteria:} Finally we have the optimisation criterion (criterion~10) to
-minimise the number of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
+\paragraph{Optimization criteria:} Finally we have the optimization criterion (criterion~10) to
+minimize the number of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
 
@@
 \begin{align}
-    \intertext{We minimise the maximum imbalance over all skippers:\smallskip}
+    \intertext{We minimize the maximum imbalance over all skippers:\smallskip}
     & \forall i \in \{ 0 \nldots n{-}1 \} : \imbalance[{i}] \equiv \sigma[{i}].\maxImbalance \label{V12} \tag{V12} \\
@@
         position 2 (last). Perfect balance would be 2 matches in each position, only achieved by
-    skipper 2.}\label{tab2}
+        $\sigma[{2}]$.}\label{tab2}
 \end{SCtable}
@@
 
-\subsection{Stage 2: Minimising Imbalances}
-
-Having produced a schedule that minimises boat changes, we then minimise imbalance (i.e.\ apply
-criterion~6) by extending the model as in Figure~\ref{model:stage2}.  Assuming the first stage
+\subsection{Stage 2: Minimizing Imbalances}
+\vspace{-1mm}
+Having produced a schedule that minimizes boat changes, we then minimize imbalance (i.e.\ apply
+criterion~6) by extending the model in Figure~\ref{model:stage2}.  Assuming the first stage
 produces a schedule with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage
@@
 We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13} and \ref{C15}) and
-minimise this \eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
+minimize this \eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
 $\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.
@@
 \subsection{Stage 3: Renaming Skippers}
-
+\vspace{-1mm}
 Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round
@@
 \subsection{Stage 4: Orienting Matches}
-
+\vspace{-1mm}
 \begin{figure}[tb]
@@
 starboard (green). This is done to satisfy criteria~2 and~3, 5 and~8. A sketch of the constraint
-model is given with a supporting diagram, Figure~\ref{oriented}.  A sequence of zero/one constrained
-integer variables, of length $n-1$, is produced for each skipper. These correspond to the sequence
-of skippers they meet in matches. For example, taking the schedule in Table~\ref{tab2}, skipper
-$\sigma[{2}]$ meets skippers in order: 3,0,1,4,5,6, and skipper $\sigma[{5}]$ in the order
-4,6,0,1,3,2.  Therefore, skipper $\sigma[{2}]$'s 4$^{th}$ variable must take a different value from
-$\sigma[{5}]$'s 5$^{th}$ variable. There are summation constraints on each skipper to enforce
+model is given with a supporting diagram, Figure~\ref{oriented}.  The two dimensional array 
+of constrained integer variables $orient[i,j] \in \{0,1\}$ has $orient[i,j] = 0$ if and only if skipper $\sigma[i]$ is on port side in his $j^{th}$ match (starboard otherwise).
+For example, taking the schedule in Table~\ref{tab2}, skipper 
+$\sigma[{2}]$ meets skippers in the order 3,0,1,4,5,6; skipper 
+$\sigma[3]$ meets skippers in the order 2,6,0,5,1,4 and 
+$\sigma[{5}]$ meets skippers in the order 4,6,0,1,3,2.  Therefore
+$orient[2,0] \neq orient[3,0]$,
+$orient[2,4] \neq orient[5,5]$ and
+$orient[3,3] \neq orient[5,4]$.
+There are summation constraints on each skipper to enforce
 criteria~2 and~3 (equal number of port and starboard matches). Criterion~8 is enforced by posting
 constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher 
-indexed skipper (lower ranked) is on the port side. A DFA constraint is posted for criterion~5
+indexed skipper (lower ranked) is on the port side. A DFA constraint (i.e. \emph{regular}) is posted for criterion~5
 (restricting sequences of port and starboard assignments).
@@
 each skipper is shown on the left. Bottom right is the DFA, and top right is the final schedule
-produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. Three
-days CPU time was devoted to stages 1 and 2. Stages 3 and 4 completed in 15 milliseconds. The
-schedule presented here is new, not appearing in the example schedules provided in the manual
+produced from stages 1 to 4. The schedule has 6 boat changes and a maximum imbalance of 1. 
+The schedule presented here is new, not appearing in the example schedules provided in the manual
 \cite{isaf}.
@@
 \section{Sample Schedules}\label{sec:samples}
-
+\vspace{-2mm}
 We present four pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
@@
 both published by ISAF and generated by us. Finally, we show what is a relatively easy problem, 8 skippers
-and 8 boats.  For each of our schedules (with the exception of the latter ``easy-8'' problem), we used 1 day
-CPU time for the first stage (minimising boat changes) then a further 2 days to minimise imbalance.
-Stages 3 and 4 (renaming and orientation) completed in less than a second.
+and 8 boats.  For each of our schedules (with the exception of the latter ``easy-8'' problem) we used 1 day
+CPU time for the first stage (minimizing boat changes) then a further 2 days to minimize imbalance. We were unable to find and prove optimality in this time, therefore some of 
+these schedules might be improved. The processor used was an Intel (R) Xeon (R) E5-2660 at 2.20GHz. 
+Note, stages 3 and 4 (renaming and orientation) completed in less than a second.
 
@@
 
-\paragraph{8 skippers and 6 boats:} We first analyse the ISAF schedule, Figure~\ref{08-06} on the
+\paragraph{8 skippers and 6 boats:} We first analyze the ISAF schedule, Figure~\ref{08-06} on the
 left. Criterion~4 (skippers in last match in a flight cannot be first in next flight) is violated on
@@
 \section{Discussion}
-
+\vspace{-2mm}
 It was anticipated that this problem would be easy to model. This naivety was due to the use of the
@@
 automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
-teams communications, it was also a constraint.
+teams communications, it was also a constraint (the \emph{regular} constraint).
 
@@
 
-We used the choco constraint programming toolkit and one of our goals was to use only toolkit
-constraints, i.e.\ we wanted to see how far we could go without implementing our own specialised
+We used the Choco constraint programming toolkit and one of our goals was to use only toolkit
+constraints, i.e.\ we wanted to see how far we could go without implementing our own specialized
 constraints. We are pleased to say that we did not have to do anything out of the box, although we
@@
 surprisingly short amount of time, sometimes minutes of coding to add in a new feature. The model
-was then enhanced so that it would address optimisation rather than just satisfaction, again a
+was then enhanced so that it would address optimization rather than just satisfaction, again a
 trivial programming task.
@@
 selectively violating some of constraints. We have also not yet encoded criterion~7, addressing the
-situation of 10 or more boats. To do this we will have to modify the DFA constraint used in the
+situation of 10 or more boats. To do this we will have to modify the DFA used by the \emph{regular} constraint in the
 first two stages. In addition, we have yet to address the format of
@@
 \section{Conclusion}\label{sec:conclusions}
-
+\vspace{-2mm}
 \begin{figure}[tb]
     \centering
-    \includegraphics[keepaspectratio=true,width=4.6in]{dinghy.jpg}
+    \includegraphics[keepaspectratio=true,width=4.1in]{dinghy.jpg}
 \caption{Scene from an imaginary dinghy race.}
@@
 
-We have produced new and better match race schedules. These schedules can be used by anyone that
+We have produced new and better match race schedules. These schedules can be used by anyone who
 competes under the criteria published by ISAF. Our schedules can be downloaded as blank schedules
@@
 we might exploit in the future: we can now investigate the effect different criteria have on our
-ability to produce schedules and how relaxation of those affect optimisation criteria. That is, the
+ability to produce schedules and how relaxation of those affect optimization criteria. That is, the
 constraint program might be used to design the next set of criteria for match race schedules, or
-allow the event organiser to decide which criteria to sacrifice to ensure a faster schedule with
+allow the event organizer to decide which criteria to sacrifice to ensure a faster schedule with
 fewer boat changes.

### 2015-06-19 paper.tex
Removed vspace and modified subsection on orientation
no more negative space
in 3.4 orient[2,0] = 1 and orient[3,0] = 0 due to criterion 8

@@
 \section{Introduction}
-\vspace{-2mm}
 This work describes a round-robin competition format that arises from sailing, known as match
@@
 \section{Problem Definition: Round-Robin Pairing Lists}\label{sec:definition}
-\vspace{-2mm}
 The guidelines for running match racing events~\cite{isaf} places a number of criteria on how the
@@
 \section{The Constraint Models}\label{sec:models}
-\vspace{-2mm}
 Our approach produces schedules in four stages. The first stage produces a schedule that respects
@@
 \subsection{Stage 1: Minimizing Boat Changes}
-\vspace{-1mm}
 \paragraph{Modeling skippers:} The first thing we model, in the first half of
@@
 \subsection{Stage 2: Minimizing Imbalances}
-\vspace{-1mm}
 Having produced a schedule that minimizes boat changes, we then minimize imbalance (i.e.\ apply
@@
 \subsection{Stage 3: Renaming Skippers}
-\vspace{-1mm}
 Stage 3 then takes as input the schedule produced in stage 2 and renames skippers in the last round
@@
 \subsection{Stage 4: Orienting Matches}
-\vspace{-1mm}
 \begin{figure}[tb]
@@
 The final stage, stage 4, orients skippers within matches, such that they are either port (red) or
-starboard (green). This is done to satisfy criteria~2 and~3, 5 and~8. A sketch of the constraint
-model is given with a supporting diagram, Figure~\ref{oriented}.  The two dimensional array 
+starboard (green). This is done to satisfy criteria~2,~3, 5 and~8. A sketch of the constraint
+model is given with a supporting diagram, Figure~\ref{oriented}.  A two dimensional array 
 of constrained integer variables $orient[i,j] \in \{0,1\}$ has $orient[i,j] = 0$ if and only if skipper $\sigma[i]$ is on port side in his $j^{th}$ match (starboard otherwise).
@@
 $\sigma[{5}]$ meets skippers in the order 4,6,0,1,3,2.  Therefore
-$orient[2,0] \neq orient[3,0]$,
+$orient[2,0] = 1 ~and~ orient[3,0] = 0$ (criterion 8),
 $orient[2,4] \neq orient[5,5]$ and
 $orient[3,3] \neq orient[5,4]$.
-There are summation constraints on each skipper to enforce
+Summation constraints on each skipper enforce
 criteria~2 and~3 (equal number of port and starboard matches). Criterion~8 is enforced by posting
@@
 \section{Sample Schedules}\label{sec:samples}
-\vspace{-2mm}
 We present four pairs of schedules. The first pair is for 8 skippers and 6 boats, one published by
@@
 \section{Discussion}
-\vspace{-2mm}
 It was anticipated that this problem would be easy to model. This naivety was due to the use of the
@@
 \section{Conclusion}\label{sec:conclusions}
-\vspace{-2mm}
 \begin{figure}[tb]

### 2015-06-22 paper.tex
Wording on what N means
Just say prove, not find and prove

@@
 flights is $f = \lceil n(n-1)/m \rceil$, and there are $t = n(n-1)/2$ matches (and time slots) in
-total. In \eqref{V4} we assume $\mathbb{N}$ contains zero.}\label{model:stage1}
+total. We define $\mathbb{N}$ to include zero.}\label{model:stage1}
 \end{figure}
@@
 and 8 boats.  For each of our schedules (with the exception of the latter ``easy-8'' problem) we used 1 day
-CPU time for the first stage (minimizing boat changes) then a further 2 days to minimize imbalance. We were unable to find and prove optimality in this time, therefore some of 
+CPU time for the first stage (minimizing boat changes) then a further 2 days to minimize imbalance. We were unable to prove optimality in this time, therefore some of
 these schedules might be improved. The processor used was an Intel (R) Xeon (R) E5-2660 at 2.20GHz. 

### 2015-06-22 paper.tex
Mark special edge with a star

@@
 skipper has finished all matches in flight $i$ (i.e.\ is in state $\END$) then that skipper will also have
-finished all matches in flight $i+1$ (and so on). Note that when we have as many boats as skippers directed edge $(\BYE,\LAST)$ becomes bidirectional.
+finished all matches in flight $i+1$ (and so on). Note that when we have as many
+boats as skippers, the directed edge $(\BYE,\LAST)$ (marked $\star$) becomes bidirectional.
 
@@
 
-        \draw [<-, >=latex, thick] (DFAL) to (DFAB);
+        \draw [<-, >=latex, thick] (DFAL) to node [xshift=0.6em] { $\star$ } (DFAB);
 
@@
         criteria~4, 11 and~12 is drawn with state $\START$ in white, $\FIRST$ in blue, $\MID$ in
-        yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red.}\label{skipper5}
+        yellow, $\LAST$ in green, $\BYE$ in pink and $\END$ in red. The edge
+        marked $\star$ is explained in the text.}\label{skipper5}
 \end{figure}

### 2015-06-22 paper.tex
Wording of regular

@@
     &\eachOccursExactlyOnce(\timeSlot, \{0, \nldots, n{-}1\} \setminus \{\sigma\}) \label{C2} \tag{C2} \\
-    & \regular(\state) \label{C3} \tag{C3} \\[0.1cm]
+    & \regular(\state, \textnormal{Figure~\ref{skipper5}}) \label{C3} \tag{C3} \\[0.1cm]
     & \forall i \in \{0 \nldots f{-}2\}: \change[{i}] \in \{0,1\} \label{V3} \tag{V3} \\
@@
 in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i+1$ is not first).
-These criteria are imposed by \eqref{C3}, which is a deterministic finite automaton (DFA) constraint, i.e. Pesant's \emph{regular} constraint 
-\cite{Pesant04}. The transitions for the DFA are shown pictorially in Figure~\ref{skipper5}: arcs
-represent a possible transition from one state to another. The DFA is encoded as a set of transition objects
-$\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from state $q_{i}$ to state $q_{j}$
-when encountering input~$\iota$. In addition we specify the accepting states, which are all states
-except the start state (white) and the bye state (pink).  This constraint also ensures that if a
-skipper has finished all matches in flight $i$ (i.e.\ is in state $\END$) then that skipper will also have
-finished all matches in flight $i+1$ (and so on). Note that when we have as many
-boats as skippers, the directed edge $(\BYE,\LAST)$ (marked $\star$) becomes bidirectional.
+These criteria are imposed in \eqref{C3} by the deterministic finite automaton (DFA) shown in
+Figure~\ref{skipper5} using Pesant's \emph{regular} constraint \cite{Pesant04}. The arcs in
+Figure~\ref{skipper5} represent possible transitions from one state to another. The DFA is encoded
+as a set of transition objects $\langle q_{i},\iota,q_{j} \rangle$, where a transition is made from
+state $q_{i}$ to state $q_{j}$ when encountering input~$\iota$. In addition we specify the accepting
+states, which are all states except the start state (white) and the bye state (pink).  This
+constraint also ensures that if a skipper has finished all matches in flight $i$ (i.e.\ is in state
+$\END$) then that skipper will also have finished all matches in flight $i+1$ (and so on). Note that
+when we have as many boats as skippers, the directed edge $(\BYE,\LAST)$ (marked $\star$) becomes
+bidirectional.
 
@@
 constraints such that in a match ($\sigma[{i}],\sigma[{j}]$) where $\abs*{i - j} = 1$, the higher 
-indexed skipper (lower ranked) is on the port side. A DFA constraint (i.e. \emph{regular}) is posted for criterion~5
+indexed skipper (lower ranked) is on the port side. A \emph{regular} constraint is posted for criterion~5
 (restricting sequences of port and starboard assignments).

### 2015-06-22 paper.tex
Spacing for refs

@@
 
-Variable $\state[{i}]$ \eqref{var:state} gives the state of this skipper in flight~$i$,
+Variable $\state[{i}]$~\eqref{var:state} gives the state of this skipper in flight~$i$,
 corresponding to time slots $\timeSlot[{m \cdot i}]$ to $\timeSlot[{m(i+1)-1}]$.
-The cases in \eqref{C1} state that a skipper can be in a match in the first time slot in the flight,
+The cases in~\eqref{C1} state that a skipper can be in a match in the first time slot in the flight,
 or in the middle of the flight\footnote{i.e.\ not first and not last.}, or in the last time slot of
@@
 We must then ensure that each skipper $\sigma$ is in a match with all other skippers $\{0, \nldots,
-n-1\} \setminus \{\sigma\}$. This is \eqref{C2}, which is enforced by imposing a global
+n-1\} \setminus \{\sigma\}$. This is~\eqref{C2}, which is enforced by imposing a global
 cardinality constraint \cite{globCard} on the array $\timeSlot$.
@@
 in a bye in flight $i+1$) and criterion~12 (if flight $i$ is a bye then flight $i+1$ is not first).
-These criteria are imposed in \eqref{C3} by the deterministic finite automaton (DFA) shown in
+These criteria are imposed in~\eqref{C3} by the deterministic finite automaton (DFA) shown in
 Figure~\ref{skipper5} using Pesant's \emph{regular} constraint \cite{Pesant04}. The arcs in
@@
 skipper 5 in the schedule shown in Table~\ref{tab1}. The $\state$ array is presented as coloured boxes, and
-below that is the $\timeSlot$ array. The arrows represent the channeling constraints \eqref{C1}. The
+below that is the $\timeSlot$ array. The arrows represent the channeling constraints~\eqref{C1}. The
 $\state$ array is coloured with green representing $\LAST$, yellow for $\MID$, blue for $\FIRST$,
@@
 $i$ and then is in a match in the next flight $i+1$.  This is encoded using the array of zero/one
-variables \eqref{V3}, and the constraint \eqref{C4}, and accumulated into $\totalChanges$
+variables~\eqref{V3}, and the constraint~\eqref{C4}, and accumulated into $\totalChanges$
 (\ref{V4},~\ref{C5}).
@@
 half of Figure~\ref{model:stage1} we present a match perspective of the schedule, using a two
-dimensional array of variables $\match$ \eqref{V5}, where $\match[{i,j}]$ is the time slot in which
+dimensional array of variables $\match$~\eqref{V5}, where $\match[{i,j}]$ is the time slot in which
 skippers $\sigma[{i}]$ and $\sigma[{j}]$ meet in a match. Only the half above the diagonal is
 represented, and the lower half is made up of exactly the same variables, i.e.\ $\match[{i,j}]$ is
-\emph{exactly} the same constrained variable as $\match[{j,i}]$. Constraint \eqref{C6} states that
+\emph{exactly} the same constrained variable as $\match[{j,i}]$. Constraint~\eqref{C6} states that
 a match between skippers $\sigma[{i}]$ and $\sigma[{j}]$ takes place at time $k$ (i.e.\
@@
 $\sigma[{j}]$ and conversely that skipper $\sigma[{j}]$'s $k^{th}$ time slot is skipper
-$\sigma[{i}]$. Variables \eqref{V6} and constraints \eqref{C7} then convert this from time slots to
+$\sigma[{i}]$. Variables~\eqref{V6} and constraints~\eqref{C7} then convert this from time slots to
 flights, i.e.\ $\modMatch[{i,j}]$ is the flight in which skippers $\sigma[{i}]$ and $\sigma[{j}]$
-meet for a match. Finally, constraint \eqref{C8} ensures that each skipper's match occurs in
+meet for a match. Finally, constraint~\eqref{C8} ensures that each skipper's match occurs in
 different flights. Also, since $\modMatch[{i,j}] \equiv \modMatch[{j,i}]$, setting rows to be all
@@
 
-\paragraph{Temporal perspective:} We now take a temporal view \eqref{V7}, such that
+\paragraph{Temporal perspective:} We now take a temporal view~\eqref{V7}, such that
 $\timeVar[{\tau}]$ is a pair $(i,j)$, stating that at time $\tau$ skippers $\sigma[{i}]$ and
 $\sigma[{j}]$ are in a match. We channel between the match perspective and the temporal perspective
-using \eqref{C9}.
+using~\eqref{C9}.
 
 \paragraph{Optimization criteria:} Finally we have the optimization criterion (criterion~10) to
-minimize the number of boat changes. This is handled by \eqref{V8} and \eqref{C10}.
+minimize the number of boat changes. This is handled by~\eqref{V8} and~\eqref{C10}.
 
@@
 criterion~6) by extending the model in Figure~\ref{model:stage2}.  Assuming the first stage
-produces a schedule with $\beta$ boat changes we post this as a hard constraint \eqref{C11} in stage
-2. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$ \eqref{V9} which is
+produces a schedule with $\beta$ boat changes we post this as a hard constraint~\eqref{C11} in stage
+2. For each skipper $\sigma$ we introduce a zero/one variable $position[{i,j}]$~\eqref{V9} which is
 1 if and only if skipper $\sigma$ is in a match in time $m \cdot j + i$, i.e.\ in the $i^{th}$ match
-of the  $j^{th}$ flight \eqref{C12}. Imbalance \eqref{V10} is then computed for each position, as
-the absolute amount over or under the expected presence in a given position \eqref{C13}. Finally, we
+of the  $j^{th}$ flight~\eqref{C12}. Imbalance~\eqref{V10} is then computed for each position, as
+the absolute amount over or under the expected presence in a given position~\eqref{C13}. Finally, we
 compute the maximum imbalance over all positions for this skipper (\ref{V11}, \ref{C14}).
 
-We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13} and \ref{C15}) and
-minimize this \eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
+We then capture the maximum imbalance over all skippers (\ref{V12}, \ref{V13} and~\ref{C15}) and
+minimize this~\eqref{C16}. As before, the decision variables are $\timeVar[{0}]$ to
 $\timeVar[{t-1}]$ and the same symmetry breaking is imposed at top of search.

### 2015-06-22 paper.tex
Page layout tweaks
Picture can be bigger
Typo

@@
 flights within a schedule and the position of skippers within a match. This permits fair schedules
-that provide the sufficient changeover time for skippers changing boats, etc.
+that provide sufficient changeover time for skippers changing boats, etc.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \begin{minipage}[t]{0.48\textwidth}
@@
     \centering
-    \includegraphics[keepaspectratio=true,width=4.1in]{dinghy.jpg}
+    \includegraphics[keepaspectratio=true,width=4.6in]{dinghy.jpg}
 \caption{Scene from an imaginary dinghy race.}

### 2015-06-22 paper.tex
That's not an i.e.
Apostrophe

@@
 In perfect balance, each of the 8 skippers would appear twice in each position.
-Balance is one of our optimization criteria, and we do this unconditionally i.e.\ even when there are more skippers than boats.
+Balance is one of our optimization criteria, and we do this unconditionally, even when there are more skippers than boats.
 
@@
 automaton. This became our Rosetta Stone, with the surprising benefit that it not only improved the
-teams communications, it was also a constraint (the \emph{regular} constraint).
+team's communications, it was also a constraint (the \emph{regular} constraint).
 

### 2015-06-22 paper.tex
Spelling

@@
 \section{Discussion}
-It was anticipated that this problem would be easy to model. This naivety was due to the use of the
+It was anticipated that this problem would be easy to model. This na{\"\i}vety was due to the use of the
 term ``round-robin'' for these schedules, leading us to believe that we could use some of the models
-already in the literature \cite{trick2002,trick2008,henz2004}. This naivety slowly dissolved as
+already in the literature \cite{trick2002,trick2008,henz2004}. This na{\"\i}vety slowly dissolved as
 we addressed more and more of the ISAF criteria. A number of models we produced were scrapped due to
